\chapter{Geometry of Number Fields}
  Throughout, all rings will be understood to be commutative and with unity. We will also use the theory of integral lattices in \cref{sec:integral_lattices} and some results of the beta function is \cref{sec:the_gamma_function}.
  \section{Minkowski Space}
    Let \(K\) be number field of degree \(n\). If \(\s \in \Hom_{\Q}(K,\conj{\Q})\) then either \(\s\) is real or complex and in the latter case it is has a paired \(\Q\)-embedding \(\conj{\s}\) which is the complex conjugate of \(\s\). Accordingly, let \(r_{1}\) and \(2r_{2}\) be the number of real and complex \(\Q\)-embeddings of \(K\) into \(\conj{\Q}\) respectively. We call the pair \((r_{1},r_{2})\) the \textbf{signature}\index{signature} of \(K\) and it satisfies the relation
    \[
      n = r_{1}+2r_{2}.
    \]
    Setting
    \[
      K_{\C} = \C^{n},
    \]
    makes \(K_{\C}\) into a component-wise \(\C\)-algebra. Moreover, \(K_{\C}\) is also a complex Hilbert space with respect to the standard complex inner product which we denote by \(\<\cdot,\cdot\>_{K_{\C}}\). We also write \(d\l_{K_{\C}}\) for the induced Lebesgue measure on \(K_{\C}\) by this inner product. Also let \(\Trace_{K_{\C}}\) and \(\Norm_{K_{\C}}\) denote the trace and norm of \(K_{\C}/\C\). Because \(K_{\C}\) is a component-wise \(\C\)-algebra, the trace and the norm are given by
    \[
      \Trace_{K_{\C}}(\mathbf{z}) = \sum_{\s}z_{\s} \quad \text{and} \quad \Norm_{K_{\C}}(\mathbf{z}) = \prod_{\s}z_{\s},
    \]
    for all \(\mathbf{z} \in K_{\R}\). We define the \textbf{canonical embedding}\index{canonical embedding} \(j\) of \(K\) to be the \(\Q\)-embedding
    \[
      j:K \to K_{\C} \qquad \k \mapsto (\s(\k))_{\s}.
    \]
    In other words, the canonical embedding is a component-wise \(\Q\)-embedding of \(K\) into \(K_{\C}\) via the \(\s\). In view of \cref{prop:formulas_for_trace_and_norm}, we have
    \[
      \Trace_{K_{\C}}(j(\k)) = \Trace_{K}(\k) \quad \text{and} \quad \Norm_{K_{\C}}(j(\k)) = \Norm_{K}(\k),
    \]
    which is to say that the compositions of the trace and norm of \(K_{\C}/\C\) with the canonical embedding produces the field trace and field norm. Our primary aim is to construct an \(\R\)-subalgebra of \(K_{\C}\) which corrects for the fact that the complex \(\Q\)-embeddings come in pairs. To this end, consider the conjugation map
    \[
      F:\C \to \C \qquad z \mapsto \conj{z}.
    \]
    This induces an automorphism of \(K_{\C}\) given by
    \[
      F:K_{\C} \to K_{\C} \qquad \mathbf{z} \mapsto (\conj{z_{\conj{\s}}})_{\s},
    \]
    which is an involution. A short computation shows
    \[
      \<F(\mathbf{z}),F(\mathbf{w})\>_{K_{\C}} = F(\<\mathbf{z},\mathbf{w}\>_{K_{\C}}),
    \]
    for all \(\mathbf{z},\mathbf{w} \in K_{\C}\). In other words, inner product \(\<\cdot,\cdot\>_{K_{\C}}\) is \(F\)-equivariant. We define the \textbf{Minkowski space}\index{Minkowski space} \(K_{\R}\) of \(K\) by
    \[
      K_{\R} = \{\mathbf{z} \in K_{\C}:F(\mathbf{z}) = \mathbf{z}\}.
    \]
    In other words, \(K_{\R}\) consists of all of the \(F\)-invariant points of \(K_{\C}\). Note that \(K_{\R}\) is an \(\R\)-subalgebra of \(K_{\C}\). We denote the restriction of the inner product \(\<\cdot,\cdot\>_{K_{\C}}\) to \(K_{\R}\) by \(\<\cdot,\cdot\>_{K_{\R}}\). Moreover, the inner product \(\<\cdot,\cdot\>_{K_{\R}}\) turns \(K_{\R}\) into a real Hilbert space. Indeed, the conjugate symmetry and \(F\)-equivariance of the inner product together give
    \[
      \conj{\<\mathbf{z},\mathbf{w}\>} = \<\mathbf{z},\mathbf{w}\>,
    \]
    for any \(\mathbf{z},\mathbf{w} \in K_{\R}\). Accordingly, we call \(\<\cdot,\cdot\>_{K_{\R}}\) the \textbf{Minkowski inner product}\index{Minkowski inner product} of \(K\). We denote the restriction of the Lebesgue measure \(d\l_{\C}\) to \(K_{\R}\) by \(d\l_{K_{\R}}\) which is also the Lebesgue measure associated to \(\<\cdot,\cdot\>_{K_{\R}}\). We call \(d\l_{K_{\R}}\) the \textbf{Minkowski measure}\index{Minkowski measure}. Lastly, we denote the restrictions of \(\Trace_{K_{\C}}\) and \(\Norm_{K_{\C}}\) to \(K_{\R}\) by \(\Trace_{K_{\R}}\) and \(\Norm_{K_{\R}}\) respectively which are the norm and trace of \(K_{\R}/\R\). We call \(\Trace_{K_{\R}}\) and \(\Norm_{K_{\R}}\) the \textbf{Minkowski trace}\index{Minkowski trace} and \textbf{Minkowski norm}\index{Minkowski norm} of \(K\) respectively. As the complex \(\Q\)-embeddings of \(K\) into \(\conj{\Q}\) come in conjugate pairs, \(j(K) \subset K_{\R}\) so that the canonical embedding is a \(\Q\)-embedding of \(K\) into Minkowski space. Whence
    \[
      \Trace_{K_{\R}}(j(\k)) = \Trace_{K}(\k) \quad \text{and} \quad \Norm_{K_{\R}}(j(\k)) = \Norm_{K}(\k).
    \]
    So the compositions of the Minkowski trace and Minkowski norm with the canonical embedding produces the field trace and field norm.
    
    To give a more explicit description of Minkowski space, let \(N_{\s} = 1,2\) according to if \(\s\) is real or complex respectively. Also let \(\rho\) and \(\tau\) run over the real \(\Q\)-embeddings and a complete set of representatives for the pairs of complex \(\Q\)-embeddings of \(\Hom_{\Q}(K,\conj{\Q})\) respectively. Note that \(N_{\rho} = 1\) and \(N_{\tau} = 2\). Then
    \[
      K_{\R} = \{\mathbf{z} \in K_{\C}:\Im(z_{\rho}) = 0 \text{ and } z_{\conj{\tau}} = \conj{z_{\tau}} \text{ for all } \rho \text{ and } \tau\}.
    \]
    In fact, this gives an explicit isomorphism between Minkowski space and \(\R^{n}\).
    
    \begin{proposition}\label{prop:Minkowski_space_isomorphism}
      Let \(K\) be a number field of degree \(n\) and signature \((r_{1},r_{2})\). Then the map
      \[
        z_{\s} \mapsto x_{\s} = \begin{cases} z_{\s} & \text{if \(\s = \rho\)}, \\ \Re(z_{\s}) & \text{if \(\s = \tau\)}, \\ \Im(z_{\s}) & \text{if \(\s = \conj{\tau}\)}, \end{cases}
      \]
      induces a component-wise isomorphism between \(K_{\R}\) and \(\R^{n}\) making \(K_{\R}\) a real vector space of dimension \(n\). Moreover, the inner product \(\<\cdot,\cdot\>\) on \(\R^{n}\) induced by the Minkowski inner product is given by
      \[
        \<\mathbf{x},\mathbf{x}'\> = \sum_{\s}N_{\s}x_{\s}x'_{\s},
      \]
      for any \(\mathbf{x},\mathbf{x}' \in \R^{n}\).
    \end{proposition}
    \begin{proof}
      This map has inverse
      \[
        x_{\s} \mapsto z_{\s} = \begin{cases} x_{\s} & \text{if \(\s = \rho\)}, \\ x_{\s}+ix_{\conj{\s}} & \text{if \(\s = \tau\)}, \\ x_{\conj{\s}}+ix_{\s} & \text{if \(\s = \conj{\tau}\)}. \end{cases}
      \]
      As both maps are \(\R\)-linear, it follows that the original map induces a component-wise isomorphism between \(K_{\R}\) and \(\R^{n}\) proving the first statement. For the second statement, let \(\mathbf{z},\mathbf{z}' \in K_{\R}\) and let \(\mathbf{x},\mathbf{x}' \in \R^{n}\) be the corresponding elements in \(\R^{n}\) under this isomorphism respectively. If \(\s = \rho\) then
      \[
        x_{\rho} = z_{\rho} \quad \text{and} \quad x'_{\rho} = z'_{\rho},
      \]
      and thus
      \[
        x_{\rho}x'_{\rho} = z_{\rho}\conj{z'_{\rho}}.
      \]
      If \(\s = \tau\) then
      \[
        x_{\tau} = \Re(z_{\tau}), \quad x_{\conj{\tau}} = \Im(z_{\tau}), \quad x'_{\tau} = \Re(z'_{\tau}), \quad \text{and} \quad x'_{\conj{\tau}} = \Im(z'_{\tau}).
      \]
      Whence a short computation shows
      \[
        2(x_{\tau}x'_{\tau}+x_{\conj{\tau}}x'_{\conj{\tau}}) = z_{\tau}\conj{z'_{\tau}}+z_{\conj{\tau}}\conj{z'_{\conj{\tau}}}.
      \]
      The claim about the inner product follows.
    \end{proof}

    In view of this result, we define the \textbf{Minkowski embedding}\index{Minkowski embedding} \(\s_{K}\) of \(K\) by
    \[
      \s_{K}:K \to \R^{n} \qquad \k \mapsto (\rho(\k))_{\rho} \op (\Re(\tau(\k)),\Im(\tau(\k)))_{\tau}.
    \]
    Note that the Minkowski embedding is a \(\Q\)-embedding of \(K\) into \(\R^{n}\) as it is the composition of the canonical embedding and the isomorphism established in the previous result.
    
    We have now constructed Minkowski space and determined its dimension as a real vector space. Our goal now is to pass from \(\Z\)-lattices of \(K\) to integral lattices of Minkowski space. Being an inner product space, this will permit us to measure fractional ideals of \(K\) geometrically via their images inside Minkowski space. As \(j\) is a \(\Q\)-embedding and any fractional ideal \(\mf{f}\) of \(K\) is a complete \(\Z\)-lattice of \(K\), \(j(\mf{f})\) is a complete integral lattice of \(K_{\R}\). The covolume \(V_{j(\mf{f})}\) of \(j(\mf{f})\) is easily determined.

    \begin{proposition}\label{prop:covolume_of_fractional_ideal_under_j}
      Let \(K\) be a number field with signature \((r_{1},r_{2})\) and let \(\mf{f}\) be a fractional ideal of \(K\). Then \(V_{j(\mf{f})}\) is the absolute value of the determinant of any embedding matrix of a basis for \(K/\Q\) contained in \(\mf{f}\). In particular,
      \[
        V_{j(\mf{f})} = \Norm_{K}(\mf{f})\sqrt{|\D_{K}|},
      \]
      and
      \[
        V_{j(\mc{O}_{K})} = \sqrt{|\D_{K}|}.
      \]
    \end{proposition}
    \begin{proof}
      Upon writing \(\mf{f} = \frac{1}{d}\mf{a}\) for some nonzero \(d \in \Z\) and integral ideal \(\mf{a}\) and \cref{prop:norm_and_field_norms_are_identical}, it suffices to prove the statements for the integral ideal \(\mf{a}\). Let \(\k_{1},\ldots,\k_{n}\) be a basis for \(K/\Q\) contained in \(\mf{a}\). Then the associated generator matrix for \(j(\mf{a})\) is the embedding matrix \(M(\k_{1},\ldots,\k_{n})\). Hence
      \[
        V_{j(\mf{a})} = |\det(M(\k_{1},\ldots,\k_{n}))|,
      \]
      proving the first statement. To prove the first identity of the second statement, in view of \cref{equ:embedding_matrix_discriminant_relation} it suffices to show
      \[
        |\det(M(\k_{1},\ldots,\k_{n}))| = \Norm_{K}(\mf{a})|\det(M(\a_{1},\ldots,\a_{n}))|,
      \]
      for any integral basis \(\a_{1},\ldots,\a_{n}\) for \(K/\Q\). Note that \(\k_{1},\ldots,\k_{n}\) is necessarily a basis for \(\mf{a}\) as a free \(\Z\)-module by \cref{thm:integral_basis_AKBL} and write
      \[
        \k_{i} = \sum_{j}a_{i,j}\a_{j},
      \]
      with \(a_{i,j} \in \Z\). Then \((a_{i,j})\) is the base change matrix from \(\a_{1},\ldots,\a_{n}\) to \(\k_{1},\ldots,\k_{n}\). Whence the image of \(\mc{O}_{K}\) under this matrix is \(\mf{a}\). As \(\Z\) is a principal ideal domain, the smith normal form of this matrix implies that
      \[
        \Norm(\mf{a}) = |\det((a_{i,j}))|.
      \]
      This fact together with \cref{equ:base_change_discriminant,disc_as_square_of_embedding_matrix} gives
      \[
        |\det(M(\k_{1},\ldots,\k_{n}))| = \Norm(\mf{a})|\det(M(\a_{1},\ldots,\a_{n}))|,
      \]
      as claimed. The second identity follows from the first upon taking \(\mf{f} = \mc{O}_{K}\).
    \end{proof}
    
    As \(\s_{K}\) is also a \(\Q\)-embedding, \(\s_{K}(\mf{f})\) is a complete integral lattice in \(\R^{n}\). As a corollary of the previous result, we can determine the covolume of \(V_{\s_{K}(\mf{f})}\) of \(\s_{K}(\mf{f})\) as well.
    
    \begin{corollary}\label{cor:covolume_of_fractional_ideal_under_canonical_embedding}
      Let \(K\) be a number field with signature \((r_{1},r_{2})\) and let \(\mf{f}\) be a fractional ideal of \(K\). Then
      \[
        V_{\s_{K}(\mf{f})} = \Norm_{K}(\mf{f})\frac{\sqrt{|\D_{K}|}}{2^{r_{2}}},
      \]
      and
      \[
        V_{\s_{K}(\mc{O}_{K})} = \frac{\sqrt{|\D_{K}|}}{2^{r_{2}}}.
      \]
    \end{corollary}
    \begin{proof}
      Let \(\k_{1},\ldots,\k_{n}\) be a basis for \(K/\Q\) contained in \(\mf{f}\). Also let \(\rho_{1},\ldots,\rho_{r_{1}}\) and \(\tau_{1},\ldots,\tau_{r_{2}}\) run over the real \(\Q\)-embeddings and a complete set of representatives for the pairs of complex \(\Q\)-embeddings of \(\Hom_{\Q}(K,\conj{\Q})\) respectively. Then the associated generator matrix for \(\s_{K}(\mf{f})\) is
      \[
        \begin{pmatrix} \rho_{1}(\k_{1}) & \cdots & \rho_{r_{1}}(\k_{1}) & \Re(\tau_{1}(\k_{1})) & \Im(\tau_{1}(\k_{1})) & \cdots & \Re(\tau_{r_{2}}(\k_{1})) & \Im(\tau_{r_{2}}(\k_{1})) \\ \vdots & & \vdots & \vdots & \vdots & & \vdots & \vdots \\ \rho_{1}(\k_{n}) & \cdots & \rho_{r_{1}}(\k_{n}) & \Re(\tau_{1}(\k_{n})) & \Im(\tau_{1}(\k_{n})) & \cdots & \Re(\tau_{r_{2}}(\k_{n})) & \Im(\tau_{r_{2}}(\k_{n})) \end{pmatrix}^{t}.
      \]
      By \cref{prop:covolume_of_fractional_ideal_under_j} we are done if the absolute value of the determinant of this matrix is \(\frac{1}{2^{r_{2}}}\) times the absolute value of the determinate of the embedding matrix for \(\k_{1},\ldots,\k_{n}\). To show this, first add an \(i\) multiple of the imaginary columns to their corresponding real columns and then apply the identity \(\Im(z) = \frac{z-\conj{z}}{2i}\) to the imaginary columns. We obtain the matrix
      \[
        \begin{pmatrix} \rho_{1}(\k_{1}) & \cdots & \rho_{r_{1}}(\k_{1}) & \tau_{1}(\k_{1}) & \frac{\tau_{1}(\k_{1})-\conj{\tau_{1}}(\k_{1})}{2i} & \cdots & \tau_{r_{2}}(\k_{1}) & \frac{\tau_{r_{2}}(\k_{1})-\conj{\tau_{r_{2}}}(\k_{1})}{2i} \\ \vdots & & \vdots & \vdots & \vdots & & \vdots & \vdots \\ \rho_{1}(\k_{n}) & \cdots & \rho_{r_{1}}(\k_{n}) & \tau_{1}(\k_{n}) & \frac{\tau_{1}(\k_{n})-\conj{\tau_{1}}(\k_{n})}{2i} & \cdots & \tau_{r_{2}}(\k_{n}) & \frac{\tau_{r_{2}}(\k_{n})-\conj{\tau_{r_{2}}}(\k_{n})}{2i} \end{pmatrix}^{t},
      \]
      which has the same determinant as the generator matrix. Now multiply the imaginary columns by \(-2i\) and then adding the preceding columns to annihilate the negative terms. This results in the matrix
      \[
        \begin{pmatrix} \rho_{1}(\k_{1}) & \cdots & \rho_{r_{1}}(\k_{1}) & \tau_{1}(\k_{1}) &\conj{\tau_{1}}(\k_{1}) & \cdots & \tau_{r_{2}}(\k_{1}) & \conj{\tau_{r_{2}}}(\k_{1}) \\ \vdots & & \vdots & \vdots & \vdots & & \vdots & \vdots \\ \rho_{1}(\k_{n}) & \cdots & \rho_{r_{1}}(\k_{n}) & \tau_{1}(\k_{n}) & \conj{\tau_{1}}(\k_{n}) & \cdots & \tau_{r_{2}}(\k_{n}) & \conj{\tau_{r_{2}}}(\k_{n}) \end{pmatrix}^{t},
      \]
      whose determinant is \((-2i)^{-r_{2}}\) that of the generator matrix. But this latter matrix is the embedding \(M(\k_{1},\ldots,\k_{n})\). Whence
      \[
        V_{\s_{K}(\mf{f})} = \frac{|\det(M(\k_{1},\ldots,\k_{n}))|}{2^{r_{2}}}.
      \]
    \end{proof}
  \section{\todo{Finiteness of the Class Number}}
    Recall that the class number of a Dedekind domain is a measure of how much the Dedekind domain fails to be a principal ideal domain and even need not be finite from \cref{rem:general_class_number_not_finite}. However, we will show that the class number \(h_{K}\) for a number field \(K\) is always finite and thus \(\mc{O}_{K}\) only has finite failure from being a principal ideal domain. In doing so, we will also show that every ideal class contains an integral ideal of bounded norm.

    \begin{theorem}\label{equ:finitness_of_class_number}
      Let \(K\) be a number field of degree \(n\) and signature \((r_{1},r_{2})\). Also, let \(X \subseteq \R^{n}\) be a compact convex symmetric set and set \(M = \max_{\mathbf{x} \in X}\left(\prod_{i}|x_{i}|\right)\). Then every ideal class contains an integral ideal \(\mf{a}\) satisfying
      \[
        \Norm_{K}(\mf{a}) \le \frac{2^{r_{1}+r_{2}}M}{\Vol(X)}\sqrt{|\D_{K}|}.
      \]
      Moreover, the class number \(h_{K}\) is finite which is to say the ideal class group \(\Cl(K)\) is.
    \end{theorem}
    \iffalse
    \begin{proof}
      Let \(\mf{f}\) be a fractional ideal, \(n\) be a positive integer, and set
      \[
        \l^{n} = 2^{n}\frac{V_{\s_{K}(\mf{f}^{-1})}}{\Vol(X)}.
      \]
      Then by construction,
      \[
        \Vol(\l X) = \l^{n}\Vol(X) = 2^{n}V_{\s_{K}(\mf{f}^{-1})}.
      \]
      By Minkowski's lattice point theorem, there exists a nonzero \(\a \in \mf{f}^{-1}\) such that \(\s_{K}(\a) \in \s_{K}(\mf{f}^{-1})\) and \(\s_{K}(\a) \in \l X\). Since \(\a \in \mf{f}^{-1}\), \(\a\mf{f} \subseteq \mc{O}_{K}\) so that \(\a\mf{f}\) is an integral ideal in the same ideal class as \(\mf{f}\). Now let \(\s\) run over \(\Hom_{\Q}(K,\conj{\Q})\). Since the norm is multiplicative, we have
      \[
        \Norm_{K}(\a\mf{f}) = |\Norm_{K}(\a)|\Norm_{K}(\mf{f}) = \left|\prod_{\s}\s(\a)\right|\Norm_{K}(\mf{f}) \le \l^{n}M\Norm_{K}(\mf{f}),
      \]
      where in the first equality we have applied multiplicativity of the norm and \cref{prop:norm_and_field_norms_are_identical}, in the second we have used \cref{prop:formulas_for_trace_and_norm}, and the inequality follows since \(\s_{K}(\a) \in \l X\). This inequality, our choice of \(\l^{n}\), and \cref{cor:covolume_of_fractional_ideal_under_canonical_embedding} together give
      \[
        \Norm_{K}(\a\mf{f}) \le \l^{n}M\Norm_{K}(\mf{f}) = 2^{n}M\Norm_{K}(\mf{f})\frac{V_{\s_{K}(\mf{f}^{-1})}}{\Vol(X)} = 2^{n}M\frac{\sqrt{|\D_{K}|}}{2^{r_{2}}\Vol(X)} = \frac{2^{r_{1}+r_{2}}M}{\Vol(X)}\sqrt{|\D_{K}|},
      \]
      which proves the first statement since the fractional ideal \(\mf{f}\) was arbitrary. We now prove that the class group is finite. By what we have just proved, we can find a complete set of representatives for \(\Cl(K)\) consisting of integral ideals of bounded norm. Since the norm is multiplicative, the prime factors of these representatives have bounded norm as well. As we have seen, the norm of a prime integral ideal is exactly the prime \(p\) below it. Thus the norms of these prime factors are bounded primes \(p\). As there are finitely many prime integral ideals above any prime \(p\) (because \(p\mc{O}_{K}\) factors into a product of prime integral ideals and these are exactly the prime integral ideals above \(p\)), it follows that these representatives have finitely many prime factors. Altogether this means that there are finitely many representatives. Hence \(\Cl(K)\) is finite and so the class number \(h_{K}\) is too.
    \end{proof}

    We would like to obtain an explicit bound in \cref{equ:finitness_of_class_number} by making a choice for the set \(X\). To obtain a bound that is not too large, we need to ensure that the volume of \(X\) is large while the constant \(M\) is small. The following lemma dictates our choice of \(X\) and computes its volume:

    \begin{lemma}\label{lem:Minkowski_bound_lemma}
      Suppose \(n\) is a positive integer and write \(n = r_{1}+2r_{2}\) for some nonnegative integers \(r_{1}\) and \(r_{2}\). Let \(X \subset \R^{n}\) to be the compact convex symmetric set given by
      \[
        X = \left\{\mathbf{x} \in \R^{n}:\sum_{1 \le i \le r_{1}}|x_{i}|+2\sum_{\substack{1 \le j \le r_{2} \\ j \equiv 1 \tmod{2}}}\sqrt{x_{r_{1}+j}^{2}+x_{r_{1}+j+1}^{2}} \le n\right\}.
      \]
      Then
      \[
        \Vol(X) = \frac{n^{n}}{n!}2^{r_{1}}\left(\frac{\pi}{2}\right)^{r_{2}}.
      \]
    \end{lemma}
    \begin{proof}
      Making the change of variables \(x_{r_{1}+j} \mapsto u_{j}\sin(\t_{j})\) and \(x_{r_{1}+j+1} \mapsto u_{j}\cos(\t_{j})\) for all \(j\) gives
      \[
        \Vol(X) = \int_{X'}u_{1} \cdots u_{r_{2}}\,dx_{1} \cdots dx_{r_{1}}\,du_{1}\t_{1} \cdots du_{r_{2}}\t_{r_{2}},
      \]
      where
      \[
        X' = \left\{(x_{1},\ldots,x_{r_{1}},u_{1},\t_{1},\ldots,u_{r_{2}},\t_{r_{2}}):\sum_{1 \le i \le r_{1}}|x_{i}|+2\sum_{1 \le j \le r_{2}}u_{j} \le n\right\}.
      \]
      Since the integrand is independent of the \(\t_{j}\), we have
      \[
        \Vol(X) = (2\pi)^{r_{2}}\int_{X'}u_{1} \cdots u_{r_{2}}\,dx_{1} \cdots dx_{r_{1}}\,du_{1} \cdots du_{r_{2}}.
      \]
      Making the change of variables \(u_{j} \mapsto \frac{u_{j}}{2}\) for all \(j\) and using the fact that the integrand is symmetric in the \(x_{i}\) for all \(i\) gives
      \begin{equation}\label{equ:Minkowski_bound_lemma_1}
        \Vol(X) = 2^{r_{1}}\left(\frac{\pi}{2}\right)^{r_{2}}\int_{X''}u_{1} \cdots u_{r_{2}}\,dx_{1} \cdots dx_{r_{1}}\,du_{1} \cdots du_{r_{2}},
      \end{equation}
      where
      \[
        X'' = \left\{(x_{1},\ldots,x_{r_{1}},u_{1},\ldots,u_{r_{2}}):\sum_{1 \le i \le r_{1}}x_{i}+\sum_{1 \le j \le r_{2}}u_{j} \le n\right\}.
      \]
      To compute the remaining integral, for nonnegative integers \(\ell\) and \(k\) and \(t \ge 0\), we let
      \[
        X''_{\ell,k}(t) = \left\{(x_{1},\ldots,x_{\ell},u_{1},\ldots,u_{k}):\sum_{1 \le i \le \ell}x_{i}+\sum_{1 \le j \le k}u_{j} \le t\right\},
      \]
      and set 
      \[
        I_{\ell,k}(t) = \int_{X''_{\ell,k}(t)}u_{1} \cdots u_{\ell}\,dx_{1} \cdots dx_{n}\,du_{1} \cdots du_{k}.
      \]
      Then we have to compute \(I_{r_{1},r_{2}}(n)\). To this end, the change of variables \(x_{i} \mapsto tx_{i}\) and \(u_{j} \mapsto tu_{j}\) for all \(i\) and \(j\) gives
      \begin{equation}\label{equ:Minkowski_bound_lemma_2}
        I_{\ell,k}(t) = t^{\ell+2k}I_{\ell,k}(1).
      \end{equation}
      Now note that the condition
      \[
        \sum_{1 \le i \le \ell}x_{i}+\sum_{1 \le j \le k}u_{j} \le t,
      \]
      is equivalent to
      \[
        \sum_{1 \le i \le \ell-1}x_{i}+\sum_{1 \le j \le k}u_{j} \le t-x_{i}.
      \]
      This fact together with the Fubini–Tonelli theorem and \cref{equ:Minkowski_bound_lemma_2} gives
      \[
        I_{\ell,k}(1) = \int_{0}^{1}I_{\ell-1,k}(1-x_{\ell})\,dx_{\ell} = \int_{0}^{1}(1-x_{\ell})^{\ell-1+2k}I_{\ell-1,k}(1)\,dx_{\ell} = \frac{1}{\ell+2k}I_{\ell-1,k}(1).
      \]
      Repeating this procedure \(\ell-1\) times results in
      \begin{equation}\label{equ:Minkowski_bound_lemma_3}
        I_{\ell,k}(1) = \frac{1}{(\ell+2k) \cdots (2k+1)}I_{0,k}(1).
      \end{equation}
      Similarly, the condition
      \[
        \sum_{1 \le j \le k}u_{j} \le t,
      \]
      is equivalent to
      \[
        \sum_{1 \le j \le k-1}u_{j} \le t-u_{k}.
      \]
      This fact together with the Fubini–Tonelli theorem, \cref{equ:Minkowski_bound_lemma_2}, and \cref{prop:integral_reprepsentation_for_beta_function}, gives
      \[
        I_{0,k}(1) = \int_{0}^{1}u_{k}I_{0,k-1}(1-u_{k})\,du_{k} = \int_{0}^{1}u_{k}(1-u_{k})^{2k-2}I_{0,k-1}(1)\,du_{k} = B(1,2k-1)I_{0,k-1}(1) = \frac{1}{2k}I_{0,k-1}(1).
      \]
      Repeating this procedure \(k-1\) times results in
      \begin{equation}\label{equ:Minkowski_bound_lemma_4}
        I_{0,k}(1) = \frac{1}{k!},
      \end{equation}
      since \(I_{0,0}(1) = 1\). Combining \cref{equ:Minkowski_bound_lemma_2,equ:Minkowski_bound_lemma_3,equ:Minkowski_bound_lemma_4} we find that
      \[
        I_{\ell,k}(t) = t^{\ell+2k}\frac{1}{(\ell+2k)!}.
      \]
      In particular, \(I_{r_{1},r_{2}}(n) = \frac{n^{n}}{n!}\) and from \cref{equ:Minkowski_bound_lemma_1} we obtain
      \[
        \Vol(X) = \frac{n^{n}}{n!}2^{r_{1}}\left(\frac{\pi}{2}\right)^{r_{2}},
      \]
      as desired.
    \end{proof}

    Observe that the set \(X\) in \cref{lem:Minkowski_bound_lemma} just consists of those points in \(\R^{n}\) whose induced norm corresponding to the induced Minkowski inner product is at most \(n\) (recall \cref{prop:Minkowski_space_isomorphism}). We can now obtain an explicit bound in \cref{equ:finitness_of_class_number} known as the \textbf{Minkowski bound}\index{Minkowski bound}:

    \begin{theorem*}[Minkowski bound]
      Let \(K\) be a number field of degree \(n\) and signature \((r_{1},r_{2})\). Then every ideal class contains an integral ideal \(\mf{a}\) satisfying
      \[
        \Norm_{K}(\mf{a}) \le \left(\frac{4}{\pi}\right)^{r_{2}}\frac{n!}{n^{n}}\sqrt{|\D_{K}|}.
      \]
    \end{theorem*}
    \begin{proof}
      Let \(X\) be given by
      \[
        X = \left\{\mathbf{x} \in \R^{n}:\sum_{1 \le i \le r_{1}}|x_{i}|+2\sum_{\substack{1 \le j \le r_{2} \\ j \equiv 1 \tmod{2}}}\sqrt{x_{r_{1}+j}^{2}+x_{r_{1}+j+1}^{2}} \le n\right\}.
      \]
      Then \cref{equ:finitness_of_class_number,lem:Minkowski_bound_lemma} together show that every ideal class contains an integral ideal \(\mf{a}\) such that
      \[
        \Norm_{K}(\mf{a}) \le M\left(\frac{4}{\pi}\right)^{r_{2}}\frac{n!}{n^{n}}\sqrt{|\D_{K}|},
      \]
      where \(M = \max_{\mathbf{x} \in X}\left(\prod_{1 \le \ell \le n}|x_{\ell}|\right)\). But for all \(\mathbf{x} \in X\), the arithmetic-geometric mean inequality gives
      \[
        \left(\prod_{1 \le \ell \le n}|x_{\ell}|\right)^{\frac{1}{n}} \le \frac{1}{n}\sum_{1 \le \ell \le n}|x_{\ell}| \le 1,
      \]
      where the second inequality holds by the definition of \(X\). Hence \(M \le 1\) and this completes the proof.
    \end{proof}

    As a corollary we can obtain a lower bound for the discriminant of a number field and show that every number field \(K\), other than \(\Q\), has at least one ramified prime in \(\mc{O}_{K}/\Z\):

    \begin{corollary}
      Let \(K\) be a number field of degree \(n\). Then
      \[
        |\D_{K}| \ge \left(\frac{\pi}{4}\right)^{\frac{n}{2}}\frac{n^{n}}{n!}.
      \]
      In particular, there is at least one ramified prime in \(\mc{O}_{K}/\Z\) provided the degree of \(K\) is at least \(2\). 
    \end{corollary}
    \begin{proof}
      Since the norm of every integral ideal is at least \(1\), \(\pi < 4\), and \(r_{2}\) is at most \(n\), the desired inequality follows immediately from the Minkowski bound. Now suppose \(n \ge 2\). In the case \(n = 2\), the lower bound is larger than \(1\) so that \(|\D_{K}|\) is at least \(2\) for every quadratic number field. As \(n^{n} \ge n!\) for all \(n \ge 1\) (which easily follows by induction), \(\left(\frac{\pi}{4}\right)^{\frac{n}{2}}\frac{n^{n}}{n!}\) is an increasing function in \(n\). Therefore \(|\D_{K}| \ge 2\) for all \(n \ge 2\) so that \(|\D_{K}|\) has a prime divisor. This means at least one prime of \(K\) ramifies in \(\mc{O}_{K}/\Z\).
    \end{proof}

    Generally speaking, the class number \(h_{K}\) is one of the most difficult pieces of arithmetic data about \(K\) to compute. For example, it is still unknown if there are infinitely many number fields of class number \(1\), that is, number fields such that their ring of integers are principal ideal domains.
  \fi\section{\todo{Dirichlet's Unit Theorem}}\iffalse
    Let \(K\) be a number field of signature \((r_{1},r_{2})\). We define the \textbf{rank}\index{rank} \(r_{K}\) of \(K\) to be
    \[
      r_{K} = r_{1}+r_{2}-1.
    \]
    This will be an important in the following. Another very important piece of arithmetic data about \(K\) is the structure of the unit group \(\mc{O}_{K}^{\ast}\). Note that \(\mc{O}_{K}^{\ast}\) is closed under conjugation because \(\Norm_{K}(\a) = \Norm_{K}(\conj{\a})\) as a consequence of \cref{prop:formulas_for_trace_and_norm}. Moreover, since the norm of a unit is \(\pm1\), we can express the unit group as
    \[
      \mc{O}_{K}^{\ast} = \{\e \in \mc{O}_{K}:\Norm_{K}(\e) = \pm 1\}.
    \]
    Our main goal will be to describe the group structure of \(\mc{O}_{K}^{\ast}\) completely. Let \(\W\) denote the group of all roots of unity. We will set \(\mu(K) = \mc{O}_{K}^{\ast} \cap \W\) so that \(\mu(K)\) is the subgroup of \(\mc{O}_{K}^{\ast}\) consisting of all of the roots of unity in \(K\). Clearly \(\{\pm 1\} \subseteq \mu(K)\). In fact, \(\mu(K)\) is finite since any root of unity in \(K\) is a root of \(x^{n}-1\) and thus an \(n\)-th root of unity. We set
    \[
      w_{K} = |\mu(K)|.
    \]
    Our goal will be to show that \(\mc{O}_{K}^{\ast}\) is a direct product of \(\mu(K)\) and a free abelian group of rank \(r_{K}\). Determining that the rank of the free group is exactly \(r_{K}\) will be the most difficult part of the proof. We will require a map on \(K^{\ast}\) that transitions between the field trace and the field norm. Let \(\rho_{1},\ldots,\rho_{r_{1}}\) be the real \(\Q\)-embeddings of \(\Hom_{\Q}(K,\conj{\Q})\) and \(\tau_{1},\ldots,\tau_{r_{2}}\) run over a complete set of representatives for the pairs of complex \(\Q\)-embeddings of \(\Hom_{\Q}(K,\conj{\Q})\). First consider the map
    \[
      \ell:K_{\R}^{\ast} \to \R^{r_{K}+1} \qquad (z_{\s})_{\s} \mapsto (\log|z_{\rho_{1}}|,\ldots,\log|z_{\rho_{r_{1}}}|,2\log|z_{\tau_{1}}|,\ldots,2\log|z_{\tau_{r_{2}}}|).
    \]
    This map is independent of the choice of representatives \(\tau_{1},\ldots,\tau_{r_{2}}\) because \(z_{\conj{\tau}} = \conj{z_{\tau}}\) for \(\mathbf{z} \in K_{\R}\).
    We define the \textbf{logarithmic embedding}\index{logarithmic embedding} \(\log_{K}\) of \(K\) by
    \[
      \log_{K}:K^{\ast} \to \R^{r_{K}+1} \qquad \k \mapsto (\log|\rho_{1}(\k)|,\ldots,\log|\rho_{r_{1}}(\k)|,2\log|\tau_{1}(\k)|,\ldots,2\log|\tau_{r_{2}}(\k)|).
    \]
    Then \(\log_{K}\) is just the restriction of \(j\) to \(K^{\ast}\) composed with \(\ell\). Since \(\ell\) is a homomorphism and \(j\) is a \(\Q\)-embedding, \(\log_{K}\) is a homomorphism. We distinguish the subsets
    \[
      S = \{\mathbf{x} \in  \R_{+}^{r_{K}+1}:\Norm_{\R^{r_{K}+1}/\R}(\mathbf{x}) = 1\} \quad \text{and} \quad H = \{\mathbf{x} \in \R^{r_{K}+1}:\Trace_{\R^{r_{K}+1}/\R}(\mathbf{x}) = 0\},
    \]
    called the \textbf{norm-one hypersurface}\index{norm-one hypersurface} and \textbf{trace-zero hyperplane}\index{trace-zero hyperplane} of \(\R^{r_{K}+1}\) respectively. Note that \(H\) is an \(r_{K}\)-dimensional subspace of \(\R^{r_{K}+1}\). We will also make use of the subset
    \[
      U = \{\mathbf{z} \in K_{\R}:\Norm_{K_{\R}}(\mathbf{z}) = \pm 1\}.
    \]
    Let \(\l\) denote the restriction of \(\log_{K}\) to \(\mc{O}_{K}^{\ast}\) and set
    \[
      \L = \log_{K}(\mc{O}_{K}^{\ast}),
    \]
    so that \(\L\) is the image of \(\l\). We call \(\L\) the \textbf{unit lattice}\index{unit lattice} of \(K\). It is not immediately obvious that \(\L\) is a lattice, but we will show this and more. Observe that \(\ell\) takes \(U\) into \(H\) since \(\Trace_{\R^{r_{K}+1}/\R}(\ell(\mathbf{z})) = \log|\Norm_{K_{\R}}(\mathbf{z})| = 1\). In particular, \(\L \subset H\) since \(j(\mc{O}_{K}^{\ast}) \subset U\). All of this data can be collected into the following commutative diagram:

    \begin{center}
      \begin{tikzcd}[row sep=large, column sep=large]
        \mc{O}_{K}^{\ast} \arrow{d} \arrow{r}{j} \arrow[bend left]{rr}{\log_{K}} & U \arrow{d} \arrow{r}{\ell} & H \arrow{d} \\
        K^{\ast} \arrow{d}{\Norm} \arrow{r}{j} & K_{\R} \arrow{d}{\Norm_{K_{\R}}}^{\ast} \arrow{r}{\ell} & \R^{r_{K}+1} \arrow{d}{\Trace_{\R^{r_{K}+1}/\R}} \\
        \Q^{\ast} \arrow{r} & \R^{\ast} \arrow{r}{\log|\phantom{\cdot}|} & \R.
      \end{tikzcd}
    \end{center}
    We first show that the logarithmic embedding fits into an exact sequence:

    \begin{proposition}\label{prop:exact_sequence_for_Dirichlets_unit_theorem}
      Let \(K\) be a number field. Then the sequence

      \begin{center}
        \begin{tikzcd}[row sep=large, column sep=large]
          1 \arrow{r} & \mu(K) \arrow{r} & \mc{O}_{K}^{\ast} \arrow{r}{\l} & \L \arrow{r} & 0,
        \end{tikzcd}
      \end{center}

      is exact.
    \end{proposition}
    \begin{proof}
      Exactness of this sequence means that \(\mu(K)\) is the kernel of \(\l\). If \(\w \in \mu(K)\) then \(|\w| = 1\) and it follows that \(\l(\w) = 0\). Therefore \(\ker\l\) contains \(\mu(K)\). To see that this is all of \(\ker\l\), suppose \(\e \in \mc{O}_{K}^{\ast}\) is such that \(\l(\e) = 0\). But then every component of \(j(\e)\) is has absolute value \(1\) and therefore belongs to a bounded subset of the Minkowski space \(K_{\R}\). Since \(\mc{O}_{K}^{\ast}\) is a subgroup of \(\mc{O}_{K}\) and \(j(\mc{O}_{K})\) is a complete lattice in \(K_{\R}\) (as we have already remarked), \(j(\mc{O}_{K}^{\ast})\) is a lattice in \(K_{\R}\). But then \(j(\e)\) belongs to a discrete set by \cref{prop:integral lattice_if_and_only_if_discrete_subgroup}. Together, \(j(\e)\) belongs to a discrete and bounded set and hence is necessarily finite. Since \(j\) is a \(\Q\)-embedding, it follows that the subgroup \(\ker\l\) of \(\mc{O}_{K}^{\ast}\) contains finitely many elements and hence only roots of unity because \(\ker\l \subset K \subset \C\). Thus \(\ker\l = \mu(K)\).
    \end{proof}

    Our aim now is to show that the unit lattice \(\L\) is a a free abelian group of rank \(r_{K}\). For this, we will require a lemma:

    \begin{lemma}\label{lem:finitely_many_elements_of_fixed_norm}
      Let \(K\) be a number field. There are finitely many elements in \(\mc{O}_{K}\) of a given norm up to multiplication by units.
    \end{lemma}
    \begin{proof}
      Recall that the norm of an algebraic integer is an integer and that the elements of norm \(\pm1\) are exactly the units of \(K\). Therefore it suffices to prove the claim for norm \(n \ge 2\) (the norm is only zero for zero itself). Further recall that \(\mc{O}_{K}/n\mc{O}_{K}\) is finite (with \(\Norm_{K}(n\mc{O}_{K})\) many elements). Therefore, it suffices to show that in each coset there is at most one element of norm \(n\) up to multiplication by units. To show this, suppose \(\a\) and \(\b\) are two representatives in the same coset and are of norm \(n\). Writing \(\a = \b+n\g\) for some \(n\g \in n\mc{O}_{K}\), we have
      \[
        \frac{\a}{\b} = 1+\frac{n}{\b}\g = 1+\frac{\Norm_{K}(\b)}{\b}\g,
      \]
      which is an element of \(\mc{O}_{K}\) because \(\frac{\Norm_{K}(\b)}{\b}\) is since \(\Norm_{K}(\b) \in \b\mc{O}_{K}\) as any integral ideal contains it norm. Hence \(\frac{\a}{\b} \in \mc{O}_{K}\), and interchanging the roles of \(\a\) and \(\b\) shows that \(\frac{\b}{\a} \in \mc{O}_{K}\) too. But then \(\frac{\a}{\b}\) is a unit in \(\mc{O}_{K}\) and thus \(\a\) and \(\b\) differ up to multiplication by a unit.
    \end{proof}

    Recall that \(\L \subset H\). We will show \(\L\) is a lattice in \(H\), actually a complete lattice, and compute its rank as a free abelian group:

    \begin{theorem}\label{thm:unit_group_complete_lattice}
      Let \(K\) be a number field of degree \(n\) and signature \((r_{1},r_{2})\). Then the unit lattice \(\L\) is a complete lattice in the trace-zero hyperplane \(H\) of \(\R^{r_{K}+1}\). In particular, \(\L\) is a free abelian group of rank \(r_{K}\).
    \end{theorem}
    \begin{proof}
      Throughout, let \(\s\) run over \(\Hom_{\Q}(K,\conj{\Q})\), \(\rho\) run over all such real \(\Q\)-embeddings, and \(\tau\) run over a complete set of representatives for the pairs of complex \(\Q\)-embeddings. We first prove \(\L\) is a lattice in \(H\). Since \(\l\) is a homomorphism (because \(\log_{K}\) is), \(\L\) is a subgroup of \(H\). So by \cref{prop:integral lattice_if_and_only_if_discrete_subgroup}, \(\L\) is a lattice if and only if it is discrete. In particular, we will show that for any \(c > 0\), the bounded region
      \[
        X = \{\mathbf{x} \in \R^{r_{K}+1}:|x_{\rho}| \le c \text{ and } |x_{\tau}| \le 2c \text{ for all } \rho \text{ and } \tau\},
      \]
      contains only finitely many points of \(\L\). The preimage of \(X\) under \(\ell\) is
      \[
        \ell^{-1}(X) = \{\mathbf{z} \in K_{\R}:e^{-c} \le |z_{\s}| \le e^{c} \text{ for all } \s\},
      \]
      and hence it contains finitely many points of \(j(\mc{O}_{K}^{\ast})\) because this is a subset of the lattice \(j(\mc{O}_{K})\). It follows that \(X\) contains finitely many points of \(\L\) (as the preimage of \(\mathbf{x}\) in \(\R^{n}\) under \(\ell\) contains \(2^{n}\) points of \(K_{\R}\)) so that \(\L\) is discrete and thus a lattice. We will now show that \(\L\) is a complete lattice in \(H\) and since \(H\) is an \(r_{K}\)-dimensional real vector space, this will also prove the claim about the rank of \(\L\). By \cref{prop:complete_integral lattice_if_and_only_if_bounded_translates_cover} it suffices to show that there is a bounded subset \(M\) of the trace-zero hyperplane \(H\) whose translates by \(\L\) cover \(H\). Actually, since \(\ell\) is surjective it suffices to construct a bounded subset \(T\) of \(U\) such that
      \[
        U = \bigcup_{\e \in \mc{O}_{K}^{\ast}}j(\e)T.
      \]
      Indeed, if such \(T\) exists then any \(\mathbf{z} \in T\) satisfies \(|\Norm_{K_{\R}}(\mathbf{z})| = \prod_{\s}|z_{\s}| = 1\) and hence each \(z_{\s}\) is bounded above and away from zero because \(T\) is bounded. Setting \(M = \ell(T)\), it follows that \(M\) is also bounded (because \(\log|z|\) is continuous) and
      \[
        H = \bigcup_{\l}(M+\l).
      \]
      It now suffices to construct such a subset \(T\). For every \(\s\), fix constants \(c_{\s} > 0\) satisfying
      \[
        c_{\s} = c_{\conj{\s}} \quad \text{and} \quad \prod_{\s}c_{\s} > \left(\frac{2}{\pi}\right)^{r_{2}}\sqrt{|D_{K}|},
      \]
      and set \(C = \prod_{\s}c_{\s}\). Now consider the bounded subset
      \[
        Z = \{\mathbf{z} \in K_{\R}:|z_{\s}| < c_{\s} \text{ for all } \s\}.
      \]
      For any \(\mathbf{w} \in U\), we have
      \[
        \mathbf{w}Z = \{\mathbf{z} \in K_{\R}:|z_{\s}| < |w_{\s}|c_{\s} \text{ for all } \s\},
      \]
      and \(\prod_{\s}|w_{\s}|c_{\s} = \Norm_{K_{\R}}(\mathbf{w})C = C\) so that \(\mathbf{w}Z\) is also bounded. By \cref{prop:Minkowski_space_isomorphism}, the volume of \(\mathbf{w}Z\) is \(2^{r_{2}}\) times the volume of
      \[
        X = \{\mathbf{x} \in \R^{n}:|x_{\rho}| < c_{\rho} \text{ and } x_{\tau}^{2}+x_{\conj{\tau}}^{2} < c_{\tau}^{2} \text{ for all } \rho \text{ and } \tau\},
      \]
      which is \(\prod_{\rho}(2c_{\rho})\prod_{\tau}(\pi c_{\tau}^{2}) = C2^{r_{1}}\pi^{r_{2}}\) because \(X\) is the product of \(r_{1}\) many intervals each of length \(2c_{\rho}\) and \(r_{2}\) many disks each of of radius \(c_{\tau}\). Thus \(\Vol(\mathbf{w}Z) = C2^{r_{K}+1}\pi^{r_{2}}\). By \cref{prop:covolume_of_fractional_ideal_under_j}, \(V_{j(\mc{O}_{K})} = \sqrt{|D_{K}|}\) and our choice of \(C\) gives
      \[
        \Vol(\mathbf{w}Z) > 2^{n}V_{j(\mc{O}_{K})}.
      \]
      Since \(j(\mc{O}_{K})\) is a complete lattice in \(K_{\R}\), Minkowski's lattice point theorem implies that there exists some nonzero \(\a \in \mc{O}_{K}\) such that \(j(\a) \in \mathbf{w}Z\). Now by \cref{lem:finitely_many_elements_of_fixed_norm}, there exist finitely many nonzero elements \(\a_{1},\ldots,\a_{m}\) of \(\mc{O}_{K}\) such that every \(\a \in \mc{O}_{K}\) with \(0 < \Norm_{K}(\a) \le C\) is equal to \(\a_{i}\) for some \(1 \le i \le m\) by multiplying by a unit. Set
      \[
        T = U \cap \left(\bigcup_{1 \le i \le m}j(\a_{i})^{-1}Z\right).
      \]
      Then \(T\) is a bounded subset of \(U\) since \(Z\) is a bounded subset of \(K_{\R}\) (and thus the \(j(\a_{i})^{-1}Z\) are too). We now claim that
      \[
        U = \bigcup_{\e \in \mc{O}_{K}^{\ast}}j(\e)T.
      \]
      Indeed, since \(\mathbf{w}^{-1} \in U\) for any \(\mathbf{w} \in U\)  we have shown implies that there exists a nonzero \(\a \in \mc{O}_{K}\) such that \(j(\a) \in \mathbf{w}^{-1}Z\). Hence \(j(\a) = \mathbf{w}^{-1}\mathbf{z}\) for some \(\mathbf{z} \in Z\). But as
      \[
        |\Norm_{K}(\a)| = |\Norm_{K_{\R}}(j(\a))| = |\Norm_{K_{\R}}(\mathbf{w}^{-1}\mathbf{z})| = |\Norm_{K_{\R}}(\mathbf{z})| < C,
      \]
      it follows that there exists an \(\a_{i}\) and \(\e \in \mc{O}_{K}^{\ast}\) such that \(\a_{i} = \a\e\). Writing \(\mathbf{w} = j(\a)^{-1}\mathbf{z}\) (recall that \(K_{\R}\) is commutative), we have 
      \[
        \mathbf{w} = j(\a)^{-1}\mathbf{z} = j(\a_{i}\e^{-1})^{-1}\mathbf{z} = j(\e)j(\a_{i})^{-1}\mathbf{z},
      \]
      where the last equality holds because \(j\) is a \(\Q\)-embedding. As \(\mathbf{w},j(\e) \in U\), we see that \(j(\a_{i})^{-1}\mathbf{z} \in U\) and thus \(j(\a_{i})^{-1}\mathbf{z} \in T\). But then \(\mathbf{w} \in j(\e)T \subset U\) as desired.
    \end{proof}

    By \cref{thm:unit_group_complete_lattice}, there exist elements \(\e_{1},\ldots,\e_{r_{K}}\) of \(\mc{O}_{K}^{\ast}\) such that \(\l(\e_{1}),\ldots,\l(\e_{r_{K}})\) is a basis for the unit lattice \(\L\) by taking the preimage under \(j\) of any basis for \(\L\). We say that \(\e_{1},\ldots,\e_{r_{K}}\) are a \textbf{system of fundamental units}\index{system of fundamental units} of \(K\) and we call any such element a \textbf{fundamental unit}\index{fundamental unit} for \(K\). The structure theorem for \(\mc{O}_{K}^{\ast}\) known as \textbf{Dirichlet's unit theorem}\index{Dirichlet's unit theorem} says that \(\mc{O}_{K}^{\ast}\) is a product of a root of unity in \(K\) and powers of fundamental units:

    \begin{theorem*}[Dirichlet's unit theorem]
      Let \(K\) be a number field of signature \((r_{1},r_{2})\). Then
      \[
        \mc{O}_{K}^{\ast} \cong \mu(K) \x \Z^{r_{K}}.
      \]
      In particular, if \(\e_{1},\ldots,\e_{r_{K}}\) is a system of fundamental units for \(K\) then any unit \(\e\) of \(K\) is of the form
      \[
        \e = \w\e_{1}^{\nu_{1}} \cdots \e_{r_{K}}^{\nu_{r_{K}}},
      \]
      for some \(\w \in \mu(K)\) and \(\nu_{i} \in \Z\) for \(1 \le i \le r_{K}\).
    \end{theorem*}
    \begin{proof}
      By \cref{prop:exact_sequence_for_Dirichlets_unit_theorem} we have an exact sequence

      \begin{center}
        \begin{tikzcd}[row sep=large, column sep=large]
          1 \arrow{r} & \mu(K) \arrow{r} & \mc{O}_{K}^{\ast} \arrow{r}{\l} & \L \arrow{r} & 0,
        \end{tikzcd}
      \end{center}

      and by \cref{thm:unit_group_complete_lattice} we know that \(\L\) is a free abelian group of rank \(r_{K}\). Let \(\e_{1},\ldots,\e_{r_{K}}\) be a system of fundamental units for \(K\) and let \(E\) be the subgroup of \(\mc{O}_{K}^{\ast}\) generated by them. Then \(\l\) induces an isomorphism between \(E\) and \(\L\) so that \(\mu(K) \cap E = \{1\}\) because the sequence is exact. As \(\mu(K)\) and \(E\) are subgroups, \(\mu(K) \cap E = \{1\}\) implies \(\mc{O}_{K}^{\ast} \cong \mu(K) \x E\). Since \(E \cong \Z^{r_{K}}\) (because \(\L \cong \Z^{r_{K}}\)), we have \(\mc{O}_{K}^{\ast} \cong \mu(K) \x \Z^{r_{K}}\). Moreover, from the isomorphism \(E \cong \Z^{r_{K}}\) we see that any element of \(E\) is of the form \(\e_{1}^{\nu_{1}} \cdots \e_{r_{K}}^{\nu_{r_{K}}}\) with \(\nu_{i} \in \Z\) for \(1 \le i \le r_{K}\). This completes the proof.
    \end{proof}

    Note that Dirichlet's unit theorem also implies that \(\L\) is a complete lattice in \(H\) (by the definition of \(\l\)). In other words, we may reference this result instead of \cref{thm:unit_group_complete_lattice}. We will now discuss the covolume \(V_{\L}\) of \(\L\). Let \(\e_{1},\ldots,\e_{r_{K}}\) be a system of fundamental units for \(K\). Then \(\l(\e_{1}),\ldots,\l(\e_{r_{K}})\) is a basis for \(\L\). Setting
    \[
      \l_{0} = \frac{1}{\sqrt{r_{K}+1}}\mathbf{1},
    \]
    we see that \(\l_{0}\) is a unit vector in \(\R^{r_{K}+1}\) since \(\|\mathbf{1}\| = r_{K}+1\) and is orthogonal to \(H\) because \(\Trace_{\R^{r_{K}+1}/\R}(\l_{0}) = \sqrt{r_{K}+1}\) is nonzero. As \(\l_{0}\) is orthogonal to \(\L \subset H\), we see that \(\l_{0},\l(\e_{1}),\ldots,\l(\e_{r_{K}})\) is a basis for the complete lattice \(\L' = \Z\l_{0}+\L\) in \(\R^{r_{K}+1}\). Since \(\l_{0}\) is a unit vector, the volume of the fundamental domain for \(\L'\) in \(\R^{r_{K}+1}\) is equal to the volume of the fundamental domain for \(\L\) in \(\H\). By \cref{prop:covolume_equals_volume_of_fundamental_domain}, the corresponding covolumes are equal which is to say \(V_{\L} = V_{\L'}\). So it suffices to compute \(V_{\L'}\). The generator matrix \(P\) for \(\L'\) associated to the basis \(\l_{0},\l(\e_{1}),\ldots,\l(\e_{r_{K}})\) is given by
    \[
      P = \begin{pmatrix} \frac{1}{\sqrt{r_{K}+1}} & \l(\e_{1})_{1} & \cdots & \l(\e_{r_{K}})_{1} \\ \vdots & \vdots & & \vdots \\ \frac{1}{\sqrt{r_{K}+1}} & \l(\e_{1})_{r_{K}+1} & \cdots & \l(\e_{r_{K}})_{r_{K}+1} \end{pmatrix}.
    \]
    Adding all of the rows to a fixed row results in
    \[
      P' = \begin{pmatrix} \frac{1}{\sqrt{r_{K}+1}} & \l(\e_{1})_{1} & \cdots & \l(\e_{r_{K}})_{1} \\ \vdots & \vdots & & \vdots \\ \sqrt{r_{K}+1} & 0 & & 0 \\ \vdots & \vdots & & \vdots \\ \frac{1}{\sqrt{r_{K}+1}} & \l(\e_{1})_{r_{K}+1} & \cdots & \l(\e_{r_{K}})_{r_{K}+1} \end{pmatrix},
    \]
    because \(\l(\e) \in H\) for all \(\e \in \mc{O}_{K}^{\ast}\). As \(P'\) differs from \(P\) be row addition, their determinants are the same. Cofactor expanding along the row with all zeros except the first entry, and that this row is arbitrary, shows
    \begin{equation}\label{equ:covolume_of_unit_lattice}
      V_{\L} = \sqrt{r_{K}+1}R_{K},
    \end{equation}
    where \(R_{K}\) is the absolute value of the determinant of any rank \(r_{K}\) minor of
    \[
      \begin{pmatrix} \l(\e_{1})_{1} & \cdots & \l(\e_{r_{K}})_{1} \\ \vdots & & \vdots \\ \l(\e_{1})_{r_{K}+1} & \cdots & \l(\e_{r_{K}})_{r_{K}+1}  \end{pmatrix}.
    \]
    We call \(R_{K}\) the \textbf{regulator}\index{regulator} of \(K\). Since \(V_{\L}\) is independent of the choice of basis, the regulator \(R_{K}\) is independent of any choice of a system of fundamental units for \(K\). Moreover, since \(H\) is a real inner product space we see that the regulator is roughly a measure of the density of the fundamental units in \(K\) (recall \cref{prop:covolume_equals_volume_of_fundamental_domain}). The smaller the regulator the more dense the fundamental units are.
  \fi