\documentclass[12pt]{article}
\usepackage{import}
\input{/Users/henrytwiss/Documents/Documents/LaTeX/Notes/Vignettes/preamble.tex}

\title{Modular Forms}
\author{Henry Twiss}
\makeindex

\begin{document}
  \date{}
  \maketitle
  \tableofcontents
  \section{The Upper-half Plane and Congruence Subgroups}
    If \(a\) is an integer modulo \(m\) with \((a,m) = 1\) we write \(a^{-1}\) for the inverse of \(a\) modulo \(m\). For any complex \(z\) let
    \[
      e(z) = e^{2\pi iz}.
    \]
    We will distinguish the primitive third root of unity \(\w = e\left(\frac{1}{3}\right)\). Also, all sums and products over a quotient group will be consider to be over a complete set of representatives.
    \subsection{The Upper-half Plane}
      The group \(\GL_{2}^{+}(\R)\) acts on the Riemann sphere \(\what{\C}\) by M\"obius transformations. Explicitly, any \(\a = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \GL_{2}^{+}(\R)\) acts on \(z \in \what{\C}\) by
      \[
        \a z = \frac{az+b}{cz+d}.
      \]
      Moreover, this group action is by automorphisms of the Riemann sphere and is invariant under scalar multiplication as well as negation. A short computation shows
      \begin{equation}\label{equ:Mobius_transformation_imaginary_part}
        \Im(\a z) = \det(\a)\frac{\Im(z)}{|cz+d|^{2}},
      \end{equation}
      Therefore \(\a\) preserves the sign of the imaginary part of \(z\). This means \(\GL_{2}^{+}(\R)\) preserves the upper half-plane \(\H\), the lower half-plane \(\conj{\H}\), and the extended real line \(\what{\R}\). Of course, the subgroup \(\GL_{2}^{+}(\Q)\) also preserves \(\what{\Q}\).
      
      We will be primarily interested in this action on the upper-half plane \(\H\). We equip \(\H\) with the \textbf{hyperbolic measure}\index{hyperbolic measure} \(d\mu\) given by
      \[
        d\mu = \frac{dx\,dy}{y^{2}}.
      \]
      This is simply the Lebesgue measure on \(\C\) restricted to \(\H\) and scaled by a factor of \(\frac{1}{y^{2}}\). The most important property about the hyperbolic measure is that it is \(\GL_{2}^{+}(\R)\)-invariant.

      \begin{proposition}\label{prop:hyperbolic_measure_invariance}
        The hyperbolic measure is \(\GL_{2}^{+}(\R)\)-invariant.
      \end{proposition}
      \begin{proof}
        Let \(\a = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \GL_{2}^{+}(\R)\). Since \(\a z\) is a M\"obius transformation it satisfies the Cauchy-Riemann equations. So for the change of variables \(z \mapsto \a z\), the absolute value of the Jacobian determinant is the absolute value of the square of the derivative of \(\a z\). A short computation shows that this is \(\frac{\det(\a)^{2}}{|cz+d|^{4}}\). From this fact and \cref{equ:Mobius_transformation_imaginary_part}, a short computation shows
        \[
          \mu(\a z) = \mu(z).
        \]
        This means \(d\mu\) is \(\GL_{2}^{+}(\R)\)-invariant.
      \end{proof}
    \subsection{Congruence Subgroups}
      To define congruence subgroups, we first need to introduce an associated group. We call \(\SL_{2}(\Z)\) the \textbf{modular group}\index{modular group} which is the group of matrices with integer entries and of determinant \(1\). We will distinguish two matrices
      \[
        S = \begin{pmatrix} 0 &-1 \\ 1 & 0 \end{pmatrix} \quad \text{and} \quad T = \begin{pmatrix} 1 & 1 \\ 0 & 1 \end{pmatrix}.
      \]
      The first matrix is of order \(4\) while the second has infinite order. They act on \(z \in \H\) by
      \[
        Sz = -\frac{1}{z} \quad \text{and} \quad Tz = z+1,
      \]
      respectively. Therefore \(S\) acts by a pseudo-inversion while \(T\) acts by unit translation. The first result usually proved about the modular group is that it is generated by \(S\) and \(T\).

      \begin{proposition}\label{prop:PSL_generator}
          \[
            \SL_{2}(\Z) = \<S,T\>.
          \]
      \end{proposition}
      \begin{proof}
        Let \(n\) be an integer and \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z)\). We will prove \(\g \in \<S,T\>\) by demonstrating that it can be reduced to the identity matrix. If \(c = 0\) then \(\g\) is the identity matrix since \(\det(\g) = 1\) and we are done. So suppose \(c \neq 0\) and write \(a = qc+r\) for some integers \(q\) and \(r\) with \(|r| < |c|\). A short computation shows
        \[
          ST^{-q}\g = \begin{pmatrix} -c & -d \\ r & b-qd \end{pmatrix}.
        \]
        The upper-left entry of this matrix strictly larger than the lower-left entry in absolute value. Therefore if we repeatedly apply this argument, it must terminate with the lower-left entry vanishing. But then we have reached the identity matrix.
      \end{proof}
      
      We can now introduce congruence subgroups which are special subgroups of the modular group defined by congruence conditions on their entries. We begin with principal congruence subgroups. For a positive integer \(N\), the \textbf{principal congruence subgroup}\index{principal congruence subgroup} \(\G(N)\) of level \(N\) is defined by
      \[
        \G(N) = \left\{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_{2}(\Z):\begin{pmatrix} a & b \\ c & d \end{pmatrix} \equiv \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix} \tmod{N}\right\}.
      \]
      This congruence subgroup consists of the matrices which reduce to the identity modulo \(N\). Whence \(\G(N)\) is the kernel of the homomorphism
      \[
        \pi:\SL_{2}(\Z) \to \SL_{2}(\Z/N\Z) \qquad \begin{pmatrix} a & b \\ c & d \end{pmatrix} \mapsto \begin{pmatrix} a & b \\ c & d \end{pmatrix} \tmod{N},
      \]
      and is therefore a normal subgroup. A subgroup \(\G\) of the modular group is said to be a \textbf{congruence subgroup}\index{congruence subgroup} if it contains a principal congruence subgroup. The minimal such \(N\) for which \(\G(N) \subseteq \G\) is called the \textbf{level}\index{level} of \(\G\). Note that if \(M \mid N\) then \(\G(N) \subseteq \G(M)\). Thus if \(\G\) is a congruence subgroup of level \(N\) then it contains the principal congruence subgroups \(\G(kN)\) for all positive integers \(k\). This implies that congruence subgroups are preserved under intersection. In fact, if \(\G_{1}\) and \(\G_{2}\) are congruence subgroups of levels \(N_{1}\) and \(N_{2}\) then \(\G_{1} \cap \G_{2}\) is guaranteed to be a congruence subgroup of level at most \([N_{1},N_{2}]\). Also, it turns out that the aforementioned homomorphism is surjective.

      \begin{proposition}\label{prop:surjective_modulo_N_for_modular_group}
        Let \(N\) be a positive integer. Then the homomorphism
        \[
          \pi:\SL_{2}(\Z) \to \SL_{2}(\Z/N\Z) \qquad \begin{pmatrix} a & b \\ c & d \end{pmatrix} \mapsto \begin{pmatrix} a & b \\ c & d \end{pmatrix} \tmod{N},
        \]
        given by natural projection, is surjective.
      \end{proposition}
      \begin{proof}
        Let \(U\) and \(L\) be the matrices in \(\SL_{2}(\Z/N\Z)\) given by
        \[
          U = \begin{pmatrix} 1 & 1 \\ 0 & 1 \end{pmatrix} \quad \text{and} \quad L = \begin{pmatrix} 1 & 0 \\ 1 & 1 \end{pmatrix}.
        \]
        A short computation shows that these are the images of \(T\) and \(TST\) under \(\pi\) respectively. So \cref{prop:PSL_generator} will imply that \(\pi\) is surjective provided \(U\) and \(L\) generate \(\SL_{2}(\Z/N\Z)\). So let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z/N\Z)\). We will prove \(\g \in \<U,L\>\) by demonstrating that it can be reduced to the identity matrix. To show this, observe that \(U^{n} = U(n)\) and \(L^{n} = L(n)\) where \(U(n)\) and \(L(n)\) are the upper and lower unipotent matrices
        \[
          U(n) = \begin{pmatrix} 1 & n \\ 0 & 1 \end{pmatrix} \quad \text{and} \quad L(n) = \begin{pmatrix} 1 & 0 \\ n & 1 \end{pmatrix},
        \]
        for \(n\) modulo \(N\). So it suffices to show that this collection of unipotent matrices generates \(\SL_{2}(\Z/N\Z)\).  If \(c = 0\) then \(\det(\g) = 1\) implies \(d\) is the inverse of \(a\) modulo \(N\) so that \(\g = \begin{psmallmatrix} a & b \\ 0 & a^{-1} \end{psmallmatrix}\). Short computations show
        \[
          U(-ab)\g= \begin{pmatrix} a & 0 \\ 0 & a^{-1} \end{pmatrix},
        \]
        and
        \[
          L(a^{-1}-1)U(1)L(a-1)U(-a^{-1}) = \begin{pmatrix} a & 0 \\ 0 & a^{-1} \end{pmatrix}.
        \]
        Whence \(\g\) can be reduced to the identity matrix. If \(c \neq 0\) then \(\det(\g) = 1\) and therefore \(c\) is invertible. A short computation shows
        \[
          L(-c)U((1-a)c^{-1})\g = \begin{pmatrix} 1 & (d-1)c^{-1} \\ 0 & 1 \end{pmatrix},
        \]
        and we recognize this latter matrix is as \(U((d-1)c^{-1})\). Whence \(\g\) can again be reduced to the identity matrix.
      \end{proof}
      
      As \(\G(N)\) is the kernel of this homomorphism, the result implies \([\SL_{2}(\Z):\G(N)] = |\SL_{2}(\Z/N\Z)|\). Since any congruence subgroup \(\G\) contains a principal congruence subgroup of some level, it follows that \(\G\) has finite index in \(\SL_{2}(\Z)\). Accordingly, we set
      \[
        d_{\G} = [\SL_{2}(\Z):\G].
      \]
      We now distinguish two important classes of congruence subgroups other than the principal ones. These are the congruence subgroups
      \[
        \G_{1}(N) = \left\{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_{2}(\Z):\begin{pmatrix} a & b \\ c & d \end{pmatrix} \equiv \begin{pmatrix} 1 & \ast \\ 0 & 1 \end{pmatrix} \tmod{N}\right\},
      \]
      and
      \[
        \G_{0}(N) = \left\{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_{2}(\Z):\begin{pmatrix} a & b \\ c & d \end{pmatrix} \equiv \begin{pmatrix} \ast & \ast \\ 0 & \ast \end{pmatrix} \tmod{N}\right\},
      \]
      both of which are of level \(N\). These congruence subgroups consist of the matrices which reduce to unipotent upper triangular and upper triangular modulo \(N\) respectively. The latter subgroup \(\G_{0}(N)\) is called the \textbf{Hecke congruence subgroup}\index{Hecke congruence subgroup} of level \(N\). Note that \(\G(N) \subseteq \G_{1}(N) \subseteq \G_{0}(N)\). 
      
      Since the principal congruence subgroups are normal in \(\SL_{2}(\Z)\), if \(\G\) is a congruence subgroup of level \(N\) then so is \(\a^{-1}\G\a\) for any \(\a \in \SL_{2}(\Z)\). In fact, something more general holds. Congruence subgroups are preserved under conjugation by elements of \(\GL_{2}^{+}(\Q)\) provided we restrict to those elements in \(\SL_{2}(\Z)\).

      \begin{lemma}\label{lem:coset_lemma_1}
        Let \(\G\) be a congruence subgroup and \(\a \in \GL_{2}^{+}(\Q)\). Then \(\a^{-1}\G\a \cap \SL_{2}(\Z)\) is a congruence subgroup. In particular, if \(\a^{-1}\G\a \subseteq \SL_{2}(\Z)\) then \(\a^{-1}\G\a\) is a congruence subgroup.
      \end{lemma}
      \begin{proof}
        Let the level of \(\G\) be \(N\) and choose a positive integer \(r\) such that \(r\a,r\a^{-1} \in \GL_{2}^{+}(\Z)\). Let \(M = r^{2}N\) and notice that any \(\g \in \G(M)\) is of the form
        \[
          \g = \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix}+M\begin{pmatrix} k_{1} & k_{2} \\ k_{3} & k_{4} \end{pmatrix},
        \]
        for integers \(k_{1},\ldots,k_{4}\). Therefore \(\G(M) \subseteq I+M\Mat_{2}(\Z)\) and so
        \[
          \a\G(M)\a^{-1} \subseteq I+N\Mat_{2}(\Z).
        \]
        As \(\G(N) = (I+N\Mat_{2}(\Z)) \cap \SL_{2}(\Z)\), it follows that \(\a\G(M)\a^{-1} \subseteq \G(N)\). Whence \(\G(M) \subseteq \a^{-1}\G\a\) because \(\G\) is of level \(N\). Intersecting with \(\SL_{2}(\Z)\) proves the first statement. The second statement is immediate.
      \end{proof}

      Note that in the case \(\a^{-1}\G\a \subseteq \SL_{2}(\Z)\), normality of principal congruence subgroups force \(\G\) and \(\a^{-1}\G\a\) to be of the same level. In particular, this will always happen whenever we conjugate by elements of the modular group.
    \subsection{Fuchsian Groups and Modular Curves}
      We first restrict our group action on the upper-half plane to \(\SL_{2}(\R)\). Note that for any \(\a = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\R)\), \cref{equ:Mobius_transformation_imaginary_part} simplifies to
      \begin{equation}\label{equ:Mobius_transformation_imaginary_part_simplified}
        \Im(\a z) = \frac{\Im(z)}{|cz+d|^{2}}.
      \end{equation}
       So \(\SL_{2}(\R)\) preserves the upper half-plane \(\H\), the lower half-plane \(\conj{\H}\), and the extended real line \(\what{\R}\). Of course, the subgroup \(\SL_{2}(\Q)\) also preserves \(\what{\Q}\).
       
       A subgroup \(\D\) of \(\SL_{2}(\R)\) is said to be \textbf{Fuchsian}\index{Fuchsian} if it is discrete and acts properly discontinuously on \(\H\). The modular group is the prototypical example of a Fuchsian group.

      \begin{proposition}\label{prop:modular_group_is_Fuchsian}
        The modular group is Fuchsian.
      \end{proposition}
      \begin{proof}
        \(\SL_{2}(\Z)\) is discrete in \(\SL_{2}(\R)\) because \(\Z\) is discrete in \(\R\). So it remains to show that \(\SL_{2}(\Z)\) acts properly discontinuously on \(\H\). To prove this, it suffices to show that for any compact subset \(K \subset \H\) there are finitely many \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z)\) satisfying \(\g K \cap K \neq 0\). Set \(M = \min_{z \in K}\Im(z)\). If \(\g K \cap K \neq \emt\) then there exists a \(z \in K\) such that \(\Im(\g z) \ge M\). This inequality is equivalent to
        \[
          (cx+d)^{2}+(cy)^{2} \le \frac{y}{M},
        \]
        by \cref{equ:Mobius_transformation_imaginary_part_simplified}, which is only satisfied for finitely many pairs of relatively prime integers \((c,d)\) since \(y > 0\). Each pair determines infinitely many matrices \(\g_{k} = \begin{psmallmatrix} a+kc & b+kd \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z)\) possibly satisfying \(\g_{k}K \cap K \neq \emt\). As \(K\) is compact it has bounded real part and so only finitely many such \(k\) satisfy this condition. Hence there are finitely many possible matrices \(\g\).
      \end{proof}
      
      As an immediate consequence of this result, any subgroup or conjugate of the modular group is also Fuchsian. In particular, all congruence subgroups and their conjugates are Fuchsian.
      
      Since any Fuchsian group \(\D\) acts properly discontinuously on \(\H\) and the hyperbolic measure is \(\SL_{2}(\R)\)-invariant by \cref{prop:hyperbolic_measure_invariance}, the hyperbolic measure induces a measure on the quotient \(\D\backslash\H\) which we also denote by \(d\mu\). Moreover, there exist fundamental domains \(\mc{F}_{\D}\) for \(\D\backslash\H\) which are integrable with respect to the hyperbolic measure so that
      \[
         \int_{\D\backslash\H}f(z)\,d\mu =  \int_{\mc{F}_{\D}}f(z)\,d\mu,
      \]
      for any \(\D\)-invariant complex function \(f\) on \(\H\). In particular, we define the \textbf{covolume}\index{convolume} \(V_{\D}\) of \(\D\) to be
      \[
        V_{\D} = \int_{\D\backslash\H}\,d\mu.
      \]
      A Fuchsian group \(\D\) is said to be of the \textbf{first kind}\index{first kind} if its covolume is finite. In this case, the integral of any \(\D\)-invariant function \(f\) over \(\D\backslash\H\) is absolutely convergent whenever \(f\) is bounded.
      
      It turns out that the modular group is Fuchsian of the first kind, but to show this we need to produce a fundamental domain for \(\SL_{2}(\Z)\backslash\H\) which are integrable with respect to the hyperbolic measure. In fact, we will show that a fundamental domain is
      \[
        \mc{F} = \left\{z \in \H:|\Re(z)| \le \frac{1}{2} \text{ and } |z| \ge 1\right\}.
      \]

      \begin{proposition}\label{prop:fundamental_domain_modular_group}
        \(\mc{F}\) is a fundamental domain for \(\SL_{2}(\Z)\backslash\H\).
      \end{proposition}
      \begin{proof}
        We first show any point in \(\H\) is \(\SL_{2}(\Z)\)-equivalent to a point in \(\mc{F}\). So let \(z \in \H\) and \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z)\). Then \cref{equ:Mobius_transformation_imaginary_part_simplified} gives
        \[
          \Im(\g z) = \frac{y}{|cz+d|^{2}}.
        \]
        Since \(\det(\g) = 1\) we cannot have \(c = d = 0\). As \(y > 0\), it is easily checked that \(|cz+d| \ge \min(y,1)\) and thus bounded away from zero. Whence there are finitely many pairs of relatively prime integers \((c,d)\) such that \(|cz+d|^{2} \le M\) for any \(M > 0\). So choose a \(\g\) such that it minimizes \(|cz+d|\) and hence maximizes \(\Im(\g z)\). In particular, \(\Im(S\g z) \le \Im(\g z)\) which is to say
        \[
          \frac{\Im(\g z)}{|\g z|^{2}} \le \Im(\g z).
        \]
        The inequality implies \(|\g z| \ge 1\). Since \(\Im(T^{n}\g z) = \Im(\g z)\) for all integers \(n\), repeating the argument above with \(T^{n}\g\) in place of \(\g\), we see that \(|T^{n}\g z| \ge 1\). But \(T\) shifts the real part by \(1\) so we can choose \(n\) such that \(|\Re(T^{n}\g z)| \le \frac{1}{2}\). Therefore \(T^{n}\g\) maps \(z\) into \(\mc{F}\). It remains to show that no two distinct interior points of \(\mc{F}\) are \(\SL_{2}(\Z)\)-equivalent. So suppose to the contrary that there exist distinct \(z,z' \in \mc{F}^{\circ}\) and \(\g \in \SL_{2}(\Z)\) such that \(z' = \g z\). Without loss of generality, we may assume \(\Im(z') \ge \Im(z)\). Then
        \[
          \Im(z') = \frac{\Im(z)}{|cz+d|^{2}},
        \]
        by \cref{equ:Mobius_transformation_imaginary_part_simplified} and so \(|cz+d| \le 1\). As \(|z| > 1\) and \(|\Re(z)| < \frac{1}{2}\), short computations show that this inequality is valid only if \(c = 0\). Then \(\det(\g) = 1\) forces \(a = d = \pm 1\). Finally, \(|\Re(z)| < \frac{1}{2}\) further forces \(b = 0\). But then \(\g = \pm I\) which gives a contradiction since we assumed \(z\) and \(z'\) were distinct.
      \end{proof}

      \begin{figure}[ht]
        \centering
        \begin{tikzpicture}[scale=3]
          \def\xmin{-2} \def\xmax{2}
          \def\ymin{0} \def\ymax{2}
          \draw[thick] (\xmin,0) -- (\xmax,0);

          \draw[very thick] (0.5,\ymax) -- (0.5,{sqrt(3)/2}) arc (60:120:1) -- (-0.5,\ymax);

          \node at (-0.5,0) [below] {\tiny{\(-\frac{1}{2}\)}};
          \node at (0.5,0) [below] {\tiny{\(\frac{1}{2}\)}};
          \node at (-1.5,0) [below] {\tiny{\(-\frac{3}{2}\)}};
          \node at (1.5,0) [below] {\tiny{\(\frac{3}{2}\)}};
          \node at (0,0) [below] {\tiny{\(0\)}};
          \node at (-1,0) [below] {\tiny{\(-1\)}};
          \node at (1,0) [below] {\tiny{\(1\)}};
          \node at (-2,0) [below] {\tiny{\(-2\)}};
          \node at (2,0) [below] {\tiny{\(2\)}};

          \draw[thin] (0.5,0) -- (0.5,\ymax);
          \draw[thin] (-0.5,0) -- (-0.5,\ymax);
          \draw[thin] (1.5,0) -- (1.5,\ymax);
          \draw[thin] (-1.5,0) -- (-1.5,\ymax);

          \draw (1,0) arc (0:180:1);
          \draw (-1,0) arc (0:90:1);
          \draw (2,1) arc (90:180:1);

          \draw (0,0) arc (0:180:1);
          \draw (2,0) arc (0:180:1);

          \draw (1,0) arc (0:180:{sqrt(3)/6});
          \draw ({sqrt(3)/3},0) arc (0:180:{sqrt(3)/6});

          \draw (2,0) arc (0:180:{sqrt(3)/6});
          \draw ({1+sqrt(3)/3},0) arc (0:180:{sqrt(3)/6});

          \draw (0,0) arc (0:180:{sqrt(3)/6});
          \draw ({(sqrt(3)/3)-1},0) arc (0:180:{sqrt(3)/6});

          \draw (-1,0) arc (0:180:{sqrt(3)/6});
          \draw ({(sqrt(3)/3)-2},0) arc (0:180:{sqrt(3)/6});

          \node at (0,1.5) {\tiny{\(\mc{F}\)}};
          \node at (-1,1.5) {\tiny{\(T^{-1}\mc{F}\)}};
          \node at (1,1.5) {\tiny{\(T\mc{F}\)}};
          \node at (0,0.75) {\tiny{\(S\mc{F}\)}};
          \node at (-1,0.75) {\tiny{\(T^{-1}S\mc{F}\)}};
          \node at (1,0.75) {\tiny{\(TS\mc{F}\)}};
          \node at (-0.3,0.5) {\tiny{\(ST\mc{F}\)}};
          \node at (0.3,0.5) {\tiny{\(ST^{-1}\mc{F}\)}};

          \begin{scope}
            \path[clip] (0.5,\ymax) -- (0.5,{sqrt(3)/2}) arc (60:120:1) -- (-0.5,\ymax) -- cycle;
            \fill[gray,opacity=0.3] (-0.5,0) rectangle (0.5,\ymax);
          \end{scope}
        \end{tikzpicture}
        \caption{The standard fundamental domain for \(\SL_{2}(\Z)\backslash\H\).} \label{fig:fundamental_domain_modular_group}
      \end{figure}
      
      The region \(\mc{F}\), shaded in \cref{fig:fundamental_domain_modular_group}, is called the \textbf{standard fundamental domain}\index{standard fundamental domain}. Any \(z \in \mc{F}\) satisfies \(\Im(z) \ge \frac{\sqrt{3}}{2}\). Indeed, \(z\) occurs on the arc of a circle of radius \(r \ge 1\) subject to \(|\Re(z)| \le \frac{1}{2}\). Then \(\Im(z)\) is minimized on the arc \(|z| = 1\), and on this arc
      \[
        \Im(z) = \sqrt{1-\Re(z)^{2}}.
      \]
      The right-hand side is minimized at \(\Re(z) = \pm\frac{1}{2}\) giving \(\Im(z) = \frac{\sqrt{3}}{2}\). This corresponds to the points \(-\frac{1}{2}+i\frac{\sqrt{3}}{2}\) and \(\frac{1}{2}+i\frac{\sqrt{3}}{2}\) which are \(\w\) and \(1+\w\) respectively. They are the vertices of the boundary of \(\mc{F}\).
  
      If \(\G\) is a congruence subgroup, we can use the standard fundamental domain to produce a fundamental domain for \(\GH\) which can be used to evaluate the covolume of \(\G\). It so happens that
      \[
        \mc{F}_{\G} = \bigcup_{\b \in \G\backslash\SL_{2}(\Z)}\b\mc{F},
      \] 
      is a fundamental domain for \(\GH\) which is obtained from the standard fundamental domain using representatives of orbits of \(\G\backslash\SL_{2}(\Z)\).

      \begin{proposition}\label{prop:fundamental_domain_congruence_subgroup}
        \(\mc{F}_{\G}\) is a fundamental domain for \(\GH\).
      \end{proposition}
      \begin{proof}
        We first show that every point in \(\H\) is \(\G\)-equivalent to a point in \(\mc{F}_{\G}\). From the definition of \(\mc{F}_{\G}\), it is straightforward to check that
        \[
          \bigcup_{\g \in \G}\g\mc{F}_{\G} = \H.
        \]
        Whence every point in \(\H\) is \(\G\)-equivalent to a point in \(\mc{F}_{\G}\). We will now show that no two distinct interior points of \(\mc{F}_{\G}\) are \(\G\)-equivalent. Suppose to the contrary that there are distinct \(z,z' \in \mc{F}_{\G}^{\circ}\) and a \(\g \in \G\) such that \(\g z = z'\). In particular, \(z \in \b\mc{F}^{\circ}\) and \(z' \in \b'\mc{F}^{\circ}\) for some \(\b,\b' \in \G\backslash\SL_{2}(\Z)\). As no two distinct interior points of \(\mc{F}\) are \(\SL_{2}(\Z)\)-equivalent, this forces \(\b\) and \(\b'\) to belong to the same coset of \(\G\backslash\SL_{2}(\Z)\). Whence \(\b = \b'\) and implying \(z,z' \in \b\mc{F}^{\circ} \cap \b'\mc{F}^{\circ}\). This gives a contradiction since no two distinct interior points of \(\mc{F}\) are \(\SL_{2}(\Z)\)-equivalent. Hence no two distinct interior points of \(\mc{F}_{\G}\) are \(\G\)-equivalent.
      \end{proof}

      We can now show that the modular group is Fuchsian of the first kind. For brevity, we write \(V = V_{\SL_{2}(\Z)}\) so that
      \[
        V = \int_{\SL_{2}(\Z)\backslash\H}\,d\mu.
      \]
      Using \cref{prop:fundamental_domain_modular_group} to write this integral explicitly, we obtain
      \[
        V = \int_{-\frac{1}{2}}^{\frac{1}{2}}\int_{\sqrt{1-x^{2}}}^{\infty}\frac{dy\,dx}{y^{2}},
      \]
      and a short computation shows \(V = \frac{\pi}{3}\). Therefore the modular group is Fuchsian of the first kind. There is also a simple relation between \(V_{\G}\) and \(d_{\G}\) given by
      \begin{equation}\label{equ:Petersson_volume_relation}
        V_{\G} = d_{\G}V,
      \end{equation}
      which follows immediately from \cref{prop:fundamental_domain_congruence_subgroup}. Whence every congruence subgroup is Fuchsian of the first kind as well. Using \(\SL_{2}(\R)\)-invariance of the hyperbolic measure and the change of variables \(z \mapsto \a^{-1}z\), a short computation shows
      \begin{equation}\label{equ:volume_conjugation_invariance}
        V_{\a^{-1}\G\a} = V_{\G},
      \end{equation}
      for any \(\a \in \SL_{2}(\R)\). So the conjugate of every congruence subgroup is also Fuchsian of the first kind.

      It is also possible to say something about the stabilizer subgroups of points in \(\H\) with respect to the action of a congruence subgroup \(\G\). Let \(\G_{z}\) denote the stabilizer subgroup of \(z \in \H\). Then \(\G_{\g z} = \g\G_{z}\g^{-1}\) for any \(\g \in \G\) and it follows that all of the stabilizer subgroups are determined by those for \(z \in \mc{F}_{\G}\). Moreover, since \(\mc{F}_{\G}\) is a fundamental domain, \(\G_{z}\) is trivial if \(z \in \mc{F}_{\G}^{\circ}\). So any point with a nontrivial stabilizer subgroups must lie on the boundary of \(\mc{F}_{\G}\). As \(\G\) is a subgroup of \(\SL_{2}(\Z)\), we conclude \(\G_{z}\) is a subgroup of \(\SL_{2}(\Z)_{z}\). This leads us to determining the stabilizer subgroups in the case of the modular group.

      \begin{proposition}\label{prop:stabilizer_subgroup}
        Let \(z \in \mc{F}\). Then
        \[
          \SL_{2}(\Z)_{z} = \begin{cases} \<S\> & \text{if \(z = i\)}, \\ \<ST\> & \text{if \(z = \w\)}, \\ \<TS\> & \text{if \(z = 1+\w\)}, \\ \<-I\> & \text{if \(z \neq i,\w,1+\w\)}. \end{cases}
        \]
        Moreover, \(\SL_{2}(\Z)_{i}\) is of order \(4\) while \(\SL_{2}(\Z)_{\w}\) and \(\SL_{2}(\Z)_{1+\w}\) are of order \(6\).
      \end{proposition}
      \begin{proof}
        Let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z)\). Then \(\g z = z\) implies
        \[
          cz^{2}+(d-a)z-b = 0.
        \]
        We will analyze this identity on a case by case basis. In particular, we will take \(z = i\), \(z = \w\), \(z = 1+\w\), and \(z \neq i,\w,1+\w\) respectively.

        Taking \(z = i\) in this identity gives
        \[
          -c+(d-a)i-b = 0.
        \]
        Equating the real and imaginary parts shows that \(b = -c\) and \(d = a\). Then \(\g = \begin{psmallmatrix} a & -c \\ c & a \end{psmallmatrix}\) and \(a^{2}+c^{2} = 1\). Therefore we have \(a = 1\) and \(c = 0\), \(a = -1\) and \(c = 0\), \(a = 0\) and \(c = 1\), or \(a = 0\) and \(c = -1\). These four cases correspond to the matrices \(I\), \(-I\), \(S\), and \(-S\) respectively. Since \(S^{2} = -I\), it follows that \(\SL_{2}(\Z)_{i} = \<S\>\) and is of order \(4\).
        
        Taking \(z = \w\) in the identity instead gives
        \[
          c\w^{2}+(d-a)\w-b = 0.
        \]
        Recall that \(m_{\w}(x) = x^{2}+x+1\) is the minimal polynomial for \(\w\) over \(\Q\). So \(\w^{2} = -\w-1\) and substituting this identity into the one above yields
        \[
        (d-a-c)\w-(b+c) = 0.
        \]
        By minimality of \(m_{\w}(x)\), \(\w\) and \(1\) are linearly independent over \(\Q\) so we may equate coefficients to see that \(d = a+c\) and \(b = -c\). Then \(\g = \begin{psmallmatrix} a & -c \\ c & a+c \end{psmallmatrix}\) and \(a^{2}+ac+c^{2} = 1\). Completing the square shows \((a+c)^{2}-ac = 1\). Therefore we have \(a = 1\) and \(c = 0\), \(a = -1\) and \(c = 0\), \(a = 0\) and \(c = 1\), \(a = 0\) and \(c = -1\), \(a = -1\) and \(c = 1\), or \(a = 1\) and \(c = -1\). These six cases correspond to the matrices \(I\), \(-I\), \(ST\), \((ST)^{4}\), \((ST)^{2}\), and \((ST)^{5}\) respectively. As \((ST)^{3} = -I\), it follows that \(\SL_{2}(\Z)_{\w} = \<ST\>\) and is of order \(6\). Moreover, if \(z = 1+\w\) then \(z = T\w\). Whence \(\SL_{2}(\Z)_{1+\w} = T\SL_{2}(\Z)_{\w}T^{-1} = \<TS\>\) and is of order \(6\).
        
        It remains to show that if \(z \neq i,\w,1+\w\) then \(\SL_{2}(\Z)_{z} = \<I\>\). Equivalently, will show the contrapositive which is to say that if \(\SL_{2}(\Z)_{z} \neq \<-I\>\) then \(z = i,\w,1+\w\). Since the stabilizer subgroup of \(z\) is trivial if \(z \in \mc{F}^{\circ}\), we may additionally assume \(z\) lies on the boundary of \(\mc{F}\). Now suppose for such \(z\) that \(\g \neq \pm I\). We first claim \(c > 0\). For if \(c = 0\), \(\det(\g) = 1\) implies \(a = d = \pm1\). This further forces \(b = 0\) implying \(\g = \pm I\) which is a contradiction. Hence \(c \neq 0\) and so \(z\) satisfies the aforementioned identity which is a quadratic. A short computation shows that the discriminant is \((a+d)^{2}-4\). Since this quadratic has integer coefficients and \(z\) is complex, the discriminant must be negative. So
        \[
          (a+d)^{2}-4 < 0,
        \]
        which forces \(a+d = 0,1,-1\). These three cases correspond to the discriminant being \(-4\) in the first case and \(-3\) in the latter two cases. Whence the quadratic formula implies
        \[
          z = \frac{a\pm i}{c}, \quad \text{or} \quad z = \frac{2a-1\pm\sqrt{3}i}{2c}, \quad \text{or} \quad z = \frac{2a+1\pm\sqrt{3}i}{2c},
        \]
        respectively. In any case, recalling that \(\Im(z) \ge \frac{\sqrt{3}}{2}\) for \(z \in \mc{F}\) implies \(c = \pm 1\). This forces \(a = 0\) in the first case, \(a = 0,1\) in the second, and \(a = 0,-1\) in the third. Whence \(z = i\) in the first case and \(z = \w,1+\w\) in the second and third cases. This completes the proof.
      \end{proof}

      Returning to the case of a congruence subgroup \(\G\), it follows from this result and our previous remarks that \(\G_{z}\) is necessarily trivial if \(z\) is not \(\SL_{2}(\Z)\)-equivalent to \(i\), \(\w\), or \(1+\w\). Moreover, if \(z\) is \(\SL_{2}(\Z)\)-equivalent to one of these points then \(\G_{z}\) is trivial unless at least one of the matrices \(\pm S\), \(\pm ST\), or \(\pm TS\) belongs to \(\G\) respectively. In particular, \(\G_{z}\) is always finite.

      A \textbf{modular curve}\index{modular curve} is a quotient \(\GH\) of \(\H\) by a congruence subgroup \(\G\). Observe that \(\GH\) is not compact as the fundamental domain \(\mc{F}_{\G}\) need not contain points of \(\what{\Q}\). These points correspond to cusps which we now define. Recall that \(\G\) acts on \(\what{\Q}\). A \textbf{cusp class}\index{cusp class} of \(\GH\) is a coset of \(\G\backslash\what{\Q}\). There is only one cusp class for the modular group since it acts transitively. Indeed, \(\what{\Q}\) is exactly the orbit of \(\infty\). For if \(\frac{a}{c} \in \Q\) with \((a,c) = 1\), B\'ezout's identity provides the existence of integers \(b\) and \(d\) such that \(ad-bc = 1\) whence \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \SL_{2}(\Z)\) satisfies \(\g\infty = \frac{a}{c}\). Therefore the action is transitive and there can only be finitely many cosets of \(\G\backslash\what{\Q}\) since \(\G\) has finite index in the modular group. In other words, the number of cusp classes is finite and at most \(d_{\G}\). In particular, the orbit of \(\infty\) is a cusp class of \(\GH\). A \textbf{cusp}\index{cusp} is a representative of a cusp class. We denote cusps by gothic characters \(\mf{a}\), \(\mf{b}\), etc.

      \begin{remark}
        The cusps are exactly the points needed to make a fundamental domain \(\mc{F}_{\G}\) compact as a subset of \(\what{\C}\). To see this, suppose \(\mf{a}\) is a limit point of \(\mc{F}_{\G}\) that does not belong to \(\mc{F}_{\G}\). Then \(\mf{a} \in \what{\R}\). As the unique limit point of \(\mc{F}\) not belonging to \(\mc{F}\) is \(\infty\) and \(\what{\Q} = \SL_{2}(\Z)\infty\), \cref{prop:fundamental_domain_congruence_subgroup} implies \(\mf{a} \in \what{\Q}\) which means \(\mf{a}\) is a cusp. In the case of the standard fundamental domain \(\mc{F}\), the only cusp is \(\infty\).
      \end{remark}

      We will now describe the stabilizer subgroups of \(\G\) relative to a cusp \(\mf{a}\). This will slightly depend upon if \(\G\) contains \(-I\), so let \(\e_{\G} = 1,0\) according to if \(-I \in \G\) or not. We will denote the stabilizer subgroup of the cusp \(\mf{a}\) by \(\G_{\mf{a}}\). We begin by describing \(\G_{\infty}\). If \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G\) stabilizes \(\infty\) then necessarily \(c = 0\) and since \(\det(\g) = 1\) we must have \(a = d = \pm 1\) or \(a = d = 1\) according to if \(-I \in \G\) or not. In either case, \(\g\) acts by translation by \(b\). If we let \(h_{\infty}\) be the smallest positive integer such that \(\g_{\infty} = \begin{psmallmatrix} 1 & h_{\infty} \\ 0 & 1 \end{psmallmatrix} \in \G_{\infty}\) then
      \[
        \G_{\infty} = \<\g_{\infty},(-I)^{\e_{\G}}\>.
      \]
      By our previous discussion, there exists a matrix \(\eta_{\mf{a}} \in \SL_{2}(\Z)\) such that \(\eta_{\mf{a}}\infty = \mf{a}\). This matrix is determined up to multiplication on the right by an element of \(\G_{\infty}\). In any case, \(\G_{\mf{a}} = \eta_{\mf{a}}\G_{\infty}\eta_{\mf{a}}^{-1} \cap \G\) and so
      \[
        \G_{\mf{a}} = \<\eta_{\mf{a}},(-I)^{\e_{\G}}\>,
      \]
      where \(\g_{\mf{a}}\) is of the form
      \[
        \g_{\mf{a}} = \eta_{\mf{a}}\begin{pmatrix} 1 & h_{\mf{a}} \\ 0 & 1 \end{pmatrix}\eta_{\mf{a}}^{-1},
      \]
      for some positive integer \(h_{\mf{a}}\). We call \(h_{\mf{a}}\) the \textbf{width}\index{width} of the cusp \(\mf{a}\). Equivalently, \(h_{\mf{a}}\) is the shift of the minimal translation belonging to \(\eta_{\mf{a}}^{-1}\G\eta_{\mf{a}}\). Also observe that \(h_{\mf{a}}\) does not depend on the choice of \(\eta_{\mf{a}}\). We will set
      \[
        \g_{\infty}^{(h_{\mf{a}})} = \begin{pmatrix} 1 & h_{\mf{a}} \\ 0 & 1 \end{pmatrix} \quad \text{and} \quad \G_{\infty}^{(h_{\mf{a}})} = \<\g_{\infty}^{(h_{\mf{a}})},(-I)^{\e_{\G}}\>,
      \]
      so that
      \[
        \eta_{\mf{a}}^{-1}\G_{\mf{a}}\eta_{\mf{a}} = \G_{\infty}^{(h_{\mf{a}})}.
      \]
      In particular, \(\g_{\infty}^{(h_{\infty})} = \g_{\infty}\) and \(\G_{\infty}^{(h_{\infty})} = \G_{\infty}\).

      \begin{remark}\label{rem:scaling_matrix_to_cusp_class}
        Suppose \(\mf{a}'\) is a cusp that belongs to the same cusp class at \(\mf{a}\). Then \(\mf{a}' = \g\mf{a}\) for some \(\g \in \G\). It follows that \(\G\eta_{\mf{a}}\G_{\infty}\) only depends upon the cusp class of \(\mf{a}\) which is \(\G\eta_{\mf{a}}\infty\). Moreover, \(\G_{\mf{a}'} = \g\G_{\mf{a}}\g^{-1}\) and \(\G_{\mf{a}'} = \g\eta_{\mf{a}}\G_{\infty}\eta_{\mf{a}}^{-1}\g^{-1} \cap \G\). Whence \(\g_{\mf{a}'} = \g\g_{\mf{a}}\g^{-1}\) and therefore \(h_{\mf{a}} = h_{\mf{a'}}\) because the width of a cusp does not depend upon the choice of \(\eta_{\mf{a}}\). This means that the width of \(\mf{a}\) only depends upon its cusp class and so the same is true for \(\g_{\infty}^{(h_{\mf{a}})}\) and \(\G_{\infty}^{(h_{\mf{a}})}\).
      \end{remark}
    
      If \(\G\) is of level \(N\) then \(N\) is the smallest positive integer such that \(\G(N) \subseteq \G\). This means \(\begin{psmallmatrix} 1 & N \\ 0 & 1 \end{psmallmatrix}\) is the minimal translation guaranteed to belong to \(\G\). Since principal congruence subgroups are normal in the modular group, we have \(\G(N) \subseteq \G_{\infty}^{(h_{\mf{a}})}\) and so the aforementioned translation must be a power of \(\g_{\infty}^{(h_{\mf{a}})}\) which means \(h_{\mf{a}} \mid N\). We say that \(\G\) is \textbf{reduced}\index{reduced} at \(\mf{a}\) if \(h_{\mf{a}} = 1\). For example, the congruence subgroups \(\G_{0}(N)\), \(\G_{1}(N)\), and \(\G(N)\) are all reduced at \(\infty\). The width of the cusps are also related to the index \(d_{\G}\) in a simple manner.

      \begin{proposition}\label{prop:sum_of_widths_equals_index}
        For any congruence subgroup \(\G\) and any cusp \(\mf{a}\) of \(\GH\), there are \(h_{\mf{a}}\) many cosets of \(\G\backslash\SL_{2}(\Z)\). In particular,
        \[
          \sum_{\mf{a} \in \G\backslash\what{\Q}}h_{\mf{a}} = d_{\G}.
        \]
      \end{proposition}
      \begin{proof}
        Choose \(\eta_{\mf{a}} \in \SL_{2}(\Z)\) with \(\eta_{\mf{a}}\infty = \mf{a}\). It follows from \cref{rem:scaling_matrix_to_cusp_class} that the cusp classes of \(\GH\) are in bijection with the double cosets of \(\G\backslash\SL_{2}(\Z)/\G_{\infty}\) where a cusp class \(\G\eta_{\mf{a}}\infty\) corresponds to the double coset \(\G\eta_{\mf{a}}\G_{\infty}\) under this bijection. As the action of \(\SL_{2}(\Z)\) on \(\what{\Q}\) is transitive, consider the surjection
        \[
          \phi:\G\backslash\SL_{2}(\Z) \to \G\backslash\SL_{2}(\Z)/\G_{\infty} \qquad \G\eta_{\mf{a}} \mapsto \G\eta_{\mf{a}}\G_{\infty}.
        \]
        We will compute the number of cosets in a fiber of \(\phi\). Suppose \(\mf{a}\) and \(\mf{a}'\) are \(\G\)-equivalent cusps so that \(\G\eta_{\mf{a}}\) and \(\G\eta_{\mf{a}'}\) belong to the fiber of \(\G\eta_{\mf{a}}\G_{\infty} = \G\eta_{\mf{a}'}\G_{\infty}\). Then \(\eta_{\mf{a}'} = \g\eta_{\mf{a}}\g_{\infty}^{n}\) for some \(\g \in \G\) and integer \(n\). Whence \(\G\eta_{\mf{a}} = \G\eta_{\mf{a}'}\) if and only if \(\G\eta_{\mf{a}} =  \G\eta_{\mf{a}}\g_{\infty}^{n}\) which is to say that \(\g_{\infty}^{n} \in \eta_{\mf{a}}^{-1}\G\eta_{\mf{a}}\). But then \(\g_{\infty}^{n} \in \G_{\infty}^{(h_{\mf{a}})}\) which happens if and only if \(h_{\mf{a}} \mid n\). So the cosets \(\G\eta_{\mf{a}}\) and \(\G\eta_{\mf{a}'}\) are equal if and only if \(h_{\mf{a}} \mid n\). This means there are \(h_{\mf{a}}\) cosets in the fiber of \(\G\eta_{\mf{a}}\G_{\infty}\). In other words, there are \(h_{\mf{a}}\) many cosets of \(\G\backslash\SL_{2}(\Z)\) proving the first statement. For the second, the sum of the number of cosets in the fibers of \(\phi\) is equal to the order of \(\G\backslash\SL_{2}(\Z)\) since \(\phi\) is surjective. This is to say
        \[
          \sum_{\mf{a} \in \G\backslash\what{\Q}}h_{\mf{a}} = d_{\G},
        \]
        proving the second statement.
      \end{proof}

      As it turns out, it will be more useful deal with the width of cusps implicitly. Set
      \[
        B_{\G} = \<T,(-1)^{\e_{\G}}\>.
      \]
      We call \(\s_{\mf{a}} \in \SL_{2}(\R)\)  a \textbf{scaling matrix}\index{scaling matrix} for \(\mf{a}\) if \(\s_{\mf{a}}\infty = \mf{a}\) and \(\s_{\mf{a}}^{-1}\g_{\mf{a}}\s_{\mf{a}} = T\). This forces
      \[
        \s_{\mf{a}}^{-1}\G_{\mf{a}}\s_{\mf{a}} = B_{\G}.
      \]
      The second condition is possible only because we are allowing the entries to be real. For example, a short computation shows that we can choose the scaling matrix to be
      \[
        \s_{\mf{a}} = \eta_{\mf{a}}\begin{pmatrix} \sqrt{h_{\mf{a}}} & 0 \\ 0 & \frac{1}{\sqrt{h_{\mf{a}}}} \end{pmatrix}.
      \]
      Observe that scaling matrices are determined up to multiplication on the right by powers of \(T\). Also, if \(\G\) is reduced at \(\mf{a}\) then we may take \(\s_{\mf{a}} = \eta_{\mf{a}}\) so that the scaling matrix can be chosen to lie in \(\SL_{2}(\Z)\). In this case, \(\G_{\mf{a}} = B_{\G}\). For example, this occurs at \(\infty\) for the Hecke congruence subgroups.

      Lastly, let us discuss a useful property of integrals over \(\GH\). Recall that we may use the fundamental domain \(\mc{F}_{\G}\) to integrate over \(\GH\) by writing
      \[
        \int_{\GH}f(z)\,d\mu = \int_{\mc{F}_{\G}}f(z)\,d\mu,
      \]
      for any \(\G\)-invariant complex function \(f\) on \(\H\). As \(\G_{\mf{a}}\) is also Fuchsian of the first kind, \(\G_{\mf{a}}\backslash\H\) admits fundamental domains \(\mc{F}_{\G_{\mf{a}}}\) that are integrable with respect to the hyperbolic measure. So
      \[
        \int_{\G_{\mf{a}}\backslash\H}f(z)\,d\mu = \int_{\mc{F}_{\mf{a}}}f(z)\,d\mu,
      \]
      for any \(\G_{\mf{a}}\)-invariant complex function \(f\) on \(\H\). It turns out that these two types of integrals are related for complex functions that are averaged over \(\G_{\mf{a}}\backslash\G\). This is known as the \textbf{unfolding/folding method}\index{unfolding/folding method}.

      \begin{theorem*}[Unfolding/folding method]
        Let \(\mf{a}\) be a cusp of \(\GH\). If \(f\) is a \(\G_{\mf{a}}\)-invariant complex function on \(\H\) then
        \[
          \int_{\GH}\sum_{\g \in \G_{\mf{a}}\backslash\G}f(\g z)\,d\mu = \int_{\G_{\mf{a}}\backslash\H}f(z)\,d\mu,
        \]
        provided either side is absolutely convergent.
      \end{theorem*}
      \begin{proof}
        If the left-hand side converges absolutely then we may interchange the sum and integral. Upon making the change of variables \(z \mapsto \g^{-1}z\), the \(\G\)-invariance of \(d\mu\) implies that the integral takes the form
        \[
          \sum_{\g \in \G_{\mf{a}}\backslash\G}\int_{\g\mc{F}_{\G}}f(z)\,d\mu.
        \]
        The result follows as \(\H = \bigcup_{\g \in \G}\g\mc{F}\). Moreover, we can argue in reverse provided the right-hand side converges absolutely. This completes the proof.
      \end{proof}

      The process of transforming the left-hand side into the right-hand side is called \textbf{unfolding}\index{unfolding} while transforming the right-hand into the left-hand side is called \textbf{folding}\index{folding}. In the special case of \(\G_{\infty}\backslash\H\), the latter integral can be computed explicitly. Indeed,
      \[
        \mc{F}_{\G_{\infty}} = \{z \in \H:0 \le \Re(z) \le h_{\infty} \text{ and } \Im(z) > 0\},
      \]
      is clearly a fundamental domain for \(\G_{\infty}\backslash\H\) so that
      \[
        \int_{\G_{\infty}\backslash\H}f(z)\,d\mu = \int_{0}^{\infty}\int_{0}^{h_{\infty}}f(z)\,\frac{dx\,dy}{y^{2}},
      \]
      for any \(\G_{\infty}\)-invariant complex function \(f\) on \(\H\).
    \subsection{Double Coset Decompositions and Exponential Sums}
      Let \(\mf{a}\) and \(\mf{b}\) be cusps of \(\GH\) with respective scaling matrices \(\s_{\mf{a}}\) and \(\s_{\mf{b}}\) respectively. It will be essential to have a double coset decomposition for sets of the form \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\). This is known as the \textbf{Bruhat decomposition}\index{Bruhat decomposition} for \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\).

      \begin{theorem*}[Bruhat decomposition]
        Let \(\mf{a}\) and \(\mf{b}\) be cusps of \(\GH\) with scaling matrices \(\s_{\mf{a}}\) and \(\s_{\mf{b}}\) respectively. Then we have the disjoint decomposition
        \[
          \s_{\mf{a}}^{-1}\G\s_{\mf{b}} = \W_{\infty} \cup \left(\bigcup_{\substack{c \in \Z_{+} \\ d \tmod{c}}}\W_{c/d}\right),
        \]
        where
        \[
          \W_{\infty} = B_{\G}w_{\infty}B_{\G} \quad \text{and} \quad \W_{c/d} = B_{\G}\w_{c/d}B_{\G},
        \]
        with \(\w_{\infty} = \begin{psmallmatrix} 1 & \ast \\ 0 & 1 \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) and \(\w_{c/d} = \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) if such matrices exists otherwise \(\W_{\infty}\) and \(\W_{c/d}\) are empty respectively. In the former case for \(\W_{\infty}\), \(\w_{\infty}\) exists if and only if \(\mf{a}\) and \(\mf{b}\) are \(\G\)-equivalent. In the former case for \(\W_{c/d}\), \(a\) and \(d\) are determined modulo \(c\) and \(\W_{c/d}\) does not depend on the entry \(a\) of \(\w_{c/d}\).
      \end{theorem*}
      \begin{proof}
        As \(B_{\G} = \s_{\mf{a}}^{-1}\G_{\mf{a}}\s_{\mf{a}}\) and \(B_{\G} = \s_{\mf{b}}^{-1}\G_{\mf{b}}\s_{\mf{b}}\), short computations show that \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) is invariant under multiplication on the left or right by elements \(B_{\G}\). This proves \(\W_{\infty}\) and \(\W_{c/d}\) are subsets of \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\). Now any \(\w_{\infty} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) satisfies \(\w_{\infty} = \s_{\mf{a}}^{-1}\g\s_{\mf{b}}\) for some \(\g \in \G\). As \(\w_{\infty}\) fixes \(\infty\), a short computation shows
        \[
          \g\mf{b} = \mf{a}.
        \]
        This means \(\mf{a}\) and \(\mf{b}\) are \(\G\)-equivalent. Conversely, if \(\mf{a}\) and \(\mf{b}\) are \(\G\)-equivalent then \(\g\mf{b} = \mf{a}\) for some \(\g \in \G\) and we may take \(\w_{\infty} = \s_{\mf{a}}^{-1}\g\s_{\mf{b}}\) because this matrix fixes \(\infty\). This proves that \(\w_{\infty}\) exists if and only if \(\mf{a}\) and \(\mf{b}\) are \(\G\)-equivalent. In this case, we may write
        \[
          \s_{\mf{a}}^{-1}\G\s_{\mf{b}} = \s_{\mf{a}}^{-1}\G\s_{\mf{a}}\w_{\infty} \quad \text{and} \quad \s_{\mf{a}}^{-1}\G\s_{\mf{b}} = \w_{\infty}\s_{\mf{b}}^{-1}\G\s_{\mf{b}},
        \]
        from which we see that the matrices in \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) acting by translation are exactly \(\W_{\infty}\). Every other matrix in \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) belongs to one of the double cosets \(\W_{c/d}\). The relation
        \[
          T\w_{c/d}T = \begin{pmatrix} a+c & \ast \\ c & d+c \end{pmatrix},
        \]
        shows that \(\W_{c/d}\) is generated uniquely by a matrix of the form \(\w_{c/d} = \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\) where \(a\) and \(d\) are determined modulo \(c\). To see that \(\W_{c/d}\) does not depend on the entry \(a\) of \(\w_{c/d}\), let \(\w'_{c/d} = \begin{psmallmatrix} a' & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\). Write \(\w_{c/d} = \s_{\mf{a}}^{-1}\g\s_{\mf{b}}\) and \(\w'_{c/d} = \s_{\mf{a}}^{-1}\g'\s_{\mf{b}}\) for some \(\g,\g' \in \G\). The relations
        \[
          \w_{c/d}(\w'_{c/d})^{-1} = \begin{pmatrix} \ast & \ast \\ 0 & \ast \end{pmatrix} \quad \text{and} \quad \g(\g')^{-1} = \s_{\mf{a}}\w_{c/d}(\w'_{c/d})^{-1}\s_{\mf{a}}^{-1},
        \]
        imply \(\g(\g')^{-1} \in \G_{\mf{a}}\). So \(\w_{c/d}(\w'_{c/d})^{-1} \in B_{\G}\) whence \(B_{\G}\w_{c/d}B_{\G} = B_{\G}\w'_{c/d}B_{\G}\).
      \end{proof}

      As the double cosets \(\W_{\infty}\) and \(\W_{c/d}\) in the Bruhat decomposition may very well be empty, we would like to track exactly which are not. To do this, let \(\mc{C}_{\mf{a},\mf{b}}\) and \(\mc{D}_{\mf{a},\mf{b}}(c)\) be the sets
      \[
        \mc{C}_{\mf{a},\mf{b}} = \left\{c \in \Z_{+}:\begin{pmatrix} \ast & \ast \\ c & \ast \end{pmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\right\} \quad \text{and} \quad \mc{D}_{\mf{a},\mf{b}}(c) = \left\{d \in \Z/c\Z:\begin{pmatrix} \ast & \ast \\ c & d \end{pmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}\right\},
      \]
      where \(\mc{D}_{\mf{a},\mf{b}}(c)\) is defined for \(c \in \mc{C}_{\mf{a},\mf{b}}\). These sets are constructed so that \(\mc{C}_{\mf{a},\mf{b}}\) and \(\mc{D}_{\mf{a},\mf{b}}(c)\) run over precisely the pairs \((c,d)\) for which \(\W_{c/d}\) is nonempty. Indeed, we may write
      \[
       \s_{\mf{a}}^{-1}\G\s_{\mf{b}} = \W_{\infty} \cup \left(\bigcup_{\substack{c \in \mc{C}_{\mf{a},\mf{b}} \\ d \in \mc{D}_{\mf{a},\mf{b}}(c)}}\W_{c/d}\right),
      \]
      where none of the double cosets \(\W_{c/d}\) are empty.

      We will now introduce two type of exponential sum associated to pairs of cusps. These are types of Kloosterman and Sali\'e sums. We being with the Kloosterman sums. For any \(c \in \mc{C}_{\mf{a},\mf{b}}\) and integers \(m\) and \(n\), the \textbf{Kloosterman sum}\index{Kloosterman sum} \(K_{\mf{a},\mf{b}}(m,n,c)\) relative to \(\mf{a}\) and \(\mf{b}\) is defined by
      \[
        K_{\mf{a},\mf{b}}(m,n,c) = \sum_{\substack{d \in \mc{D}_{\mf{a},\mf{b}}(c) \\ \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}}}e\left(\frac{ma+nd}{c}\right).
      \]
      This sum is well-defined since \(a\) and \(d\) are determined modulo \(c\) by the Bruhat decomposition. If \(m = n = 0\) then
      \[
        K_{\mf{a},\mf{b}}(0,0,c) = |\mc{D}_{\mf{a},\mf{b}}(c)|.
      \]
      The Sali\'e sums are defined in a similar manner. For any \(c \in \mc{C}_{\mf{a},\mf{b}}\), integers \(m\) and \(n\), and Dirichlet character \(\chi\) modulo \(c\), the \textbf{Sali\'e sum}\index{Sali\'e sum} \(S_{\chi,\mf{a},\mf{b}}(m,n,c)\) relative to \(\mf{a}\) and \(\mf{b}\) is defined by
      \[
        S_{\chi,\mf{a},\mf{b}}(m,n,c) = \sum_{\substack{d \in \mc{D}_{\mf{a},\mf{b}}(c) \\ \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}}}\chi(d)e\left(\frac{ma+nd}{c}\right).
      \]
      Similar as before, this sum is well-defined since \(a\) and \(d\) are determined modulo \(c\) by the Bruhat decomposition and that the \(\chi\) is a character modulo \(c\). 
      \subsubsection*{Hecke Congruence Subgroups}
        In the case of the Hecke congruence subgroup \(\G_{0}(N)\), the Bruhat decomposition simplifies and we recover the usual Kloosterman and Sali\'e sums. As the entries \(a\) and \(d\) in \(\w_{c/d} = \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix}\) are determined modulo \(c\), we find that \(d\) is the inverse of \(a\) modulo \(c\) because \(\det(\w_{c/d}) = 1\). Also, \(\mc{C}_{\infty,\infty} = N\Z_{+}\) and \(\mc{D}_{\infty,\infty}(c) = (\Z/c\Z)^{\ast}\) because if \(\g = \begin{psmallmatrix} \ast & \ast \\ c & d \end{psmallmatrix} \in \G_{0}(N)\) then \(c \equiv 0 \tmod{N}\) and we must have \((c,d) = 1\) as \(\det(\g) = 1\). Moreover, every such pair gives rise to a matrix in \(\G_{0}(N)\). Whence
      \[
        K_{\infty,\infty}(m,n,c) = K(m,n,c) \quad \text{and} \quad S_{\chi,\infty,\infty}(m,n,c) = S_{\chi}(m,n,c),
      \]
      which are the usual Kloosterman and Sali\'e sums respectively. In these cases, we will suppress the dependencies upon the cusps.
  \section{Modular Forms}
    If \(a\) is an integer modulo \(m\) with \((a,m) = 1\) we write \(a^{-1}\) for the inverse of \(a\) modulo \(m\). For any complex \(z\) let
    \[
      e(z) = e^{2\pi iz}.
    \]
    We will distinguish the primitive third root of unity \(\w = e\left(\frac{1}{3}\right)\). Also, all sums and products over a quotient group will be consider to be over a complete set of representatives.
    \subsection{Modular Forms}
      For all all \(\a = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \GL_{2}^{+}(\R)\) and \(z \in \H\), define \(j(\a,z)\) by
      \[
        j(\a,z) = (cz+d).
      \]
      With this notation, \cref{equ:Mobius_transformation_imaginary_part} becomes
      \[
        \Im(\a z) = \det(\a)\frac{\Im(z)}{|j(\a,z)|^{2}}.
      \]
      There is a very useful property that \(j(\a,z)\) satisfies. To state it, let \(\a' = \begin{psmallmatrix} a' & b' \\ c' & d' \end{psmallmatrix} \in \GL_{2}^{+}(\R)\). Then
      \[
        \a\a' = \begin{pmatrix} a'a+b'c & a'b+b'b \\ c'a+d'c & c'b+d'd \end{pmatrix},
      \]
      and from this identity, a short computation shows
      \[
        j(\a'\a,z) =  j(\a',\a z)j(\a,z).
      \]
      This identity is called the \textbf{cocycle condition}\index{cocycle condition} for \(j(\a,z)\). For any nonnegative integer \(k\) and \(\a \in \GL_{2}^{+}(\R)\), we define the \textbf{slash operator}\index{slash operator} \(|_{k}\a:C(\H) \to C(\H)\) to be the linear operator given by
      \[
        (f|_{k}\a)(z) = \det(\a)^{\frac{k}{2}}j(\a,z)^{-k}f(\a z).
      \]
      In the case of \(\a \in \SL_{2}(\R)\), the slash operator takes the simplified form
      \[
        (f|_{k}\a)(z) = j(\a,z)^{-k}f(\a z).
      \]
      In any case, the cocycle condition implies that the slash operator is multiplicative as short computations show
      \[
        (f|_{k}\a'\a)(z) = ((f|_{k}\a')|_{k}\a)(z) \quad \text{and} \quad ((fg)|_{k+\ell}\a)(z) = (f|_{k}\a)(z)(g|_{\ell}\a)(z),
      \]
      for \(f,g \in C(\H)\), positive integers \(k\) and \(\ell\), and any \(\a,\a' \in \GL_{2}^{+}(\Q)\). For fixed \(k\), an operator on \(C(\H)\) is said to be \textbf{invariant}\index{invariant} if it commutes with the slash operators \(|_{k}\a\) for every \(\a \in \SL_{2}(\Q)\).
      
      We can now introduce modular forms. Let \(\G\) be a congruence subgroup of level \(N\) and \(\nu:\G \to \C^{\ast}\) be a finite order homomorphism. We say that a function \(f:\H \to \C\) is \textbf{modular form}\index{modular form} on \(\GH\) of \textbf{weight}\index{weight} \(k\), \textbf{level}\index{level} \(N\), and \textbf{nebentypus}\index{nebentypus} \(\nu\) if the following properties are satisfied:
      \begin{enumerate}[label*=(\roman*)]
        \item \(f\) is holomorphic on \(\H\).
        \item \((f|_{k}\g)(z) = \nu(\g)f(z)\) for all \(\g \in \G\).
        \item \((f|_{k}\g)(z) = O(1)\) for all \(\g \in \SL_{2}(\Z)\).
      \end{enumerate}
      Furthermore, we say \(f\) is a \textbf{cusp form}\index{cusp form} if the additional property is satisfied:
      \begin{enumerate}[label*=(\roman*)]
        \setcounter{enumi}{3}
        \item For all cusps \(\mf{a}\) and positive \(y\), we have
        \[
          \int_{0}^{1}(f|_{k}\s_{\mf{a}})(z)\,dx = 0.
        \]
      \end{enumerate}
      Property (ii) is called the \textbf{modularity condition}\index{modularity condition} and we say \(f\) is \textbf{modular}\index{modular}. The modularity condition can equivalently be expressed as
      \[
        f(\g z) = \nu(\g)j(\g,z)^{k}f(z).
      \]
      We write \(n_{\nu}\) for the order of the nebentypus so that \(\nu\) takes its values in the \(n_{\nu}\)-th roots of unity. Moreover, we say that \(\nu\) is \textbf{regular}\index{regular} at a cusp \(\mf{a}\) if \(\nu(\g_{\mf{a}}) = 1\). Equivalently, \(\nu(\g) = 1\) for every \(\g \in \G_{\mf{a}}\). Property (iii) is called the \textbf{growth condition}\index{growth condition} and we say \(f\) is \textbf{holomorphic at the cusps}\index{holomorphic at the cusps}. By modularity, it suffices to verify the growth condition for a set of scaling matrices associated to a complete set of \(\G\)-inequivalent cusps. Therefore we only have to check this condition for finitely many matrices since the number of cusp classes is finite. Also, the growth condition is equivalent to \((f|_{k}\a)(z) = O(1)\) for all \(\a \in \GL_{2}^{+}(\Q)\). To see this, we require a lemma.

      \begin{lemma}
        Every \(\a \in \GL_{2}^{+}(\Q)\) can be written as \(\a = \g\eta\) for some \(\g \in \SL_{2}(\Z)\) and \(\eta \in \GL_{2}^{+}(\Q)\) with \(\eta = \begin{psmallmatrix} \ast & \ast \\ 0 & \ast \end{psmallmatrix}\).
      \end{lemma}
      \begin{proof}
        Let \(r\) be a positive integer such that \(r\a = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \GL_{2}^{+}(\Z)\). As \(r\a\) has nonzero determinant, we cannot have \(a = c = 0\). Whence we may set \(a' = \frac{a}{(a,c)}\) and \(c' = \frac{c}{(a,c)}\) so that \(a'\) and \(c'\) are relatively prime integers. Then there exists \(\g \in \SL_{2}(\Z)\) with \(\g^{-1} = \begin{psmallmatrix} \ast & \ast \\ -c' & a' \end{psmallmatrix}\). Moreover, a short computation shows
        \[
          \g^{-1}r\a = \begin{pmatrix} \ast & \ast \\ 0 & \ast \end{pmatrix}.
        \]
        The claim is complete upon setting \(\eta = \g^{-1}\a\).
      \end{proof}

      For the equivalence, use this lemma to write \(\a = \g\eta\) for some \(\g \in \SL_{2}(\Z)\) and \(\eta \in \GL_{2}^{+}(\Q)\) with \(\eta = \begin{psmallmatrix} \ast & \ast \\ 0 & \ast \end{psmallmatrix}\). The cocycle condition gives
      \[
        (f|_{k}\a)(z) = \det(\eta)^{\frac{k}{2}}j(\eta,z)(f|_{k}\g)(\eta z),
      \]
      and as \(j(\eta,z)\) is a constant, we have \((f|_{k}\a)(z) = O(1)\) proving the forward implication. The reverse implication is clear since \(\SL_{2}(\Z) \subset \GL_{2}^{+}(\Q)\).
      
      \begin{remark}\label{rem:odd_weight_modular_forms}
        If \(f\) is a weight \(k\) modular form with nebentypus \(\nu\) on \(\GH\) and \(-I \in \G\) then modularity implies
        \[
          f(z) = \nu(-I)(-1)^{k}f(z).
        \]
        Therefore \(\nu(-I) = (-1)^{k}\). This means \(\nu\) cannot be the identity if \(k\) is odd. In particular, there are no nonzero modular forms of odd weight with trivial nebentypus on \(\SL_{2}(\Z)\).  
      \end{remark}
      
      Modular forms also admit Fourier series expansions. First observe that modularity implies
      \[
        (f|_{k}\s_{\mf{a}})(z+1) = \nu(\g_{\mf{a}})(f|_{k}\s_{\mf{a}})(z),
      \]
      which is to say \(f|_{k}\s_{\mf{a}}\) is \(1\)-periodic up to the constant factor \(\nu(\g_{\mf{a}})\). This means we only need to verify the growth condition as \(y \to \infty\). In any case, as \(f|_{k}\s_{\mf{a}}\) is also smooth, it admits an absolutely and uniformly convergent Fourier series expansion. So we may write
      \[
        (f|_{k}\s_{\mf{a}})(z) = \sum_{n \ge 0}a_{\mf{a}}(y,n)e(nx),
      \]
      where the sum is only over nonnegative \(n\) because holomorphy at the cusps forces \(f|_{k}\s_{\mf{a}}\) to be bounded. We can also simplify the Fourier coefficients \(a_{\mf{a}}(y,n)\). Indeed, as \(f|_{k}\s_{\mf{a}}\) is holomorphic it satisfies the Cauchy-Riemann equations so that
      \[
        \frac{1}{2}\left(\frac{\del f|_{k}\s_{\mf{a}}}{\del x}+i\frac{\del f|_{k}\s_{\mf{a}}}{\del y}\right) = 0.
      \]
      Substituting in the Fourier series expansion and equating coefficients we obtain the ODE
      \[
        2\pi na_{\mf{a}}(y,n)+a_{\mf{a}}'(y,n) = 0.
      \]
      Solving this ODE by separation of variables, there exist coefficients \(a_{\mf{a}}(n)\) such that
      \[
        a_{\mf{a}}(y,n) = a_{\mf{a}}(n)e(n(iy)).
      \]
      The coefficients \(a_{\mf{a}}(n)\) are the only part of the Fourier series expansion depending on the cusp \(\mf{a}\) and scaling matrix \(\s_{\mf{a}}\). Using these coefficients instead, \(f\) admits a \textbf{Fourier series}\index{Fourier series} expansion at the \(\mf{a}\) cusp given by
      \[
        (f|_{k}\s_{\mf{a}})(z) = \sum_{n \ge 0}a_{\mf{a}}(n)e(nz),
      \]
      with \textbf{Fourier coefficients}\index{Fourier coefficients} \(a_{\mf{a}}(n)\). In the case \(\mf{a} = \infty\) and \(\s_{\mf{a}} = I\), we will drop these dependences by writing \(f|_{k}\s_{\mf{a}} = f\) and \(a_{\mf{a}}(n) = a(n)\). The Fourier coefficients do not depend upon the choice of scaling matrix used for \(f|_{k}\s_{\mf{a}}\) because
      \begin{equation}\label{equ:cusp_form_independence_of_scaling_matrix_modular}
        (f|_{k}\s_{\mf{a}}T)(z) = (f|_{k}\s_{\mf{a}})(z+1).
      \end{equation}
      Also, from property (iv) we find that \(f\) is a cusp form if and only if \(a_{\mf{a}}(0) = 0\) for every cusp \(\mf{a}\). Moreover, the Fourier coefficients corresponding to \(\G\)-equivalent cusps have a simple relationship. Suppose \(\mf{b}\) and \(\mf{a}\) are \(\G\)-equivalent cusps so that \(\g\mf{b} = \mf{a}\) for some \(\g \in \G\). Then for associated scaling matrices \(\s_{\mf{a}}\) and \(\s_{\mf{b}}\), we have \(\s_{\mf{b}} = \g\s_{\mf{a}}\). Whence modularity gives
      \[
        (f|_{k}\s_{\mf{b}})(z) = \nu(\g)(f|_{k}\s_{\mf{a}})(z),
      \]
      so that the \(n\)-th Fourier coefficient is multiplied by the root of unity \(\nu(\g)\). In particular, the condition \(a_{\mf{a}} = 0\) only depends on the cusp class of \(\mf{a}\). So we only need to verify property (iv) on a complete set of \(\G\)-inequivalent cusps. Of course, if \(\nu(\g) = 1\) the Fourier coefficients are equal. For example, this occurs when the nebentypus is trivial.

      We can also derive a bound for the Fourier coefficients of \(f\) at the \(\mf{a}\) cusp provided \(f\) is a cusp form. This bound is quite straightforward to deduce and turns out to almost be optimal. To this end, consider the integral
      \[
        \int_{0}^{1}(f|_{k}\s_{\mf{a}})(z)\Im(z)^{\frac{k}{2}}e(-nz)\,dx.
      \]
      On the one hand, substitute the Fourier series expansion and use absolute convergence to interchange the sum and the integral. In view of the identity
      \begin{equation}\label{equ:Dirac_integral_representation}
        \int_{0}^{1}e((n-m)x)\,dx = \d_{n-m,0},
      \end{equation}
      for positive integers \(n\) and \(m\), every term integrates to zero except the \(n\)-th term which is \(a_{\mf{a}}(n)\Im(z)^{\frac{k}{2}}\). On the other hand, holomorphy at \(\infty\) implies that the integral is \(O\left(e^{-2\pi n\Im(z)}\right)\). Whence
      \[
        a_{\mf{a}}(n)\Im(z)^{\frac{k}{2}} \ll e^{-2\pi n\Im(z)}.
      \]
      Upon setting \(\Im(z) = \frac{1}{n}\), the right-hand side is uniformly bounded and we obtain
      \[
        a_{\mf{a}}(n) \ll n^{\frac{k}{2}}.
      \]
      This estimate is known as the \textbf{Hecke bound}\index{Hecke bound} for modular forms. It follows from the Hecke bound that
      \[
        (f|_{k}\s_{\mf{a}})(z) = O\left(e^{-2\pi y}\right),
      \]
      upon summing the resulting geometric series. This implies \(f|_{k}\s_{\mf{a}}\) exhibits exponential decay and we say that \(f\) exhibits \textbf{exponential decay at the cusps}\index{exponential decay at the cusps}. This is stronger than simply knowing \(f|_{k}\s_{\mf{a}}\) is bounded on \(\H\) and tends to zero as \(y \to \infty\) which is provided by the fact that \(f\) is a cusp form.

      \subsubsection*{Hecke Congruence Subgroups}
        In the case of the Hecke congruence subgroup \(\G_{0}(N)\), there are a few important simplifications when dealing with modular forms on  \(\G_{0}(N)\backslash\H\). The first, which we have already noted, is that \(\G_{0}(N)\) is reduced \(\infty\). Therefore \(\G_{0}(N)_{\infty} = B_{\G_{0}(N)}\) and we may take \(\s_{\infty} = I\) for the scaling matrix at \(\infty\). The second is that the nebentypus can be induced by a Dirichlet character \(\chi\) modulo \(N\). Let \(q\) be the conductor of \(\chi\) so that \(q \mid N\). For any \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}(N)\) we know that \(c \equiv 0 \tmod{N}\) whence \(a\) is the inverse of \(d\) modulo \(N\) and thus \((d,q) = 1\). We can define a function \(\nu_{\chi}:\G_{0}(N) \to \C^{\ast}\) by
        \[
          \nu_{\chi}(\g) = \chi(d).
        \]
        If \(\g' = \begin{psmallmatrix} a' & b' \\ c' & d' \end{psmallmatrix} \in \G_{0}(N)\), then the relations
        \[
          \g\g' \equiv \begin{pmatrix} \ast & \ast \\ 0 & d'd \end{pmatrix} \pmod{N} \quad \text{and} \quad \g^{-1} = \begin{pmatrix} d & \ast \\ 0 & a \end{pmatrix} \pmod{N},
        \]
        show that
        \[
          \nu_{\chi}(\g\g') = \nu_{\chi}(\g)\nu_{\chi}(\g') \quad \text{and} \quad \nu_{\chi}(\g^{-1}) = \nu_{\chi}(\g)^{-1}.
        \]
        respectively. In other words, \(\nu_{\chi}\) is a homomorphism and it is necessarily of finite order because \(\chi\) is. Therefore \(\nu_{\chi}\) satisfies the assumptions of a nebentypus. It is also regular at \(\infty\). In the case \(f\) has nebentypus \(\nu_{\chi}\), we simply say that \(f\) has \textbf{character}\index{character} \(\chi\) and write
        \[
          \chi(\g) = \nu_{\chi}(\g).
        \]
    \subsection{Poincar\'e Series and Eisenstein Series}
      We will now introduce specific modular forms over \(\GH\). These modular forms will be constructed by averaging the slash operator over \(\G_{\mf{a}}\backslash\G\) for a cusp \(\mf{a}\) of \(\GH\) and are called Poincar\'e series and Eisenstein series where the latter is a special case of the former. 
      
      Fix an integer \(k \ge 3\) and a cusp \(\mf{a}\) with scaling matrix \(\s_{\mf{a}}\). Let \(m\) be a nonnegative integer, \(\nu:\G \to \C^{\ast}\) be a finite order homomorphism that is regular at \(\mf{a}\). We define the \(m\)-th (modular) \textbf{Poincar\'e series}\index{Poincar\'e series} \(P_{m,\nu,\mf{a}}(z)\) of \textbf{index}\index{index} \(m\) and weight \(k\) with nebentypus \(\nu\) on \(\GH\) at the \(\mf{a}\) cusp by
      \[
        P_{m,\nu,\mf{a}}(z) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\conj{\nu}(\g)\left(e(m\,\cdot\,)\bigg|_{k}\s_{\mf{a}}^{-1}\g\right)(z).
      \]
      We call \(m\) the \textbf{index}\index{index} of \(P_{m,\nu,\mf{a}}(z)\). Also, we must assume \(k \ge 3\) is because for \(k = 0,1,2\) the Poincar\'e series need not converge for any \(z \in \H\).

      The Poincar\'e series \(P_{m,\nu,\mf{a}}(z)\) is well-defined as it is independent of the choice of representatives \(\g\) and \(\s_{\mf{a}}\). For the nebentypus, this is easily checked by direct computation using the fact that \(\nu\) is regular at \(\mf{a}\). For the exponential factor, the set of representatives for \(\s_{\mf{a}}^{-1}\g\) is \(B_{\G}\s_{\mf{a}}^{-1}\g\) in view of \(\G_{\mf{a}} = \s_{\mf{a}}B_{\G}\s_{\mf{a}}^{-1}\). So it suffices to show 
      \[
        \left(e(m\,\cdot\,)\bigg|_{k}T\right)(z) = e(mz),
      \]
      which is obvious. Whence \(P_{m,\nu,\mf{a}}(z)\) is well-defined. To see that \(P_{m,\nu,\mf{a}}(z)\) is holomorphic on \(\H\), the Bruhat decomposition for \(\s_{\mf{a}}^{-1}\G\s_{\infty}\) and bounding term by term gives
      \[
        P_{m,\nu,\mf{a}}(z) \ll \sum_{(c,d) \in \Z_{0+}^{2}-\{\mathbf{0}\}}\frac{1}{|cz+d|^{k}}.
      \]
      This latter series is locally absolutely uniformly convergent for \(z \in \H\) as \(k \ge 3\). Hence \(P_{m,\nu,\mf{a}}(z)\) is holomorphic on \(\H\). As for modularity, let \(\eta \in \G\). A short computation using the change of variables \(\eta \mapsto \eta\g^{-1}\) shows
      \[
        (P_{m,\nu,\mf{a}}|_{k}\eta)(z) = \nu(\eta)P_{m,\nu,\mf{a}}(z).
      \]
      To verify the growth condition, we will need a technical lemma.

      \begin{lemma}\label{lem:technical_Poincare_convergence_lemma}
        Let \(a,b > 0\) and consider set
        \[
          S_{a,b} = \{z \in \H:|\Re(z)| \le a \text{ and } \Im(z) \ge b\}.
        \]
        Then there exists a \(\d \in (0,1)\) such that
        \[
          |nz+m| \ge \d|ni+m|,
        \]
        for all integers \(n\) and \(m\) and all \(z \in S_{a,b}\).
      \end{lemma}
      \begin{proof}
        If \(n = 0\) then the claim is obvious as any \(\d\) is sufficient. If \(n \neq 0\) then it is equivalent to prove
        \[
          \left|\frac{z+\frac{m}{n}}{i+\frac{m}{n}}\right| \ge \d.
        \]
        To this end, consider the function
        \[
          f(z,r) = \left|\frac{z+r}{i+r}\right|,
        \]
        for \(z \in S_{a,b}\) and real \(r\). We will prove the stronger statement \(f(z,r) \ge \d\). Clearly \(f(z,r)\) is continuous on \(S_{a,b} \x \R\) and it is also positive there since \(z-r \neq 0\). A short computation shows
        \[
          f(z,r)^{2} \ge \frac{|z|^{2}+r^{2}}{1+r^{2}}.
        \]
        Since \(\frac{r^{2}}{1+r^{2}} \to 1\) as \(r \to \pm\infty\), choose \(Y > b\) such that \(\frac{r^{2}}{1+r^{2}} \ge \frac{1}{4}\) for \(|r| > Y\). Now let
        \[
          S_{a,b}^{Y} = \{z \in \H:|\Re(z)| \le a \text{ and } b \le \Im(z) \le Y\},
        \]
        so that
        \[
          f(z,r) \ge \frac{1}{2},
        \]
        outside of \(S_{a,b}^{Y} \x [-Y,Y]\). But this latter region is compact and so \(f(z,r)\) attains a minimum \(\d' > 0\) on it. Setting \(\d = \min\left(\frac{1}{2},\d'\right)\) completes the proof.
      \end{proof}

      We can now verify the growth condition for \(P_{m,\nu,\mf{a}}(z)\). Choose a cusp \(\mf{b}\) and an associated scaling matrix \(\s_{\mf{b}}\). Using the cocycle condition, Bruhat decomposition for \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\), and bounding term by term shows give
      \[
        (P_{m,\nu,\mf{a}}|_{k}\s_{\mf{b}})(z) \ll \sum_{(c,d) \in \Z_{0+}^{2}-\{\mathbf{0}\}}\frac{1}{|cz+d|^{k}}.
      \]
      Now decompose this last sum as
      \[
        \sum_{(c,d) \in \Z_{0+}^{2}-\{\mathbf{0}\}}\frac{1}{|cz+d|^{k}} = \sum_{d \ge 1}\frac{1}{d^{k}}+\sum_{c \ge 1}\sum_{d \ge 0}\frac{1}{|cz+d|^{k}}.
      \]
      Since the first sum on the right-hand side is bounded, it suffices to show that the double sum is too as \(z \to \infty\). So let \(\Im(z) \ge 1\) and \(\d\) be as in \cref{lem:technical_Poincare_convergence_lemma}. Then for any positive integer \(N\), we may write
      \[
        \sum_{c \ge 1}\sum_{d \ge 0}\frac{1}{|cz+d|^{k}} \le \sum_{c+d \le N}\frac{1}{|cz+d|^{k}}+\frac{1}{\d^{k}}\sum_{c+d > N}\frac{1}{|ci+d|^{k}}.
      \]
      As \(k \ge 3\), the second sum on the right-hand side is the tail of an absolute convergent series. Whence it tends to zero as \(N \to \infty\). As for the first sum, it is finite and each term is bounded. Together this shows that the double sum is bounded as \(z \to \infty\) verifying the growth condition. We collect this work in the following theorem:

      \begin{theorem}\label{thm:Poincare_series_modular}
        The Poincar\'e series
        \[
          P_{m,\nu,\mf{a}}(z) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\conj{\nu}(\g)\left(e(m\,\cdot\,)\bigg|_{k}\s_{\mf{a}}^{-1}\g\right)(z),
        \]
        is a weight \(k\) modular form with nebentypus \(\nu\) on \(\GH\).
      \end{theorem}

      In the case of index zero Poincar\'e series, we write \(E_{\nu,\mf{a}}(z) = P_{0,\nu,\mf{a}}(z)\) and call \(E_{\nu,\mf{a}}(z)\) the (modular) \textbf{Eisenstein series}\index{Eisenstein series} of weight \(k\) and nebentypus \(\nu\) on \(\GH\) at the \(\mf{a}\) cusp. It is defined by
      \[
        E_{\nu,\mf{a}}(z) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\conj{\nu}(\g)\left(1\bigg|_{k}\s_{\mf{a}}^{-1}\g\right)(z).
      \]
      Then we obtain the following theorem as a special case of the former one:

      \begin{theorem}\label{thm:Eisenstein_series_modular}
        The Eisenstein series
        \[
          E_{\nu,\mf{a}}(z) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\conj{\nu}(\g)\left(1\bigg|_{k}\s_{\mf{a}}^{-1}\g\right)(z),
        \]
        is a weight \(k\) modular form with nebentypus \(\nu\) on \(\GH\).
      \end{theorem}
    \subsection{The Valence Formula and Petersson Inner Product}
      Let \(\mc{M}_{k}(\G,\nu)\) denote the complex vector space of all weight \(k\) modular forms with nebentypus \(\nu\) on \(\GH\) and write \(\mc{S}_{k}(\G,\nu)\) for the corresponding subspace of cusp forms. In either case, if \(\nu\) is trivial we will suppress this dependence. Note that if \(\G_{1}\) and \(\G_{2}\) are two congruence subgroups such that \(\G_{1} \subseteq \G_{2}\) then we have the inclusions
      \[
        \mc{M}_{k}(\G_{2},\nu) \subseteq \mc{M}_{k}(\G_{1},\nu) \quad \text{and} \quad \mc{S}_{k}(\G_{2},\nu) \subseteq \mc{S}_{k}(\G_{1},\nu).
      \]
      The vector space \(\mc{M}_{k}(\G,\nu)\), and hence \(\mc{S}_{k}(\G,\nu)\) as well, turns out to be finite dimensional. This will be accomplished by showing that any \(f \in \mc{M}_{k}(\G,\nu)\) is determined by finitely many of its Fourier coefficients. In fact, this will follow from an exact formula relating the weight \(k\), the index \(d_{\G}\), and the zeros of \(f\). This is known as the valence formula and we require some notation to state it. For any \(z \in \H\), let \(v_{z}(f)\) be the index of the first nonzero term in the Taylor series expansion of \(f\) about \(z\). Equivalently, \(v_{z}(f)\) is the order of vanishing of \(f\) at \(z\). Note that \(v_{z}(f)\) is necessarily nonnegative as \(f\) is holomorphic and
      \[
        v_{\g z}(f) = v_{z}(f),
      \]
      for any \(\g \in \G\) by modularity. For a cusp \(\mf{a}\) of \(\GH\), we let \(v_{\mf{a}}(f)\) be the index of the first nonzero term in the Fourier series expansion of \(f\) at the \(\mf{a}\) cusp. That is, \(v_{\mf{a}}(f)\) is the order of vanishing of \(f|_{k}\s_{\mf{a}}\) at \(\infty\). To show \(v_{\mf{a}}(f)\) is well-defined, we need to verify that it is independent of the choice of scaling matrix \(\s_{\mf{a}}\). This follows from \cref{equ:cusp_form_independence_of_scaling_matrix_modular} since scaling matrices are determined up to composition on the right by an element of \(\G_{\infty}\). Also, \(v_{\mf{a}}(f)\) is again nonnegative by the holomorphy of \(f\) and
      \[
        v_{\mf{a}'}(f) = v_{\mf{a}}(f),
      \]
      for any cusp \(\mf{a}'\) in the same cusp class as \(\mf{a}\) by modularity.

      Our method for proving the valance formula will be to prove it for the modular group via an application of the argument principle and then extend it to the congruence subgroup \(\G\). In order to do this, we will need to show how to construct a modular form on \(\SL_{2}(\Z)\backslash\H\) given one on \(\GH\). The following lemma provides the answer:

      \begin{lemma}\label{lem:lifting_lemma}
        Let \(f \in \mc{M}_{k}(\G,\nu)\) and set
        \[
          F(z) = \prod_{\b \in \G\backslash\SL_{2}(\Z)}((f|_{k}\b)(z))^{n_{\nu}}.
        \]
        Then \(F \in \mc{M}_{kn_{\nu}d_{\G}}(\SL_{2}(\Z))\).
      \end{lemma}
      \begin{proof}
        If \(f\) is zero then so is \(F\) and the claim is obvious. So assume \(f\) is nonzero. First we must show that \(F\) is well-defined which is to say that it is independent of the representatives \(\b\). Indeed, if \(\b\) and \(\b'\) belong to the same orbit then \(\b'\b^{-1} \in \G\). Modularity and that \(\nu\) is of order \(n_{\nu}\) together show
        \[
          ((f|_{k}\b')(z))^{n_{\nu}} = ((f|_{k}\b)(z))^{n_{\nu}},
        \]
        which proves \(F\) is well-defined. Since the product is finite, holomorphy of \(F\) is clear. To prove modularity, let \(\g \in \SL_{2}(\Z)\). Because \(\b\) runs over a complete set of representatives for \(\G\backslash\SL_{2}(\Z)\) so does \(\b\g\). Modularity then follows from a short computation because this permutes the choice of coset representatives. The growth condition, follows from that of \(f\) and the definition of \(F\). This proves \(F \in \mc{M}_{kn_{\nu}d_{\G}}(\SL_{2}(\Z))\). 
      \end{proof}  
      
      We can now state and prove the \textbf{valence formula}\index{valence formula}.

      \begin{theorem*}[Valence formula]
        Suppose \(f \in \mc{M}_{k}(\G,\nu)\) is nonzero. Then
        \[
          \sum_{\mf{a} \in \G\backslash\what{\Q}}v_{\mf{a}}(f)+\sum_{z \in \SL_{2}(\Z)\backslash\mc{F}_{\G}}\frac{2v_{z}(f)}{|\G_{z}|} = \frac{kd_{\G}}{12}.
        \]
      \end{theorem*}
      \begin{proof}
        We will first prove the valence formula for the modular group and then extend the result to \(\G\). Let \(F \in \mc{M}_{k}(\SL_{2}(\Z))\) be nonzero so that its zeros are isolated. We claim that all of the zeros of \(F\) satisfy \(\Im(z) < T\) for some positive \(T\). To see this, let the Fourier series expansion of \(F\) be given by
        \[
          F(z) = \sum_{n \ge 0}a(n)e(nz).
        \]
        Note that \(F\) is bounded as \(z \to \infty\) since it is holomorphic at \(\infty\). Therefore, under the change of variables \(e(z) \mapsto q\) this means
        \[
          G(q) = \sum_{n \ge 0}a(n)q^{n},
        \]
        converges absolutely provided \(|q| < 1\) and where \(G(0) = \lim_{z \to \infty}F(z)\). Then \(G\) is holomorphic on the interior of the unit disk and the order of vanishing of \(G\) at \(0\) is exactly \(v_{\infty}(F)\). Therefore we may write
        \[
          G(q) = q^{v_{\infty}(F)}H(q),
        \]
        where \(H\) is holomorphic on the interior of the unit disk and \(H(0) \neq 0\). Whence there exists a positive \(r\) such that \(G(q)\) is nonzero for \(0 < |q| < r\). But then \(F(z)\) is nonzero for \(e^{-2\pi ny} < r\) which is to say \(y > -\frac{\log(r)}{2\pi y}\). Taking \(T > -\frac{\log(r)}{2\pi y}\) proves the claim.
        
        It follows that every zero \(\rho\) of \(F\) has ordinate less than \(T\). Moreover, \(\g\rho\) is a zero for every \(\g \in \SL_{2}(\Z)\) by modularity. For our choice of \(T\), let \(\eta = \sum_{i}\eta_{i}\) be the contour in \cref{fig:valence_formula_contour} where the horizontal line is along \(t = T\) and the remaining contour is along the boundary of \(\mc{F}\) except for indentations of radius \(\e\) around possible zeros of \(F\) along this boundary as well as the points \(i\), \(\w\), and \(1+\w\). Moreover, the paths are chosen to be symmetric with respect to the actions of \(S\) and \(T\) so that each zero \(\rho\) belonging to \(\mc{F}\) has exactly one representative of its orbit occurring inside \(\eta\) except for when \(\rho = i,\w,1+\w\) which are excluded. As \(v_{z}(F) = 0\) for every \(z \in \mc{F}-\{i,\w,1+\w\}\) that is not a zero of \(F\), the argument principle gives
        \[
          \frac{1}{2\pi i}\int_{\eta}\frac{F'}{F}(z)dz = \asum_{z \in \SL_{2}(\Z)\backslash\mc{F}}\frac{2v_{z}(F)}{|\SL_{2}(\Z)_{z}|},
        \]
        where the \(\ast\) indicates that we are excluding the orbits of \(i\) and \(\w\). Now define integrals
        \[
          I_{i}(\e) = \int_{\eta_{i}}\frac{F'}{F}(z)dz,
        \]
        so that
        \[
          \frac{1}{2\pi i}\int_{\eta}\frac{F'}{F}(z)dz = \sum_{i}I_{i}(\e).
        \]

        \begin{figure}[ht]
          \centering
          \begin{tikzpicture}[scale=3]
            \def\xmin{-1.5} \def\xmax{1.5}
            \def\ymin{1} \def\ymax{4.5}
            \draw[thick] (\xmin,1) -- (\xmax,1);
            \draw[thick] (0,\ymin) -- (0,\ymax);

            \draw[->-] (1,3.6) -- (1,4);
            \draw (1,3.4) arc (270:90:0.1);
            \draw[->-] (1,3.1) -- (1,3.4);
            \draw[dashed] (1,2.9)-- (1,3.1);
            \draw[->-] (1,2.6) -- (1,2.9);
            \draw (1,2.4) arc (270:90:0.1);
            \draw[->-] ({2*cos(60)},{2*sin(60)+0.1}) -- (1,2.4);
            \draw (60:2) +(90:0.1) arc (90:{150+acos(799/800)}:0.1);

            \draw[->-] (1,4) -- (-1,4);

            \draw[->-] (-1,4) -- (-1,3.6);
            \draw (-1,3.5) +(90:0.1) arc (90:270:0.1);
            \draw[->-] (-1,3.4) -- (-1,3.1);
            \draw[dashed] (-1,3.1) -- (-1,2.9);
            \draw[->-] (-1,2.9) -- (-1,2.6);
            \draw (-1,2.5) +(90:0.1) arc (90:270:0.1);
            \draw[->-] (-1,2.4) -- ({2*cos(120)},{2*sin(120)+0.1});
            \draw (120:2) +(90:0.1) arc (90:{30-acos(799/800)}:0.1);

            \draw ({120-acos(799/800)}:2) arc ({120-acos(799/800)}:{110+acos(799/800)}:2);
            \draw (110:2) +({200+(1/2)*acos(799/800)}:0.1) arc (200:380:0.1);
            \draw ({110-acos(799/800)}:2) arc ({110-acos(799/800)}:{100+acos(799/800)}:2);
            \draw[dashed] ({100+acos(799/800)}:2) arc ({100+acos(799/800)}:{100-acos(799/800)}:2);
            \draw ({100-acos(799/800)}:2) arc ({100-acos(799/800)}:{90+acos(799/800)}:2);
            \draw[->-] (90:2) +({180+(1/2)*acos(799/800)}:0.1) arc (180:0:0.1);
            \draw ({90-acos(799/800)}:2) arc ({90-acos(799/800)}:{80+acos(799/800)}:2);
            \draw[dashed] ({80+acos(799/800)}:2) arc ({80+acos(799/800)}:{80-acos(799/800)}:2);
            \draw ({80-acos(799/800)}:2) arc ({80-acos(799/800)}:{70+acos(799/800)}:2);
            \draw (70:2) +({160+(1/2)*acos(799/800)}:0.1) arc (160:-20:0.1);
            \draw ({70-acos(799/800)}:2) arc ({70-acos(799/800)}:{60+acos(799/800)}:2);

            \node at (120:2) [circle,fill,inner sep=1pt]{};
            \node at (110:2) [circle,fill,inner sep=1pt]{};
            \node at (90:2) [circle,fill,inner sep=1pt]{};
            \node at (70:2) [circle,fill,inner sep=1pt]{};
            \node at (60:2) [circle,fill,inner sep=1pt]{};
            \node at (1,4) [circle,fill,inner sep=1pt]{};
            \node at (-1,4) [circle,fill,inner sep=1pt]{};

            \node at (1,2.5) [circle,fill,inner sep=1pt]{};
            \node at (1,3.5) [circle,fill,inner sep=1pt]{};
            \node at (-1,2.5) [circle,fill,inner sep=1pt]{};
            \node at (-1,3.5) [circle,fill,inner sep=1pt]{};

            \node at (0,4) [above right] {\tiny{\(\eta_{1}\)}};

            \node at (-1,3) [left] {\tiny{\(\eta_{2}\)}};
            \node at (1,3) [right] {\tiny{\(\eta_{8}\)}};

            \node at (100:2) [below] {\tiny{\(\eta_{4}\)}};
            \node at (0,2.1) [above left] {\tiny{\(\eta_{5}\)}};
            \node at (80:2) [below] {\tiny{\(\eta_{6}\)}};

            \node at ($(120:2)+(67.5:0.05)$) [above right] {\tiny{\(\eta_{3}\)}};
            \node at ($(60:2)+(112.5:0.05)$) [above left] {\tiny{\(\eta_{7}\)}};
          \end{tikzpicture}
          \caption{An indented standard fundamental domain contour.} \label{fig:valence_formula_contour}
        \end{figure}

        \noindent We will compute the integrals \(I_{i}(\e)\) and then take the limit as \(\e \to 0\). For the integrals along \(\eta_{2}\) and \(\eta_{8}\), modularity implies \(F(z+1) = F(z)\) and observe that \(T^{-1}\eta_{8} = -\eta_{2}\). Whence
        \[
          I_{2}(\e)+I_{8}(\e) = 0,
        \]
        so that these integrals cancel. For the integral along \(\eta_{1}\), the change of variables \(e(z) \mapsto q\) takes \(\eta_{1}\) to the circle \(|q| = e^{-2\pi T}\) transversed once with negative orientation and \(F(z)\) is taken to \(G(q)\). Then from our previous discussion of \(G(q)\), we have
        \[
          I_{1}(\e) = -v_{\infty}(F).
        \]
        The integrals along \(\eta_{3}\) and \(\eta_{7}\), as well as \(\eta_{5}\), are computed in a similar manner. Let \(\t_{\e}\) be the angle such that \(\eta_{3}\) and \(\eta_{7}\) end and begin at angles \(\frac{\pi}{6}+\t_{\e}\) and \(\frac{5\pi}{6}-\t_{\e}\) relative to \(\w\) and \(1+\w\) respectively. For \(\eta_{3}\), write \(F(z) = (z-\w)^{v_{\w}(F)}F_{\w}(z)\) where \(F_{\w}(z)\) holomorphic and nonzero at \(\w\). Then 
        \[
          I_{3}(\e) = \frac{1}{2\pi i}\int_{\eta_{4}}\left(\frac{v_{\w}(F)}{z-\w}+\frac{F_{\w}'}{F_{\w}}(z)\right)\,dz,
        \]
        and the change of variables \(z \mapsto \w+\e e^{i\t}\) shows
        \[
          I_{3}(\e) = -\frac{\frac{\pi}{3}-\t_{\e}}{2\pi}v_{\w}(F)+O(\e).
        \]
        Since \(\t_{\e} \to 0\) as \(\e \to 0\), it follows that
        \[
          \lim_{\e \to 0}I_{3}(\e) = -\frac{v_{\w}(F)}{|\SL_{2}(\Z)_{\w}|},
        \]
        as \(|\SL_{2}(\Z)_{\w}| = 6\) by \cref{prop:stabilizer_subgroup}. We argue similarly for \(\eta_{7}\). Write \(F(z) = (z-(1+\w))^{v_{1+\w}(F)}F_{1+\w}(z)\) where \(F_{1+\w}(z)\) holomorphic and nonzero at \(1+\w\). Then
        \[
          I_{7}(\e) = \frac{1}{2\pi i}\int_{\eta_{7}}\left(\frac{v_{1+\w}(F)}{z-(1+\w)}+\frac{F_{1+\w}'}{F_{1+\w}}(z)\right)\,dz,
        \]
        and the change of variables \(z \mapsto (1+\w)+\e e^{i\t}\) shows
        \[
          I_{7}(\e) = \frac{\frac{\pi}{3}-\t_{\e}}{2\pi}v_{1+\w}(F)+O(\e).
        \]
        Whence
        \[
          \lim_{\e \to 0}I_{7}(\e) = -\frac{v_{1+\w}(F)}{|\SL_{2}(\Z)_{1+\w}|},
        \]
        where \(|\SL_{2}(\Z)_{1+\w}| = 6\) by \cref{prop:stabilizer_subgroup}. For the integral along \(\eta_{5}\), write \(F(z) = (z-i)^{v_{i}(F)}F_{i}(z)\) where \(F_{i}(z)\) is holomorphic and nonzero at \(i\). Then
        \[
          I_{5}(\e) = \frac{1}{2\pi i}\int_{\eta_{5}}\left(\frac{v_{i}(F)}{z-(i)}+\frac{F_{i}'}{F_{i}}(z)\right)\,dz,
        \]
        and the change of variables \(z \mapsto i+\e e^{i\t}\) gives
        \[
          I_{5}(\e) = -\frac{v_{i}(F)}{2}+O(\e).
        \]
        Therefore
        \[
          \lim_{\e \to 0}I_{5}(\e) = -\frac{2v_{i}(F)}{|\SL_{2}(\Z)_{i}|},
        \]
        as \(|\SL_{2}(\Z)_{i}| = 4\) by \cref{prop:stabilizer_subgroup}. For the integrals along \(\eta_{4}\) and \(\eta_{6}\), let \(C_{\e}\) be the finite union of segments along \(\eta_{4}\) that lie on the boundary of \(\mc{F}\). Modularity implies \(F\left(-\frac{1}{z}\right) = z^{k}F(z)\) and notice that \(S^{-1}\eta_{6} = -\eta_{4}\). Hence
        \[
          I_{4}(\e)+I_{6}(\e) = -\frac{1}{2\pi i}\int_{C_{\e}}\frac{k}{z}\,dz.
        \]
        As \(\e \to 0\), \(C_{\e}\) tends to the arc on the unit circle between radii \(\frac{\pi}{2}\) and \(\frac{2\pi}{3}\) with negative orientation. From the change of variables \(z \mapsto e^{i\t}\), we find that
        \[
          \lim_{\e \to 0}\left(I_{4}(\e)+I_{6}(\e)\right) = \frac{k}{12}.
        \]
        Altogether, this means
        \begin{equation}\label{equ:valence_formula_9}
          \lim_{\e \to 0}\frac{1}{2\pi i}\int_{\eta}\frac{F'}{F}(z)dz = \frac{k}{12}-v_{\infty}(F)-\frac{v_{\w}(F)}{|\SL_{2}(\Z)_{\w}|}-\frac{v_{1+\w}(F)}{|\SL_{2}(\Z)_{1+\w}|}-\frac{2v_{i}(F)}{|\SL_{2}(\Z)_{i}|},
        \end{equation}
        whence
        \[
          v_{\infty}(F)+\frac{v_{\w}(F)}{|\SL_{2}(\Z)_{\w}|}+\frac{v_{1+\w}(F)}{|\SL_{2}(\Z)_{1+\w}|}+\frac{2v_{i}(F)}{|\SL_{2}(\Z)_{i}|}+\asum_{z \in \SL_{2}(\Z)\backslash\mc{F}}\frac{2v_{z}(F)}{|\SL_{2}(\Z)_{z}|} = \frac{k}{12}.
        \]
        Since \(\w\) and \(1+\w\) are \(\SL_{2}(\Z)\)-equivalent, \(v_{\w}(F) = v_{1+\w}(F)\) and \(|\SL_{2}(\Z)_{\w}| = |\SL_{2}(\Z)_{1+\w}|\) by \cref{prop:stabilizer_subgroup}. So the previous identity becomes
        \[
          v_{\infty}(F)+\sum_{z \in \SL_{2}(\Z)\backslash\mc{F}}\frac{2v_{z}(F)}{|\SL_{2}(\Z)_{z}|} = \frac{k}{12},
        \]
        which is precisely the claim for the modular group. It remains to prove the claim for \(\G\). So let \(f \in \mc{M}_{k}(\G,\nu)\) be nonzero. By \cref{lem:lifting_lemma} we may take
        \[
          F(z) = \prod_{\b \in \G\backslash\SL_{2}(\Z)}((f|_{k}\b)(z))^{n_{\nu}},
        \]
        and obtain
        \[
          v_{\infty}(F)+\sum_{z \in \SL_{2}(\Z)\backslash\mc{F}}\frac{2v_{z}(F)}{|\SL_{2}(\Z)_{z}|} = \frac{kmd_{\G}}{12}.
        \]
        Observe that the Fourier series expansion of \(F\) is a product of those for \(f\) over a complete set of \(\G\)-inequivalent cusps each with multiplicity \(m\). Therefore the index of the first nonzero term in the Fourier series expansion of \(F\) is
        \[
          v_{\infty}(F) = \sum_{\mf{a} \in \G\backslash\what{\Q}}mv_{\mf{a}}(f).
        \]
        Lastly, modularity implies \(F(z) = 0\) if and only if \(f(\b z) = 0\) for some \(\b\) in which case the zero is of multiplicity \(m\). From this and the orbit-stabilizer theorem, we find that
        \[
          \frac{2v_{z}(F)}{|\SL_{2}(\Z)_{z}|} = \sum_{\b \in \G\backslash\SL_{2}(\Z)}\frac{2mv_{\b z}(f)}{|\G_{\b z}|}.
        \]
        But then \cref{prop:fundamental_domain_congruence_subgroup} further implies
        \[
          \sum_{z \in \SL_{2}(\Z)\backslash\mc{F}}\frac{2v_{z}(F)}{|\SL_{2}(\Z)_{z}|} = \sum_{z \in \G\backslash\mc{F}_{\G}}\frac{2mv_{z}(f)}{|\G_{z}|}.
        \]
        Substituting these identities into the formula for the modular group gives
        \[
          \sum_{\mf{a} \in \G\backslash\what{\Q}}v_{\mf{a}}(f)+\sum_{z \in \SL_{2}(\Z)\backslash\mc{F}_{\G}}\frac{2v_{z}(f)}{|\G_{z}|} = \frac{kd_{\G}}{12},
        \]
        as desired.
      \end{proof}
      
      With the valence formula in hand, it is not hard to show that \(\mc{M}_{k}(\G,\nu)\) is finite dimensional.

      \begin{theorem}\label{thm:modular_forms_finite_dimensional}
        \(\mc{M}_{k}(\G,\nu)\) is finite dimensional. In particular, \(\mc{S}_{k}(\G,\nu)\) is too.
      \end{theorem}
      \begin{proof}
        Let \(f \in \mc{M}_{k}(\G,\nu)\). Recall that \(v_{\mf{a}}(f)\) and \(v_{z}(f)\) are nonnegative. In particular, \(v_{\infty}(f)\) is nonnegative and the valence formula implies \(v_{\infty}(f) \le \frac{kd_{\G}}{12}\) whenever \(f\) is nonzero. Let \(n\) be a positive integer such that \(n \ge \frac{kd_{\G}}{12}+1\) and consider the linear map \(F:\mc{M}_{k}(\G,\nu) \to \C^{n}\) sending \(f\) to its first \(n\) Fourier coefficients. Then \(F\) is injective since \(v_{\infty}(f) < n\) and hence \(\mc{M}_{k}(\G,\nu)\) is finite dimensional. The second statement follows immediately.
      \end{proof}

      For further developments, we will require the Petersson inner product. For \(f,g \in \mc{S}_{k}(\G,\nu)\) we define their \textbf{Petersson inner product}\index{Petersson inner product} \(\<f,g\>_{\G}\) by
      \[
        \<f,g\>_{\G} = \frac{1}{V_{\G}}\int_{\GH}f(z)\conj{g(z)}\Im(z)^{k}\,d\mu.
      \]
      If the congruence subgroup \(\G\) is clear from context we will suppress the dependence upon it. The integral is well-defined because the integrand is \(\G\)-invariant. Moreover, as \(f\) and \(g\) have exponential decay at the cusps, the integral is also locally absolutely uniformly convergent. We also extend the Petersson inner product to any complex functions \(f\) and \(g\) on \(\H\) provided the integrand is \(\G\)-invariant and the integral is locally absolutely uniformly convergent.

      The Petersson inner product makes \(\mc{S}_{k}(\G,\nu)\) into a complex Hilbert space. Indeed, it is clearly linear on \(\mc{S}_{k}(\G,\nu)\). It is also positive definite since
      \[
        \<f,f\> = \frac{1}{V_{\G}}\int_{\GH}|f(z)|^{2}\Im(z)^{k}\,d\mu,
      \]
      which is nonnegative and zero if and only if \(f\) is identically zero. A short computation together using the fact that \(\conj{d\mu} = d\mu\), which holds since \(d\mu = \frac{dx\,dy}{y^{2}}\), proves conjugate symmetry. Whence \(\mc{S}_{k}(\G,\nu)\) is a complex inner product space with respect to the Petersson inner product. Since \(\mc{S}_{k}(\G,\nu)\) is finite dimensional by \cref{thm:modular_forms_finite_dimensional}, it follows that \(\mc{S}_{k}(\G,\nu)\) is a complex Hilbert space.
    \subsection{Double Coset Operators}
      There are also linear operators that act on the space of modular forms. In fact, these operators allow us to transfer between modular forms on different congruence subgroups. They are defined via double cosets which we now study.

      Let \(\G_{1}\) and \(\G_{2}\) be two congruence subgroups. Since congruence subgroups are preserved under intersection, it follows from \cref{lem:coset_lemma_1} that \(\a^{-1}\G_{1}\a \cap \G_{2}\) is also a congruence subgroup for any \(\a \in \GL_{2}^{+}(\Q)\). In this setting, consider the double coset
      \[
        \G_{1}\a\G_{2} = \{\g_{1}\a\g_{2}:\g_{1} \in \G_{1} \text{ and } \g_{2} \in \G_{2}\}.
      \]
      Note that \(\G_{1}\) acts on \(\G_{1}\a\G_{2}\) by left multiplication so that it decomposes into a disjoint union of orbits. In other words, we have
      \[
        \G_{1}\a\G_{2} = \bigcup_{\b \in \G_{1}\backslash\G_{1}\a\G_{2}}\G_{1}\b.
      \]
      It turns out that this union is finite. To see this, we need to relate the orbit space \(\G_{1}\backslash\G_{1}\a\G_{2}\) to a quotient of \(\G_{2}\) with respect to the action of some subgroup. This will be the congruence subgroup \(\a^{-1}\G_{1}\a \cap \G_{2}\). As this subgroup acts on \(\G_{2}\) by left multiplication, we again have an orbit space \((\a^{-1}\G_{1}\a \cap \G_{2})\backslash\G_{2}\). These orbit spaces are related.

      \begin{lemma}\label{lem:coset_lemma_2}
        Let \(\G_{1}\) and \(\G_{2}\) be congruence subgroups and let \(\a \in \GL_{2}^{+}(\Q)\). Then the right multiplication map
        \[
          \G_{2} \to \G_{1}\backslash\G_{1}\a\G_{2} \qquad \g_{2} \mapsto \G_{1}\a\g_{2},
        \]
        induces a bijection from \((\a^{-1}\G_{1}\a \cap \G_{2})\backslash\G_{2}\) to \(\G_{1}\backslash\G_{1}\a\G_{2}\).
      \end{lemma}
      \begin{proof}
        This map is \((\a^{-1}\G_{1}\a \cap \G_{2})\)-invariant so that it induces a map on the quotient. Indeed, if \(\g \in \a^{-1}\G_{1}\a \cap \G_{2}\) then \(\g = \a^{-1}\g_{1}\a\) for some \(\g_{1} \in \G_{1}\). Thus \(\G_{1}\a\g\g_{2} = \G_{1}\a\g_{2}\) as claimed.

        We now show that the induced map is a bijection. For injectivity, let \(\g_{2}\) and \(\g'_{2}\) be representatives of orbits of \((\a^{-1}\G_{1}\a \cap \G_{2})\backslash\G_{2}\) such that \(\G_{1}\a\g_{2} = \G_{1}\a\g'_{2}\). This implies \(\a\g_{2}(\g'_{2})^{-1} \in \G_{1}\a\) and so \(\g_{2}(\g'_{2})^{-1} \in \a^{-1}\G_{1}\a\). But we also have \(\g_{2}(\g'_{2})^{-1} \in \G_{2}\) and these two facts together imply that \(\g_{2}(\g'_{2})^{-1} \in \a^{-1}\G_{1}\a \cap \G_{2}\). Hence
        \[
          (\a^{-1}\G_{1}\a \cap \G_{2})\g_{2} = (\a^{-1}\G_{1}\a \cap \G_{2})\g'_{2},
        \]
        from which injectivity follows. For surjectivity, any representative \(\b\) of an orbit in \(\G_{1}\backslash\G_{1}\a\G_{2}\) is of the form \(\b = \g_{1}\a\g_{2}\) for some \(\g_{1} \in \G_{1}\) and \(\g_{2} \in \G_{2}\). But then \(\g_{2}\) represents an orbit of \((\a^{-1}\G_{1}\a \cap \G_{2})\backslash\G_{2}\) mapping to the orbit represented by \(\b\) as \(\G_{1}\b = \G_{1}\a\g_{2}\). This shows surjectivity.
      \end{proof}

      With this lemma in hand, we can prove that the aforementioned disjoint union is finite.

      \begin{proposition}\label{prop:double_congruence_subgroup_coset_decomposition_is_finite}
        Let \(\G_{1}\) and \(\G_{2}\) be congruence subgroups and let \(\a \in \GL_{2}^{+}(\Q)\). Then the disjoint union
        \[
          \G_{1}\a\G_{2} = \bigcup_{\b \in \G_{1}\backslash\G_{1}\a\G_{2}}\G_{1}\b,
        \]
        is finite.
      \end{proposition}
      \begin{proof}
        By \cref{lem:coset_lemma_2}, the number of orbits of \(\G_{1}\backslash\G_{1}\a\G_{2}\) is in bijection with those of \((\a^{-1}\G_{1}\a \cap \G_{2})\backslash\G_{2}\) which is \([\G_{2}:\a^{-1}\G_{1}\a \cap \G_{2}]\). By \cref{lem:coset_lemma_1}, \(\a^{-1}\G_{1}\a \cap \SL_{2}(\Z)\) is a congruence subgroup and thus \(\a^{-1}\G_{1}\a \cap \G_{2}\) is as well. It follows that \([\G_{2}:\a^{-1}\G_{1}\a \cap \G_{2}] \le d_{\a^{-1}\G_{1}\a \cap \G_{2}}\) where \(d_{\a^{-1}\G_{1}\a \cap \G_{2}}\) is finite which completes the proof.
      \end{proof}

      We are ready to introduce a class of general operators depending upon double cosets. First, we define an operator closely related to the slash operator. For any nonnegative integer \(k\) and any \(\a \in \GL_{2}^{+}(\Q)\) we define the \textbf{double slash operator}\index{double slash operator} \(\|_{k}\a:C(\H) \to C(\H)\) to be the linear operator given by
      \[
        (f\|_{k}\a)(z) = \det(\a)^{k-1}j(\a,z)^{-k}f(\a z).
      \]
      In the case of \(\a \in \SL_{2}(\R)\), the double slash operator takes the simplified form
      \[
        (f\|_{k}\a)(z) = j(\a,z)^{-k}f(\a z).
      \]
      The relationship to the slash operator is
      \begin{equation}\label{equ:relationship_between_slash_operators}
        (f\|_{k}\a)(z) = \det(\a)^{\frac{k}{2}-1}(f|_{k}\a)(z).
      \end{equation}
      It follows that the double slash operator is multiplicative as we have
      \[
        (f\|_{k}\a'\a)(z) = ((f\|_{k}\a')|_{k}\a)(z) \quad \text{and} \quad ((fg)\|_{k+\ell}\a)(z) = (f\|_{k}\a)(z)(g\|_{\ell}\a)(z),
      \]
      for \(f,g \in C(\H)\), positive integers \(k\) and \(\ell\), and any \(\a,\a' \in \GL_{2}^{+}(\Q)\). Also, if \(f \in \mc{M}_{k}(\G,\nu)\) then modularity may be expressed as
      \[
        (f\|_{k}\g)(z) = \nu(\g)f(z),
      \]
      for all \(\g \in \G\). The reason for introducing the double slash operator is that it will be easier to work with when discussing Fourier coefficients of modular forms.
      
      Now for any two congruence subgroups \(\G_{1}\) and \(\G_{2}\) and any \(\a \in \GL_{2}^{+}(\Q)\), we define the \textbf{double coset operator}\index{double coset operator} \([\G_{1}\a\G_{2}]_{k}\) to be the linear operator on \(\mc{M}_{k}(\G_{1})\) given by
      \[
        (f[\G_{1}\a\G_{2}]_{k})(z) = \sum_{\b \in \G_{1}\backslash\G_{1}\a\G_{2}}(f\|_{k}\b)(z).
      \]
      This sum is finite by \cref{prop:double_congruence_subgroup_coset_decomposition_is_finite}. It remains to check that \(f[\G_{1}\a\G_{2}]_{k}\) is well-defined which amounts to showing that the sum is independent of the representatives \(\b\) used. Indeed, if \(\b\) and \(\b'\) belong to the same orbit then \(\b' = \g\b\) for some \(\g \in \G_{1}\). Modularity implies
      \[
        (f\|_{k}\b')(z) = (f\|_{k}\b)(z),
      \]
      which proves that \([\G_{1}\a\G_{2}]_{k}\) is well-defined. In fact, the double coset operator takes \(\mc{M}_{k}(\G_{1})\) to \(\mc{M}_{k}(\G_{2})\) and preserves the subspaces of cusp forms.

      \begin{proposition}\label{prop:double_coset_operator_preserves_subspaces_modular}
        For any two congruence subgroups \(\G_{1}\) and \(\G_{2}\), \([\G_{1}\a\G_{2}]_{k}\) maps \(\mc{M}_{k}(\G_{1})\) into \(\mc{M}_{k}(\G_{2})\). It also preserves the subspaces of cusp forms.
      \end{proposition}
      \begin{proof}
        Let \(f \in \mc{M}_{k}(\G_{1})\). Holomorphy is immediate since the sum in \(f[\G_{1}\a\G_{2}]_{k}\) is finite. For modularity, let \(\g \in \G_{2}\). As \(\b\) runs over a complete set of representatives for \(\G_{1}\backslash\G_{1}\a\G_{2}\) so does \(\b\g\). Modularity then follows from a short computation because this permutes the choice of coset representatives. For the growth condition, let \(\s_{\mf{a}}\) be a scaling matrix for a cusp \(\mf{a}\) of \(\G_{2}\backslash\H\). For any representative \(\b\), observe that \(\b\s_{\mf{a}}\infty = \mf{b}\) for some cusp \(\mf{b}\) of \(\G_{1}\backslash\H\). Then
        \[
          ((f[\G_{1}\a\G_{2}]_{k})|_{k}\s_{\mf{a}})(z) = \sum_{\b \in \G_{1}\backslash\G_{1}\a\G_{2}}\det(\b)^{\frac{k}{2}-1}(f|_{k}\b\s_{\mf{a}})(z),
        \]
        and so the growth condition follows from that of \(f\). This proves the first statement. The second statement follows from this identity since \(f[\G_{1}\a\G_{2}]_{k}\) is a cusp form if \(f\) is.
      \end{proof}
  \section{Arithmetic of Modular Forms on Hecke Congruence Subgroups}
    If \(a\) is an integer modulo \(m\) with \((a,m) = 1\) we write \(a^{-1}\) for the inverse of \(a\) modulo \(m\). For any complex \(z\) let
    \[
      e(z) = e^{2\pi iz}.
    \]
    Also, all sums and products over a quotient group will be consider to be over a complete set of representatives.
    \subsection{Poincar\'e Series and Eisenstein Series}
      We will now study the Poincar\'e series and Eisenstein Series on \(\G_{0}(N)\backslash\H\). As \(\G\) is a Hecke congruence subgroup, \(\G_{0}(N)_{\infty} = B_{\G_{0}(N)}\) and we may take \(\s_{\infty} = I\). We will also take \(\nu = \chi\) to be a Dirichlet character modulo \(N\). Then for a cusp \(\mf{a}\) with scaling matrix \(\s_{\mf{a}}\), our series take the forms
      \[
        P_{m,\chi,\mf{a}}(z) = \sum_{\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)}\cchi(\g)\left(e(m\,\cdot\,)\bigg|_{k}\s_{\mf{a}}^{-1}\g\right)(z),
      \]
      and
      \[
        E_{\chi,\mf{a}}(z) = \sum_{\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)}\cchi(\g)\left(1\bigg|_{k}\s_{\mf{a}}^{-1}\g\right)(z).
      \]
      In either case, if \(\chi\) is trivial or \(\mf{a} = \infty\) then we will suppress these dependencies accordingly. Also, recall that \(\chi\) is always regular at \(\infty\).
      
      It turns out that we can explicitly compute the Fourier series expansions of the Poincar\'e series and Eisenstein series. Their Fourier coefficients involve Kloosterman sums, or more generally Sali\'e sums when \(\chi\) is not trivial, relative to cusps. This will essentially follow from a careful application of Poisson summation. The arguments involved are only slightly different. We first deduce the Fourier series expansion of the Poincar\'e series.

      \begin{proposition}\label{prop:Fourier_series_Poincare_modular}
        Let \(\mf{b}\) be a cusp of \(\G_{0}(N)\backslash\H\) with scaling matrix \(\s_{\mf{b}}\). The Fourier series expansion of \(P_{m,\chi,\mf{a}}(z)\) on \(\G_{0}(N)\backslash\H\) at the \(\mf{b}\) cusp is given by
        \begin{align*}
          (P_{m,\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) &= \d_{\mf{a},\mf{b}}e(mz) \\
          &+ \sum_{n \ge 1}\left(2\pi i^{-k}\left(\frac{\sqrt{n}}{\sqrt{m}}\right)^{k-1}\sum_{\substack{c \in \mc{C}_{\mf{a},\mf{b}}}}\frac{S_{\chi,\mf{a},\mf{b}}(m,n,c)}{c}J_{k-1}\left(\frac{4\pi\sqrt{mn}}{c}\right)\right)e(nz),
        \end{align*}
        provided the index \(m\) is positive.
      \end{proposition}
      \begin{proof}
        Write
        \[
          (P_{m,\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) = \sum_{\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)}\cchi(\g)j(\s_{\mf{a}}^{-1}\g\s_{\mf{b}},z)^{-k}e(m\s_{\mf{a}}^{-1}\g\s_{\mf{b}}z).
        \]
        From the Bruhat decomposition for \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\), any \(\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)\) is of the form \(\g = \begin{psmallmatrix} a & b \\ c & c\ell+d \end{psmallmatrix}\) where \(c \in \mc{C}_{\mf{a},\mf{b}}\), \(d \in \mc{D}_{\mf{a},\mf{b}}(c)\), and \(\ell \in \Z\). Furthermore, a short computation shows
        \[
          \frac{az+b}{cz+(c\ell+d)} = \frac{a}{c}-\frac{1}{c^{2}z+c^{2}\ell+cd}.
        \]
        Using these facts together with the periodicity of \(\chi\), we have
        \[
          (P_{m,\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) = \d_{\mf{a},\mf{b}}e(mz)+\sum_{\substack{\substack{c \in \mc{C}_{\mf{a},\mf{b}} \\ d \in \mc{D}_{\mf{a},\mf{b}}(c)} \\ \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}}}\cchi(d)\sum_{\ell \in \Z}\frac{e\left(m\left(\frac{a}{c}-\frac{1}{c^{2}z+c^{2}\ell+cd}\right)\right)}{(cz+c\ell+d)^{k}}.
        \]
        Now let
        \[
          I_{c,d}(z) = \sum_{\ell \in \Z}\frac{e\left(m\left(\frac{a}{c}-\frac{1}{c^{2}z+c^{2}\ell+cd}\right)\right)}{(cz+c\ell+d)^{k}}.
        \]
        We will apply the Poisson summation formula to \(I_{c,d}(z)\). By the identity theorem it suffices to verify the claim for \(z = iy\) with \(y\) positive. Accordingly, let \(f(x)\) be given by
        \[
          f(x) = \frac{e\left(m\left(\frac{a}{c}-\frac{1}{c^{2}(iy)+c^{2}x+cd}\right)\right)}{(c(iy)+cx+d)^{k}}.
        \]
        Then \(f(x)\) is Schwartz class. We will compute its Fourier transform
        \[
          (\mc{F}f)(n) = \int_{-\infty}^{\infty}\frac{e\left(m\left(\frac{a}{c}-\frac{1}{c^{2}(iy)+c^{2}x+cd}\right)\right)}{(c(iy)+cx+d)^{k}}e(-nx)\,dx.
        \]
        Complexify the integral to get
        \[
          \int_{\Im(w) = 0}\frac{e\left(m\left(\frac{a}{c}-\frac{1}{c^{2}(iy)+c^{2}w+cd}\right)\right)}{(c(iy)+cw+d)^{k}}e(-nw)\,dw,
        \]
        and make the change of variables \(w \mapsto w-\frac{d}{c}-(iy)\) to obtain
        \[
          e\left(\frac{ma+nd}{c}+n(iy)\right)\int_{\Im(w) = y}\frac{e\left(-\frac{m}{c^{2}w}\right)}{(cw)^{k}}e(-nw)\,dw.
        \]
        The integrand is meromorphic with a pole at \(w = 0\) and has polynomial decay of order \(k\) provided \(n\) is nonpositive. So for these \(n\), we conclude that the integral vanishes upon shifting the line of integration to \(\Im(w) = T\) for positive \(T\) and taking the limit as \(T \to \infty\). It remains to compute the integral for positive \(n\). To do this, make the change of variables \(w \mapsto -\frac{w}{2\pi in}\) to the last integral to rewrite it as
        \[
          \frac{(-1)^{k}(2\pi in)^{k-1}}{c^{k}}\int_{(2\pi ty)}\frac{e^{w-\frac{4\pi^{2}mn}{c^{2}w}}}{w^{k}}\,dw.
        \]
        Homotoping the line of integration to the Hankel contour about the negative real axis, we recognize the integral as the Schl\"aflin integral representation for the \(J\)-Bessel function since \(m\) is positive. This gives
        \[
          2\pi i^{-k}\left(\frac{\sqrt{n}}{\sqrt{m}}\right)^{k-1}\frac{1}{c}J_{k-1}\left(\frac{4\pi\sqrt{mn}}{c}\right).
        \]
        So in total we obtain
        \[
          (\mc{F}f)(n) = \begin{cases} \left(2\pi i^{-k}\left(\frac{\sqrt{n}}{\sqrt{m}}\right)^{k-1}\frac{e\left(\frac{ma+nd}{c}\right)}{c}J_{k-1}\left(\frac{4\pi\sqrt{mn}}{c}\right)\right)e\left(n(iy)\right) & \text{if \(n \ge 1\)}, \\ 0 & \text{if \(n \le 0\)}. \end{cases}
        \]
        Then by Poisson summation, we have
        \[
          I_{c,r}(z) = \sum_{n \ge 1}\left(2\pi i^{-k}\left(\frac{\sqrt{n}}{\sqrt{m}}\right)^{k-1}\frac{e\left(\frac{ma+nd}{c}\right)}{c}J_{k-1}\left(\frac{4\pi\sqrt{mn}}{c}\right)\right)e(nz).
        \]
        Plugging this back into the Poincar\'e series, interchanging the sums over \(n\) and \(c\) by absolute convergence, and collecting the exponential sum over \(a\) and \(d\), we at last obtain
        \begin{align*}
          (P_{m,\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) &= \d_{\mf{a},\mf{b}}e(mz) \\
          &+ \sum_{n \ge 1}\left(2\pi i^{-k}\left(\frac{\sqrt{n}}{\sqrt{m}}\right)^{k-1}\sum_{\substack{c \in \mc{C}_{\mf{a},\mf{b}}}}\frac{S_{\chi,\mf{a},\mf{b}}(m,n,c)}{c}J_{k-1}\left(\frac{4\pi\sqrt{mn}}{c}\right)\right)e(nz).
        \end{align*}
        which is our desired Fourier series expansion.
      \end{proof}
      
      An immediate consequence of this result is that the Poincar\'e series \(P_{m,\chi,\mf{a}}\) of positive index are cusp forms.
      
      The argument to obtain the Fourier series expansion of the Eisenstein series is much the same. The only slight difference is that we will pass by the pole of the integrand instead of deforming to the Hankel contour about the negative real axis.
      
      \begin{proposition}\label{prop:Fourier_series_Eisenstein_modular}
        Let \(\mf{b}\) be a cusp of \(\G_{0}(N)\backslash\H\) with scaling matrix \(\s_{\mf{b}}\). The Fourier series expansion of \(E_{\chi,\mf{a}}(z)\) on \(\G_{0}(N)\backslash\H\) at the \(\mf{b}\) cusp is given by
        \[
          (E_{\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) = \d_{\mf{a},\mf{b}}+\sum_{n \ge 1}\left(\frac{(-2\pi i)^{k}n^{k-1}}{\G(k)}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi}(0,n,c)}{c^{k}}\right)e(nz).
        \]
      \end{proposition}
      \begin{proof}
        Write
        \[
          (E_{\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) = \sum_{\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)}\cchi(\g)j(\s_{\mf{a}}^{-1}\g\s_{\mf{b}},z)^{-k}.
        \]
        From the Bruhat decomposition for \(\s_{\mf{a}}^{-1}\G\s_{\mf{b}}\), any \(\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)\) is of the form \(\g = \begin{psmallmatrix} a & b \\ c & c\ell+d \end{psmallmatrix}\) where \(c \in \mc{C}_{\mf{a},\mf{b}}\), \(d \in \mc{D}_{\mf{a},\mf{b}}(c)\), and \(\ell \in \Z\). Furthermore, a short computation shows
        \[
          \frac{az+b}{cz+(c\ell+d)} = \frac{a}{c}-\frac{1}{c^{2}z+c^{2}\ell+cd}.
        \]
        Using these facts together with the periodicity of \(\chi\), we have
        \[
          (E_{\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) = \d_{\mf{a},\mf{b}}+\sum_{\substack{\substack{c \in \mc{C}_{\mf{a},\mf{b}} \\ d \in \mc{D}_{\mf{a},\mf{b}}(c)} \\ \begin{psmallmatrix} a & \ast \\ c & d \end{psmallmatrix} \in \s_{\mf{a}}^{-1}\G\s_{\mf{b}}}}\cchi(d)\sum_{\ell \in \Z}\frac{1}{(cz+c\ell+d)^{k}}.
        \]
        Now let
        \[
          I_{c,d}(z) = \sum_{\ell \in \Z}\frac{1}{(cz+c\ell+d)^{k}}.
        \]
        We will apply the Poisson summation formula to \(I_{c,d}(z)\). By the identity theorem it suffices to verify the claim for \(z = iy\) with \(y\) positive. Accordingly, let \(f(x)\) be given by
        \[
          f(x) = \frac{1}{(c(iy)+cx+d)^{k}}.
        \]
        Then \(f(x)\) is Schwartz class. We will compute its Fourier transform
        \[
          (\mc{F}f)(n) = \int_{-\infty}^{\infty}\frac{1}{(c(iy)+cx+d)^{k}}e(-nx)\,dx.
        \]
        Complexify the integral to get
        \[
          \int_{\Im(w) = 0}\frac{1}{(c(iy)+cw+d)^{k}}e(-nw)\,dw,
        \]
        and make the change of variables \(w \mapsto w-\frac{d}{c}-(iy)\) to obtain
        \[
          e\left(\frac{nd}{c}+n(iy)\right)\int_{\Im(w) = y}\frac{1}{(cw)^{k}}e(-nw)\,dw.
        \]
        The integrand is meromorphic with a pole at \(w = 0\) and has polynomial decay of order \(k\) provided \(n\) is nonpositive. So for these \(n\), we conclude that the integral vanishes upon shifting the line of integration to \(\Im(w) = T\) for positive \(T\) and taking the limit as \(T \to \infty\). It remains to compute the integral for positive \(n\). To do this, make the change of variables \(w \mapsto -\frac{w}{2\pi in}\) to the last integral to rewrite it as
        \[
          \frac{(-1)^{k}(2\pi in)^{k-1}}{c^{k}}\int_{(2\pi ty)}\frac{e^{w}}{w^{k}}\,dw.
        \]
        The integrand of the remaining integral is meromorphic with a pole of order \(k\) at \(w = 0\). From the Laurent series expansion of \(\frac{e^{w}}{w^{k}}\) about \(w = 0\), the residue is easily seen to be \(\G(k)\). So upon shifting the line of integration to \((-\e)\), we pass by this pole and obtain
        \[
          \frac{(-2\pi i)^{k}n^{k-1}}{\G(k)c^{k}}+\frac{(-1)^{k}(2\pi in)^{k-1}}{c^{k}}\int_{(-\e)}\frac{e^{w}}{w^{k}}\,dw.
        \]
        This last integrand has polynomial decay of order \(k\). Whence we may again conclude that the integral vanishes upon shifting the line of integration to \(\Im(w) = -T\) for positive \(T\) and taking the limit as \(T \to \infty\). So in total we obtain
        \[
          (\mc{F}f)(n) = \begin{cases} \left(\frac{(-2\pi i)^{k}t^{k-1}}{\G(k)}\frac{e\left(\frac{nd}{c}\right)}{c^{k}}\right)e\left(n(iy)\right) & \text{if \(n \ge 1\)}, \\ 0 & \text{if \(n \le 0\)}. \end{cases}
        \]
        Then by Poisson summation, we have
        \[
          I_{c,r}(z) = \sum_{n \ge 1}\left(\frac{(-2\pi i)^{k}n^{k-1}}{\G(k)}\frac{e\left(\frac{nd}{c}\right)}{c^{k}}\right)e(nz).
        \]
        Plugging this back into the Poincar\'e series, interchanging the sums over \(n\) and \(c\) by absolute convergence, and collecting the exponential sum over \(d\), we at last obtain
        \[
          (E_{\chi,\mf{a}}|_{k}\s_{\mf{b}})(z) = \d_{\mf{a},\mf{b}}+\sum_{n \ge 1}\left(\frac{(-2\pi i)^{k}n^{k-1}}{\G(k)}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi}(0,n,c)}{c^{k}}\right)e(nz).
        \]
        which is our desired Fourier series expansion.
      \end{proof}

      An interesting consequence is that the constant term in the Fourier series expansion of \(E_{\chi,\mf{a}}\) at the \(\mf{b}\) cusp is zero unless \(\mf{a}\) is \(\G\)-equivalent to \(\mf{b}\). Therefore the Eisenstein series \(E_{\chi,\mf{a}}\) are actually never cusp forms. Accordingly, write \(\mc{E}_{k}(\G,\chi)\) for the subspace spanned by the Eisenstein series associated to a complete set of \(\G\)-inequivalent cusps. It turns out that \(\mc{M}_{k}(\G,\chi)\) decomposes as
      \[
        \mc{M}_{k}(\G,\chi) = \mc{S}_{k}(\G,\chi) \op \mc{E}_{k}(\G,\chi),
      \]
      where \(\mc{S}_{k}(\G,\chi)\) is spanned by the Poincar\'e series of positive index. Moreover, this decomposition is orthogonal in the sense that the Petersson inner product between elements of \(\mc{S}_{k}(\G,\chi)\) and \(\mc{E}_{k}(\G,\chi)\) is zero. To show all of this, let \(\mf{a}\) be a cusp of \(\G_{0}(N)\backslash\H\) and choose a scaling matrix \(\s_{\mf{a}}\). Suppose \(f \in \mc{S}_{k}(\G,\chi)\) and let its Fourier series expansion at the \(\mf{a}\) cusp be
      \[
        (f|_{k}\s_{\mf{a}})(z) = \sum_{n \ge 1}a_{\mf{a}}(n)e(nz).
      \]
      For any positive integer \(m\), define linear functionals \(\phi_{m,\chi,\mf{a}}:\mc{S}_{k}(\G,\chi) \to \C\) by 
      \[
        \phi_{m,\chi,\mf{a}}(f) = a_{\mf{a}}(m).
      \]
      Since \(\mc{S}_{k}(\G,\chi)\) is a finite dimensional complex Hilbert space, the Riesz representation theorem implies that there exists unique \(v_{m,\chi,\mf{a}} \in \mc{S}_{k}(\G,\chi)\) such that
      \[
        \<f,v_{m,\chi,\mf{a}}\> = a_{\mf{a}}(m).
      \]
      We would like to know what these cusp forms are. It turns out that \(v_{m,\chi,\mf{a}}(z)\) will be the Poincar\'e series \(P_{m,\chi,\mf{a}}(z)\) up to a constant.

      \begin{proposition}\label{prop:Petersson_inner_product_with_Poincare_series}
        Let \(f \in \mc{S}_{k}(\G,\chi)\) have Fourier coefficients \(a_{\mf{a}}(n)\) at the \(\mf{a}\) cusp of \(\G_{0}(N)\backslash\H\). Then 
        \[
          \<f,P_{m,\chi,\mf{a}}\> = \frac{\G(k-1)}{V_{\G}(4\pi m)^{k-1}}a_{\mf{a}}(m),
        \]
        for all positive integers \(m\).
      \end{proposition}
      \begin{proof}
        We will compute 
        \[
          \<f,P_{m,\chi,\mf{a}}\> = \frac{1}{V_{\G}}\int_{\G_{0}(N)\backslash\H}f(z)\conj{P_{m,\chi,\mf{a}}(z)}\Im(z)^{k}\,d\mu.
        \]
        A short computation using \cref{equ:Mobius_transformation_imaginary_part_simplified} along with modularity and the cocycle condition shows this integral may be expressed as
        \[
          \frac{1}{V_{\G}}\int_{\G_{0}(N)\backslash\H}\sum_{\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)}\conj{j(\s_{\mf{a}}^{-1},\g z)^{-k}}f(\g z)e\left(-m\conj{\s_{\mf{a}}^{-1}\g z}\right)\Im(\g z)^{k}\,d\mu.
        \]
        Now unfold to obtain
        \[
          \frac{1}{V_{\G}}\int_{\G_{\mf{a}}\backslash\H}\conj{j(\s_{\mf{a}}^{-1},z)^{-k}}f(z)e\left(-m\conj{\s_{\mf{a}}^{-1}z}\right)\Im(z)^{k}\,d\mu.
        \]
        Making the change of variables \(z \mapsto \s_{\mf{a}}z\), another short computation using the fact that \(\G_{\mf{a}} = \s_{\mf{a}}\G_{0}(N)_{\infty}\s_{\mf{a}}^{-1}\) together with \cref{equ:Mobius_transformation_imaginary_part_simplified} and the cocycle condition shows that this integral becomes
        \[
          \frac{1}{V_{\G}}\int_{\G_{0}(N)_{\infty}\backslash\H}(f|_{k}\s_{\mf{a}})(z)e(-m\conj{z})\Im(z)^{k}\,d\mu.
        \]
        Substituting in the Fourier series expansion of \(f\) at the \(\mf{a}\) cusp and interchanging the inner sum and integral by absolute convergence, a short computation gives
        \[
          \frac{1}{V_{\G}}\int_{0}^{\infty}a_{\mf{a}}(m)e^{-4\pi my}y^{k}\,\frac{dy}{y^{2}},
        \]
        in view of \cref{equ:Dirac_integral_representation}, because every term integrates to zero except the \(m\)-th term. Performing the change of variables \(y \mapsto \frac{y}{4\pi m}\), this latter integral is recognized as the gamma function and we obtain
        \[
          \frac{\G(k-1)}{V_{\G}(4\pi m)^{k-1}}a_{\mf{a}}(m),
        \]
        completing the proof.
      \end{proof}
 
      It follows immediately from this result that
      \[
        v_{m,\chi,\mf{a}}(z) = \frac{V_{\G}(4\pi m)^{k-1}}{\G(k-1)}P_{m,\chi,\mf{a}}(z).
      \]
      Thus the Poincar\'e series \(P_{m,\chi,\mf{a}}(z)\) of positive index extract the Fourier coefficients of \(f\) at the \(\mf{a}\) cusp up to constants.

      An analogous argument with Eisenstein series shows that they are orthogonal to cusp forms.
      
      \begin{proposition}\label{prop:Petersson_inner_product_with_Eisenstein_series}
        Let \(f \in \mc{S}_{k}(\G,\chi)\) have Fourier coefficients \(a_{\mf{a}}(n)\) at the \(\mf{a}\) cusp of \(\G_{0}(N)\backslash\H\). Then 
        \[
          \<f,E_{\chi,\mf{a}}\> = 0.
        \]
      \end{proposition}
      \begin{proof}
        We will compute 
        \[
          \<f,E_{\chi,\mf{a}}\> = \frac{1}{V_{\G}}\int_{\G_{0}(N)\backslash\H}f(z)\conj{E_{\chi,\mf{a}}(z)}\Im(z)^{k}\,d\mu.
        \]
        A short computation using \cref{equ:Mobius_transformation_imaginary_part_simplified} along with modularity and the cocycle condition shows this integral may be expressed as
        \[
          \frac{1}{V_{\G}}\int_{\G_{0}(N)\backslash\H}\sum_{\g \in \G_{0}(N)_{\mf{a}}\backslash\G_{0}(N)}\conj{j(\s_{\mf{a}}^{-1},\g z)^{-k}}f(\g z)\Im(\g z)^{k}\,d\mu.
        \]
        Now unfold to obtain
        \[
          \frac{1}{V_{\G}}\int_{\G_{\mf{a}}\backslash\H}\conj{j(\s_{\mf{a}}^{-1},z)^{-k}}f(z)\Im(z)^{k}\,d\mu.
        \]
        Making the change of variables \(z \mapsto \s_{\mf{a}}z\), another short computation using the fact that \(\G_{\mf{a}} = \s_{\mf{a}}\G_{0}(N)_{\infty}\s_{\mf{a}}^{-1}\) together with \cref{equ:Mobius_transformation_imaginary_part_simplified} and the cocycle condition shows that this integral becomes
        \[
          \frac{1}{V_{\G}}\int_{\G_{0}(N)_{\infty}\backslash\H}(f|_{k}\s_{\mf{a}})(z)\Im(z)^{k}\,d\mu.
        \]
        Substituting in the Fourier series expansion of \(f\) at the \(\mf{a}\) cusp and interchanging the inner sum and integral by absolute convergence, a short computation gives
        \[
          \frac{1}{V_{\G}}\int_{0}^{\infty}a_{\mf{a}}(0)y^{k}\,\frac{dy}{y^{2}},
        \]
        in view of \cref{equ:Dirac_integral_representation}, because every term integrates to zero except the constant term. This integral is zero because \(f\) is a cusp form which completes the proof. 
      \end{proof}

      With these results in hand we can prove that the Poincar\'e series of positive index span the space of cusp forms and our desired decomposition.

      \begin{theorem}
        The Poincar\'e series \(P_{m,\chi}(z)\) of positive index span \(\mc{S}_{k}(\G,\chi)\). Moreover, we have the direct sum decomposition
        \[
          \mc{M}_{k}(\G,\chi) = \mc{S}_{k}(\G,\chi) \op \mc{E}_{k}(\G,\chi),
        \]
        which is orthogonal in the sense that
        \[
          \<P_{m,\chi,\mf{b}},E_{\chi,\mf{a}}\> = 0.
        \]
      \end{theorem}
      \begin{proof}
        Let \(f \in \mc{S}_{k}(\G,\chi)\). \cref{prop:Petersson_inner_product_with_Poincare_series} shows that \(\<f,P_{m,\chi,\mf{a}}\> = 0\) if and only if the \(m\)-th Fourier coefficient of \(f\) is zero. So \(f\) is orthogonal to all of the Poincar\'e series \(P_{m,\chi}\) of positive index if and only if every Fourier coefficient is zero. But this happens if and only if \(f\) is identically zero. This proves the first statement.

        To prove the direct sum decomposition, we first show that \(\mc{E}_{k}(\G,\chi)\) is disjoint from \(\mc{S}_{k}(\G,\chi)\). Indeed, suppose there are constants \(a_{\mf{a}}\) such that
        \[
          \sum_{\mf{a} \in \G\backslash\what{\Q}}a_{\mf{a}}E_{\chi,\mf{a}}(z),
        \]
        is a cusp form. Recall from \cref{prop:Fourier_series_Eisenstein_modular} that the constant term in the Fourier series expansion of \(E_{\chi,\mf{a}}\) at the \(\mf{b}\) cusp is \(\d_{\mf{a},\mf{b}}\). Therefore \(a_{\mf{a}} = 0\) which proves that these spaces are disjoint. Moreover, this fact also implies that
        \[
          f(z)-\sum_{\mf{a} \in \G\backslash\what{\Q}}a_{\mf{a}}(n)E_{\chi,\mf{a}}(z),
        \]
        is a cusp form for any \(f \in \mc{M}_{k}(\G,\chi)\) with Fourier coefficients \(a_{\mf{a}}(n)\) at the \(\mf{a}\) cusp. The direct sum decomposition follows at once. Lastly, the orthogonality statement is immediate from \cref{prop:Petersson_inner_product_with_Eisenstein_series} since the Poincar\'e series are cusp forms.
      \end{proof}
    \subsection{\todo{Diamond and Hecke Operators}}
      The diamond and Hecke operators are sums of double coset operators. They will be used to construct a linear theory of modular forms on \(\G_{0}(N)\backslash\H\) via their Fourier coefficients. Actually, these operators will be defined for modular forms on \(\G_{1}(N)\backslash\H\) with trivial nebentypus. However, it turns out that such modular forms arise from those on \(\G_{0}(N)\backslash\H\) with character via the diamond operators. So we will discuss the diamond operators first and the Hecke operators second. 
      
      To define the diamond operators, we need to consider the congruence subgroups \(\G_{1}(N)\) and \(\G_{0}(N)\). Recall that \(\G_{1}(N) \subseteq \G_{0}(N)\) and consider the surjective homomorphism
      \[
        \G_{0}(N) \to (\Z/N\Z)^{\ast} \qquad \begin{pmatrix} a & b \\ c & d\end{pmatrix} \mapsto d \tmod{N}.
      \]
      Its kernel is exactly \(\G_{1}(N)\) so that \(\G_{1}(N)\) is a normal subgroup of \(\G_{0}(N)\) whence
      \[
        \G_{0}(N)/\G_{1}(N) \cong (\Z/N\Z)^{\ast},
      \]
      by the first isomorphism theorem. Now let \(d\) be a positive integer. Then the \textbf{diamond operator}\index{diamond operator} \(\<d\>:\mc{M}_{k}(\G_{1}(N)) \to \mc{M}_{k}(\G_{1}(N))\) is defined to be the double coset operator given by
      \[
        (\<d\>f)(z) = \begin{cases} \left(f[\G_{1}(N)\a\G_{1}(N)]_{k}\right)(z) & \text{if \((d,N) = 1\)}, \\ 0 & \text{if \((d,N) > 1\)}, \end{cases}
      \]
      where in the first case we choose any \(\a \in \G_{0}(N)\) with \(\a \equiv \begin{psmallmatrix} \ast & \ast \\ 0 & d \end{psmallmatrix} \tmod{N}\). To prove the diamond operator \(
      <d\>\) is well-defined, we must show that it only depends upon \(d\) when the operator is not zero. So suppose \(\a' \in \G_{0}(N)\) with \(\a' \equiv \begin{psmallmatrix} \ast & \ast \\ 0 & d \end{psmallmatrix} \tmod{N}\). Then a short computation shows
      \[
        \a'\a^{-1} \equiv \begin{pmatrix} 1 & \ast \\ 0 & 1 \end{pmatrix} \pmod{N}.
      \]
      So \(\a' = \g\a\) for some \(\g \in \G_{1}(N)\) and therefore \([\G_{1}(N)\a'\G_{1}(N)]_{k} = [\G_{1}(N)\a\G_{1}(N)]_{k}\) proving that the diamond operator \(\<d\>\) is well-defined. Moreover, there is only orbit representative in double coset when \((d,N) = 1\). Indeed, normality of \(\G_{1}(N)\) in \(\G_{0}(N)\) implies \(\G_{1}(N)\a\G_{1}(N) = \G_{1}(N)\a\) and so
      \[
        (\<d\>f)(z) = (f\|_{k}\a)(z).
      \]
      Also, we find from the observation
      \[
        \begin{pmatrix} \ast & \ast \\ 0 & a \end{pmatrix}\begin{pmatrix} \ast & \ast \\ 0 & d \end{pmatrix} = \begin{pmatrix} \ast & \ast \\ 0 & ad \end{pmatrix},
      \]
      that the diamond operators are multiplicative and invertible with \(\<a\>\) being the inverse of \(\<d\>\) if \(a\) is the inverse of \(d\) modulo \(N\). Therefore the diamond operators induce an action of \(\G_{0}(N)\) on \(\mc{M}_{k}(\G_{1}(N))\), and since \(\G_{1}(N)\) acts trivially and is normal in \(\G_{0}(N)\), there is a further induced action of \((\Z/N\Z)^{\ast}\) in view of the previous isomorphism.
      
      One reason the diamond operators are useful is that they decompose \(\mc{M}_{k}(\G_{1}(N))\) into eigenspaces. For any Dirichlet character \(\chi\) modulo \(N\), we let
      \[
        \mc{M}_{k}(N,\chi) = \{f \in \mc{M}_{k}(\G_{1}(N)):\<d\>f = \chi(d)f\},
      \]
      be the \(\chi\)-eigenspace. Also let \(\mc{S}_{k}(N,\chi)\) be the corresponding subspace of cusp forms. Then \(\mc{M}_{k}(\G_{1}(N))\) admits a decomposition into these eigenspaces.

      \begin{proposition}\label{thm:diamond_operator_decomposition_modular}
        \(\mc{M}_{k}(\G_{1}(N))\) admits the direct sum decomposition
        \[
          \mc{M}_{k}(\G_{1}(N)) = \bigop_{\chi \tmod{N}}\mc{M}_{k}(N,\chi).
        \]
        Moreover, this decomposition respects the subspace of cusp forms.
      \end{proposition}
      \begin{proof}
        The diamond operators induce a representation \(\Phi\) of \((\Z/N\Z)^{\ast}\) over \(\mc{M}_{k}(\G_{1}(N))\). Explicitly, this representation is
        \[
          \Phi:(\Z/N\Z)^{\ast} \x \mc{M}_{k}(\G_{1}(N)) \to \mc{M}_{k}(\G_{1}(N)) \qquad (d,f) \mapsto \<d\>f.
        \]
        Since \((\Z/N\Z)^{\ast}\) is a finite abelian group, every complex representation is completely reducible and every irreducible representation is one-dimensional. As the characters of \((\Z/N\Z)^{\ast}\) are the Dirichlet characters modulo \(N\), the decomposition as a direct sum follows. Moreover, it preserves the subspace of cusp forms since \(\Phi\) restricts to a representation of \((\Z/N\Z)^{\ast}\) over \(\mc{S}_{k}(\G_{1}(N))\).
      \end{proof}
      
      Observe that every matrix in \(\g \in \G_{0}(N)\) is of the form \(\g \equiv \begin{psmallmatrix} \ast & \ast \\ 0 & d \end{psmallmatrix} \tmod{N}\) for some integer \(d\) with \((d,N) = 1\). So this result shows that the diamond operators sieve modular forms on \(\G_{1}(N)\backslash\H\) with trivial character in terms of modular forms on \(\G_{0}(N)\backslash\H\) with nontrivial characters. In particular, we have
      \[
        \mc{M}_{k}(N,\chi) = \mc{M}_{k}(\G_{0}(N),\chi) \quad \text{and} \quad \mc{S}_{k}(N,\chi) = \mc{S}_{k}(\G_{0}(N),\chi).
      \]
      We are now ready to discuss the Hecke operators. First, for any positive integer \(m\), set
      \[
        \D_{m} = \left\{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \Mat_{2}^{m}(\Z): \begin{pmatrix} a & b \\ c & d \end{pmatrix} \equiv \begin{pmatrix} 1 & \ast \\ 0 & \ast \end{pmatrix} \tmod{N} \right\}.
      \]
      In other words, \(\D_{m}\) is subset of \(\GL_{2}^{+}(\Q)\) consisting of determinant \(m\) matrices \(\a\) with integer coefficients such that \(\a \equiv \begin{psmallmatrix} 1 & \ast \\ 0 & \ast \end{psmallmatrix} \tmod{N}\). From the equivalence
      \[
        \begin{pmatrix} 1 & \ast \\ 0 & 1 \end{pmatrix}\begin{pmatrix} 1 & \ast \\ 0 & \ast \end{pmatrix}\begin{pmatrix} 1 & \ast \\ 0 & 1 \end{pmatrix} \equiv \begin{pmatrix} 1 & \ast \\ 0 & \ast \end{pmatrix} \pmod{N},
      \]
      it follows that \(\G_{1}(N)\) acts on \(\D_{m}\) by both left and right multiplication. Whence \(\D_{m}\) decomposes into a disjoint union of orbits
      \[
        \D_{m} = \bigcup_{\a \in \G_{1}(N)\backslash\D_{m}/\G_{1}(N)}\G_{1}(N)\a\G_{1}(N),
      \]
      who themselves are double cosets. To see that this decomposition is finite, write \(\a\) in smith normal form as \(\a = U\begin{psmallmatrix} a & 0 \\ 0 & d \end{psmallmatrix}V\) for some \(U,V \in \SL_{2}(\Z)\) and positive integers \(a\) and \(d\) with \(ad = m\) and \(a \mid d\). As \(\G_{1}(N)\) has finite index in \(\SL_{2}(Z)\) and there are finitely many choices for \(a\) and \(d\) we conclude that this disjoint union is finite. We define the \(m\)-th \textbf{Hecke operator}\index{Hecke operator} \(T_{m}:\mc{M}_{k}(\G_{1}(N)) \to \mc{M}_{k}(\G_{1}(N))\) to be the linear operator given by 
      \[
        (T_{m}f)(z) = \sum_{\a \in \G_{1}(N)\backslash\D_{m}/\G_{1}(N)}\left[\G_{1}(N)\a\G_{1}(N)\right]_{k}f(z).
      \]
      The Hecke operator \(T_{m}\) is well-defined because it only depends the double coset decomposition of \(\D_{m}\). In order to compute the Hecke operators explicitly, we need to find a complete set of representatives for \(\G_{1}(N)\backslash(\G_{1}(N)\a\G_{1}(N))\) and all \(\a\). But this is the same as finding one for \(\G_{1}(N)\backslash(\G_{1}(N)\D_{m}\G_{1}(N))\) which is much easier to accomplish.

      \begin{lemma}\label{lem:cosets_for_Hecke_operators}
        We have a disjoint union
        \[
          \Gamma_{1}(N)\D_{m}\Gamma_{1}(N) = \bigcup_{\substack{ad = m \\ (a,N) = 1}}\bigcup_{b \tmod{d}} \Gamma_{1}(N)\g_{a}\begin{pmatrix} a & b \\ 0 & d \end{pmatrix},
        \]
        where \(\g_{a} \in \G_{0}(N)\) is some matrix satisfying \(\g_{a} \equiv \begin{psmallmatrix} a^{-1} & 0 \\ 0 & a \end{psmallmatrix} \tmod{N}\).
      \end{lemma}
      \begin{proof}
        The reverse containment holds in view of 
        \[
           \begin{pmatrix} 1 & \ast \\ 0 & 1 \end{pmatrix}\g_{a}\begin{pmatrix} a & b \\ 0 & d \end{pmatrix} \equiv \begin{pmatrix} 1 & \ast \\ 0 & \ast \end{pmatrix} \pmod{N}.
        \]
        For the forward containment, suppose \(\a = \begin{psmallmatrix} a' & b' \\ c' & d' \end{psmallmatrix} \in \Gamma_{1}(N)\D_{m}\Gamma_{1}(N)\). As \(a'\) and \(c'\) are both non zero, we can find relatively prime integers \(u\) and \(v\) such that \(ua'+vc' = 0\). B\'ezout's identity then provides the existence of integers \(s\) and \(s\) with \(sv-ut = 1\). Now set \(\g = \begin{psmallmatrix} s & t \\ u & v \end{psmallmatrix} \in \SL_{2}(\Z)\). It follow that
        \[
          \g\a = \begin{pmatrix} \ast & \ast \\ 0 & \ast \end{pmatrix},
        \]
        Replaying \(\g\) by \(\pm \g\begin{psmallmatrix} 1 & \ell \\ 0 & 1 \end{psmallmatrix}\) for some integer \(\ell\), if necessary, we may assume that
        \[
          \g\a = \begin{pmatrix} a & b \\ 0 & d \end{pmatrix},
        \]
        for positive integers \(a\), \(b\), and \(d\) with \(ad = m\) and \(b\) modulo \(d\). As \(\a \in \D_{m}\), it also follows that
        \[
          \g \begin{pmatrix} 1 & \ast \\ 0 & m \end{pmatrix} \equiv \begin{pmatrix} a & b \\ 0 & d \end{pmatrix} \pmod{N}.
        \]
        Then \((a,N) = 1\) as \(\g\) must satisfy \(\g \equiv \begin{psmallmatrix} a & \ast \\ 0 & a^{-1} \end{psmallmatrix} \tmod{N}\) and so \(\g^{-1} \equiv \begin{psmallmatrix} a^{-1} & \ast \\ 0 & a \end{psmallmatrix} \tmod{N}\). In particular, \(\g \in \G_{0}(N)\). In view of the fact
        \[
          \begin{pmatrix} 1 & \ast \\ 0 & 1 \end{pmatrix}\begin{pmatrix} a^{-1} & 0 \\ 0 & a \end{pmatrix} \equiv \begin{pmatrix} a^{-1} & \ast \\ 0 & a \end{pmatrix} \pmod{N},
        \]
        we may write \(\g^{-1} = \eta\g_{a}\) for some \(\eta \in \G_{1}(N)\). But then
        \[
          \a = \eta\g_{a}\begin{pmatrix} a & b \\ 0 & d \end{pmatrix},
        \]
        and the reverse inclusion follows. It remains to show that the union is disjoint. If not, then there exist matrices \(\eta_{1},\eta_{2} \in \G_{1}(N)\) satisfying
        \[
          \eta_{1}\g_{a_{1}}\begin{pmatrix} a_{1} & b_{1} \\ 0 & d_{1} \end{pmatrix} = \eta_{2}\g_{a_{2}}\begin{pmatrix} a_{2} & b_{2} \\ 0 & d_{2} \end{pmatrix},
        \]
        for distinct matrices \(\begin{psmallmatrix} a_{i} & b_{i} \\ 0 & d_{i} \end{psmallmatrix}\) satisfying \(a_{i}d_{i} = m\), \((a_{i},N) = 1\), and \(b_{i}\) modulo \(d_{i}\) . Then
        \[
          \begin{pmatrix} a_{1} & b_{1} \\ 0 & d_{1} \end{pmatrix}\begin{pmatrix} \frac{d_{2}}{m} & -\frac{b_{2}}{m} \\ 0 & \frac{a_{2}}{m} \end{pmatrix} = \begin{pmatrix} \frac{a_{1}}{a_{2}} & \ast \\ 0 & \frac{d_{1}}{d_{2}} \end{pmatrix},
        \]
        belongs to \(\SL_{2}(\Z)\) which forces \(a_{1} = a_{2}\) and \(d_{1} = d_{2}\). Whence
        \[
          \begin{pmatrix} a_{1} & b_{1} \\ 0 & d_{1} \end{pmatrix} = \begin{pmatrix} 1 & \ell \\ 0 & 1 \end{pmatrix}\begin{pmatrix} a_{2} & b_{2} \\ 0 & d_{2} \end{pmatrix},
        \]
        for some integer \(\ell\). But as \(b_{1}\) and \(b_{2}\) are both modulo \(d_{1} = d_{2}\), we must have \(\ell = 0\). Hence \(b_{1} = b_{2}\). But then the matrices \(\begin{psmallmatrix} a_{i} & b_{i} \\ 0 & d_{i} \end{psmallmatrix}\) are not distinct which is a contradiction. Therefore the union is disjoint completing the proof.
      \end{proof}

      With this lemma, we immediately find that the Hecke operators may be expressed in the form
      \begin{equation}\label{equ:Hecke_operator_explicit_formula}
        (T_{m}f)(z) = m^{k-1}\sum_{ad = m}\frac{1}{d^{k}}\sum_{b \tmod{d}}\<a\>f\left(\frac{az+b}{d}\right),
      \end{equation}
      where we are permitted to remove the condition \((a,N) = 1\) since the diamond operator \(\<a\>\) acts as the zero operator whenever \((a,N) > 1\). Moreover, we can use this formula to deduce how the Hecke operators act on the Fourier series expansion of modular forms.

      \begin{proposition}\label{prop:Hecke_operators_on_Fourier_coefficients}
        Let \(f \in \mc{M}_{k}(N,\chi)\) have Fourier series expansion
        \[
          f(z) = \sum_{n \ge 0}a(n)e(nz).
        \]
        Then for any positive integer \(m\), the Fourier series expansion of \(T_{m}f\) is
        \[
          (T_{m}f)(z) = \sum_{n \ge 0}\left(\sum_{d \mid (n,m)}\chi(d)d^{k-1}a\left(\frac{nm}{d^{2}}\right)\right)e(nz).
        \]
      \end{proposition}
      \begin{proof}
        By \cref{equ:Hecke_operator_explicit_formula}, write
        \[
          (T_{m}f)(z) = m^{k-1}\sum_{ad = m }\frac{\chi(a)}{d^{k}}\sum_{b \tmod{d}}\sum_{n \ge 0}a(n)e\left(\frac{anz+bn}{d}\right).
        \]
        For fixed \(d\), the sum over \(b\) is
        \[
          \sum_{b \tmod{d}}e\left(\frac{bn}{d}\right) = \begin{cases} d & \text{if \(d \mid n\)}, \\ 0 & \text{if \(d \nmid n\)}, \end{cases}
        \]
        because in the first case every term is \(1\) and in the second it is a geometric sum with common ratio \(e\left(\frac{n}{d}\right)\).
        Whence our expression becomes
        \[
          \sum_{ad = m}a^{k-1}\chi(a)\sum_{\substack{n \ge 0 \\ d \mid n}}a(n)e\left(\frac{anz}{d}\right),
        \]
        since \(ad = m\). The change of variables \(n \mapsto \frac{nd}{a}\) yields
        \[
         \sum_{ad = m}\sum_{\substack{n \ge 0 \\ a \mid n}}a^{k-1}\chi(a)a\left(\frac{nd}{a}\right)e(nz).
        \]
        Now write \(d = \frac{m}{a}\) to obtain
        \[
        \sum_{n \ge 0}\left(\sum_{a \mid (n,m)}\chi(a)a^{k-1}a\left(\frac{nm}{a^{2}}\right)\right)e(nz).
        \]
        This is equivalent to the claim upon making the change of variables \(a \mapsto d\).
      \end{proof}

      Now that we know how the Hecke operators act on the Fourier coefficients of modular forms, we can prove composition relations about them. However, we will require a rather tedious lemma about divisor pairs.

      \begin{lemma}\label{lem:Hecke_composition_lemma}
        Fix positive integers \(m\) and \(n\) and a nonnegative \(r\). For any positive integer \(d\), set
        \[
          M(d) = \left\{d = d_{1}d_{2}:d_{1} \mid (r,m) \text{ and } d_{2} \mid \left(\frac{rm}{d_{1}^{2}},n\right)\right\}.
        \]
        Then
        \[
          M(d) = \left\{d = d_{3}d_{4}:d_{3} \mid (m,n) \text{ and } d_{4} \mid \left(r,\frac{mn}{d_{3}^{2}}\right)\right\}.
        \]
      \end{lemma}
      \begin{proof}
        As the greatest common divisor is multiplicative in every entry, it suffice to prove the claim when \(m = p^{\a}\), \(n = p^{\b}\), \(r = p^{\g}\), and \(d = d^{\d}\) are all powers of a prime \(p\). Then \(d_{1} = p^{i_{1}}\) and \(d_{2} = p^{i_{2}}\) with
        \[
          0 \le i_{1} \le \min(\a,\g) \quad \text{and} \quad 0 \le i_{2} \le \min(\a+\g-2i_{1},\b),
        \]
        while \(d_{3} = p^{i_{3}}\) and \(d_{4} = p^{i_{4}}\) with
        \[
          0 \le i_{2} \le \min(\a+\g-2i_{1},\b) \quad \text{and} \quad 0 \le i_{4} \le \min(\a+\b-2i_{3},\g).
        \]
        Moreover, \(i_{2} = \d-i_{i}\) and \(i_{4} = \d-i_{3}\). Substituting in this relations, our conditions become
        \[
          \max(0,\d-\b) \le i_{1} \le \min(\a,\g,\d,\a+\g-\d),
        \]
        and
        \[
          \max(0,\d-\g) \le i_{3} \le \min(\a,\b,\d,\a+\b-\d).
        \]
        So our claim about \(M(d)\) is proved if these intervals are of the same length. First suppose \(\d \le \a\). Then the upper bounds are \(\min(\g,\d)\) and \(\min(\b,\d)\) respectively. Therefore these intervals are of length
        \[
          \min(\g,\d)-\max(0,\d-\b)+1 \quad \text{and} \quad \min(\b,\d)-\max(0,\d-\g)+1,
        \]
        upon which a short computation shows are equal in every case. Now suppose \(\d > \a\). Then another short computation shows
        \[
          \min(\a,\g,\d,\a+\g-\d) = \a-\max(0,\d-\g) \quad \text{and} \quad \min(\a,\b,\d,\a+\b-\d) = \a-\max(0,\d-\b).
        \]
        Whence these intervals are of length
        \[
          \a-\max(0,\d-\g)-\max(0,\d-\b)+1 \quad \text{and} \quad \a-\max(0,\d-\b)-\max(0,\d-\g)+1,
        \]
        which are identical. Therefore the claim is proved.
      \end{proof}

      With this lemma in hand, we can now prove the composition formula for the Hecke operators.

      \begin{theorem}
        The Hecke operators \(T_{m}\) and \(T_{n}\) on \(\mc{M}_{k}(N,\chi)\), for any positive integers \(m\) and \(n\), satisfy
        \[
          T_{m}T_{n} = \sum_{d \mid (m,n)}\chi(d)d^{k-1}T_{\frac{mn}{d^{2}}}.
        \]
        In particular, for \((m,n) = 1\) and all primes \(p\) and positive integers \(r\) we have the relations
        \[
          T_{m}T_{n} = T_{mn} \quad \text{and} \quad T_{p}T_{p^{r}} = T_{p^{r+1}}+\chi(p)p^{k-1}T_{p^{r-1}}.
        \]
      \end{theorem}
      \begin{proof}
        To prove the first statement, it suffices to show that left-hand and right-hand sides act the same on the Fourier coefficients of any \(f \in \mc{M}_{k}(N,\chi)\). So let
        \[
          f(z) = \sum_{r \ge 0}a(r)e(r z),
        \]
        be the Fourier series expansion of \(f\). From two applications of \cref{prop:Hecke_operators_on_Fourier_coefficients}, we find that
        \[
          (T_{m}T_{n}f)(z) = \sum_{r \ge 0}\left(\sum_{d = d_{1}d_{2}}\sum_{\substack{d_{1} \mid (r,m) \\ d_{2} \mid \left(\frac{rm}{d_{1}^{2}},n\right)}}\chi(d)(d)^{k-1}a\left(\frac{rmn}{d^{2}}\right)\right)e(rz).
        \]
        By \cref{lem:Hecke_composition_lemma}, we may further write
        \[
          (T_{m}T_{n}f)(z) = \sum_{r \ge 0}\left(\sum_{d = d_{3}d_{4}}\sum_{\substack{d_{3} \mid (m,n) \\ d_{4} \mid \left(r,\frac{mn}{d_{3}^{2}}\right)}}\chi(d)(d)^{k-1}a\left(\frac{rmn}{d^{2}}\right)\right)e(rz).
        \]
        Another application of \cref{prop:Hecke_operators_on_Fourier_coefficients} shows that for fixed \(d_{3}\) the sum over \(d_{4}\) is exactly the \(r\)-th Fourier coefficient of \(T_{\frac{mn}{d_{3}^{2}}}f\). Whence
        \[
          (T_{m}T_{n}f)(z) = \sum_{d_{3} \mid (m,n)}\chi(d_{3})d_{3}^{k-1}\left(T_{\frac{mn}{d_{3}^{2}}}f\right)(z).
        \]
        The proof of the first statement is complete upon making the change of variables \(d_{3} \mapsto d\). The latter statement is immediate from the first as \(d = 1\) when \((m,n) = 1\) and \(d = 1,p\) when \(m = p\) and \(n = p^{r}\).
      \end{proof}

      \iffalse
      With \cref{lem:cosets_for_Hecke_operators}, it is not too hard to see that the diamond and Hecke operators commute:

      \begin{proposition}\label{prop:diamond_Hecke_operators_commute_modular}
        For every \(d \in (\Z/N\Z)^{\ast}\) and prime \(p\), the diamond operators \(\<d\>\) and Hecke operators \(T_{p}\) on \(\mc{S}_{k}(\G_{1}(N))\) commute:
        \[
          \<d\>T_{p} = T_{p}\<d\>
        \]
      \end{proposition}
      \begin{proof}
        Let \(\a = \begin{psmallmatrix} 1 & 0 \\ 0 & p \end{psmallmatrix}\). For \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}(N)\), we have
        \[
          \g\a\g^{-1} \equiv \begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix}\begin{pmatrix} d & -b \\ -c & a \end{pmatrix} = \begin{pmatrix} 1 & (p-1)ab \\ 0 & p \end{pmatrix} \tmod{N},
        \]
        because \(c \equiv 0 \tmod{N}\), \(ad-bc = 1\), and \(ad \equiv {1} \tmod{N}\). By \cref{lem:cosets_for_Hecke_operators}, \(\g\a\g^{-1} \in \G_{1}(N)\a\G_{1}(N)\) and so we can use this representative in place of \(\a\). On the one hand,
        \[
          \G_{1}(N)\a\G_{1}(N) = \bigcup_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}\G_{1}(N)\b.
        \]
        On the other hand, using \(\g\a\g^{-1}\) in place of \(\a\) and the normality of \(\G_{1}(N)\) in \(\G_{0}(N)\), we have
        \begin{align*}
          \G_{1}(N)\a\G_{1}(N) &= \G_{1}(N)\g\a\g^{-1}\G_{1}(N) \\
          &= \g\G_{1}(N)\a\G_{1}(N)\g^{-1} \\
          &= \g\bigcup_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}\G_{1}(N)\b\g^{-1} \\
          &= \bigcup_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}\G_{1}(N)\g\b\g^{-1}.
        \end{align*}
        Upon comparing these two decompositions of \(\G_{1}(N)\a\G_{1}(N)\) gives
        \[
          \bigcup_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}\G_{1}(N)\b = \bigcup_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}\G_{1}(N)\g\b\g^{-1}.
        \]
        Now let \(f \in \mc{S}_{k}(\G_{1}(N))\). Then this equivalence of unions implies
        \[
        \<d\>T_{p}f = \sum_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}f\|_{k}\b\g = \sum_{\b \in \G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)}f\|_{k}\g\b = T_{p}\<d\>f.
        \]
      \end{proof}
      
      Using \cref{lem:cosets_for_Hecke_operators} we can obtain an explicit description of the Hecke operator \(T_{p}\):

      \begin{proposition}\label{prop:explicit_description_of_Hecke_operators_modular}
        Let \(f \in \mc{S}_{k}(\G_{1}(N))\). Then the Hecke operator \(T_{p}\) acts on \(f\) as follows:
        \[
          (T_{p}f)(z) = \begin{cases} \displaystyle{\sum_{j \tmod{p}}}\left(f\bigg\|_{k}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right)(z)+\left(f\bigg\|_{k}\begin{pmatrix} m & n \\ N & p \end{pmatrix}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix}\right)(z) & \text{if \(p \nmid N\)}, \\ \displaystyle{\sum_{j \tmod{p}}}\left(f\bigg\|_{k}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right)(z) & \text{if \(p \mid N\)}, \end{cases}
        \]
        where \(m\) and \(n\) are chosen such that \(\det\left(\begin{psmallmatrix} m & n \\ N & p \end{psmallmatrix}\right) = 1\).
      \end{proposition}
      \begin{proof}
        Let \(\a = \begin{psmallmatrix} 1 & 0 \\ 0 & p \end{psmallmatrix}\) and define
        \[
          \b_{j} = \begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix} \quad \text{and} \quad \b_{\infty} = \begin{pmatrix} m & n \\ N & p \end{pmatrix}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} pm & n \\ Np & p \end{pmatrix},
        \]
        for \(j\) modulo \(p\) and where \(m\) and \(n\) are chosen such that \(\det\left(\begin{psmallmatrix} m & n \\ N & p \end{psmallmatrix}\right) = 1\). It will suffice to show that \(\b_{1},\ldots,\b_{p-1}\) and \(\b_{1},\ldots,\b_{p-1},\b_{\infty}\) run over complete sets of representatives for \(\G_{1}(N)\backslash\G_{1}(N)\a\G_{1}(N)\) depending on if \(p \mid N\) or not. To accomplish this, we will find a complete set of representatives for \((\a^{-1}\G_{1}(N)\a \cap \G_{1}(N))\backslash\G_{1}(N)\) and then use \cref{lem:coset_lemma_2}. First we require an explicit description of \(\a^{-1}\G_{1}(N)\a \cap \G_{1}(N)\). Let
        \[
          \G^{0}(p) = \left\{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_{2}(\Z):\begin{pmatrix} a & b \\ c & d \end{pmatrix} \equiv \begin{pmatrix} \ast & 0 \\ \ast & \ast \end{pmatrix} \tmod{p}\right\},
        \]
        and define
        \[
          \G_{1}^{0}(N,p) = \G_{1}(N) \cap \G^{0}(p).
        \]
        We claim \(\a^{-1}\G_{1}(N)\a \cap \G_{1}(N) = \G_{1}^{0}(N,p)\). First, let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{1}(N)\) and observe that
        \[
          \a^{-1}\g\a = \begin{pmatrix} 1 & 0 \\ 0 & p^{-1} \end{pmatrix}\begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix} = \begin{pmatrix} a & pd \\ p^{-1}c & d \end{pmatrix}.
        \]
        So for the forward containment, if \(\a^{-1}\g\a \in \a^{-1}\G_{1}(N)\a \cap \G_{1}(N)\) then \(\a^{-1}\g\a \in \G_{1}(N)\) and thus \(p \mid c\) so that \(\a^{-1}\g\a \in \SL_{2}(\Z)\). Moreover, the previous computation implies \(\a^{-1}\g\a \in \G_{1}^{0}(N,p)\) and so \(\a^{-1}\G_{1}(N)\a \cap \G_{1}(N) \subseteq \G_{1}^{0}(N,p)\) proving the forward containment. For the reverse containment, suppose \(\eta = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}^{1}(N,p)\). Then \(b = pk\) for some \(k \in \Z\). Now observe
        \[
          \eta = \begin{pmatrix} a & b \\ c & d \end{pmatrix} = \begin{pmatrix} 1 & 0 \\ 0 & p^{-1} \end{pmatrix}\begin{pmatrix} a & k \\ pc & d \end{pmatrix}\begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix} = \a^{-1}\g\a,
        \]
        where \(\g = \begin{psmallmatrix} a & k \\ pc & d \end{psmallmatrix}\). As \(\eta \in \G_{1}(N)\) we conclude \(\g \in \G_{1}(N)\) as well. Therefore \(\G_{0}^{1}(N,p) \subseteq \a^{-1}\G_{1}(N)\a \cap \G_{1}(N)\) proving the reverse containment. Now let
        \[
          \b'_{j} = \begin{pmatrix} 1 & j \\ 0 & 1 \end{pmatrix} \quad \text{and} \quad \b'_{\infty} = \begin{pmatrix} pm & n \\ N & 1 \end{pmatrix},
        \]
        for \(j\) taken modulo \(p\) and where \(m\) and \(n\) are as before. Clearly \(\b'_{j} \in \G_{1}(N)\) for all \(j\). As \(pm-Nn = 1\), we have \(pm \equiv 1 \tmod{N}\) so that \(\b'_{\infty} \in \G_{1}(N)\) as well. We claim that \(\b'_{1},\ldots,\b'_{p-1}\) and \(\b'_{1},\ldots,\b'_{p-1},\b'_{\infty}\) run over complete sets of representatives for \((\a^{-1}\G_{1}(N)\a \cap \G_{1}(N))\backslash\G_{1}(N)\) depending on if \(p \mid N\) or not. Again let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{1}(N)\) and consider
        \[
          \g{\b'_{j}}^{-1} = \begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} 1 & -j \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} a & b-aj \\ c & d-cj \end{pmatrix}.
        \]
        As \(\g{\b'_{j}}^{-1} \in \G_{1}(N)\) because both \(\g\) and \(\b'_{j}\) are, \(\g{\b'_{j}}^{-1} \in \a^{-1}\G_{1}(N)\a \cap \G_{1}(N) = \G_{1}^{0}(N,p)\) for some \(j\) if and only if
        \[
          b \equiv aj \tmod{p}.
        \]
        First suppose \(p \nmid a\). Then \(a\) is invertible modulo \(p\) so we may take \(j = a^{-1}b \tmod{p}\). Now suppose \(p \mid a\). If there is some \(j\) satisfying \(b \equiv aj \tmod{p}\) then we also have \(p \mid b\). But as \(ad-bc = 1\), this is impossible and so no such \(j\) exists. As \(a \equiv 1 \tmod{N}\), we have \(p \mid a\) if and only if \(p \nmid N\). In this case consider instead
        \[
          \g{\b'_{\infty}}^{-1} = \begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} 1 & -n \\ -N & pm \end{pmatrix} = \begin{pmatrix} a-Nb & pmb-na \\ c-Nd & pmd-nc \end{pmatrix}.
        \]
        Since \(p \mid a\), we have \(pmb-na \equiv 0 \tmod{p}\) so that \(\g{\b'_{\infty}}^{-1} \in \a^{-1}\G_{1}(N)\a \cap \G_{1}(N) = \G_{1}^{0}(N,p)\). Altogether, we have shown that \(\b'_{1},\ldots,\b'_{p-1}\) and \(\b'_{1},\ldots,\b'_{p-1},\b'_{\infty}\) run over representatives for \((\a^{-1}\G_{1}(N)\a \cap \G_{1}(N))\backslash\G_{1}(N)\) depending on if \(p \mid N\) or not. To show they run over complete sets of representatives, we need to show that no two representatives belong to the same coset. To this end, suppose \(i\) and \(j\) are distinct and consider
        \[
          \b'_{i}{\b'_{j}}^{-1} = \begin{pmatrix} 1 & i \\ 0 & 1 \end{pmatrix}\begin{pmatrix} 1 & j \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} 1 & i-j \\ 0 & 1 \end{pmatrix}.
        \]
        Then \(\b'_{i}{\b'_{j}}^{-1} \in \a^{-1}\G_{1}(N)\a \cap \G_{1}(N) = \G_{1}^{0}(N,p)\) if and only if \(i-j \equiv 0 \tmod{p}\). This is impossible since \(i\) and \(j\) are distinct. Hence \(\b'_{i}\) and \(\b'_{j}\) represent distinct cosets. Now consider
        \[
          \b'_{i}{\b'_{\infty}}^{-1} = \begin{pmatrix} 1 & i \\ 0 & 1 \end{pmatrix}\begin{pmatrix} 1 & -n \\ -N & pm \end{pmatrix} = \begin{pmatrix} 1-Ni & pmj-n \\ -N & pm \end{pmatrix}.
        \]
        Now \(\b'_{i}{\b'_{\infty}}^{-1} \in \a^{-1}\G_{1}(N)\a \cap \G_{1}(N) = \G_{1}^{0}(N,p)\) if and only if \(pmi-n \equiv 0 \tmod{p}\). This is impossible since \(pm-Nn = 1\) implies \(p \nmid n\). Therefore \(\b'_{i}\) and \(\b'_{\infty}\) represent distinct cosets. It follows that \(\b'_{1},\ldots,\b'_{p-1}\) and \(\b'_{1},\ldots,\b'_{p-1},\b'_{\infty}\) run over complete sets of representatives for \((\a^{-1}\G_{1}(N)\a \cap \G_{1}(N))\backslash\G_{1}(N)\) depending on if \(p \mid N\) or not. As
        \[
          \a\b'_{j} = \begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix}\begin{pmatrix} 1 & j \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix} = \b_{j} \quad \text{and} \quad \a\b'_{\infty} = \begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix}\begin{pmatrix} pm & n \\ N & 1 \end{pmatrix} = \begin{pmatrix} pm & n \\ Np & p \end{pmatrix} = \b_{\infty},
        \]
        \cref{lem:coset_lemma_2} finishes the proof.
      \end{proof}

      This explicit definition of \(T_{p}\) can be used to compute how the Hecke operators act on the Fourier coefficients of a modular form:

      \begin{proposition}\label{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular}
        Let \(f \in \mc{S}_{k}(\G_{1}(N))\) have Fourier coefficients \(a_{n}(f)\). Then for all primes \(p\), we have
        \[
          (T_{p}f)(z) = \sum_{n \ge 1}\left(a_{np}(f)+\chi_{N,0}(p)p^{k-1}a_{\frac{n}{p}}(\<p\>f)\right)e^{2\pi inz},
        \]
        is the Fourier series of \(T_{p}f\) where it is understood that \(a_{\frac{n}{p}}(f) = 0\) if \(p \nmid n\). Moreover, if \(f \in \mc{S}_{k}(N,\chi)\) then \(T_{p}f \in \mc{S}_{k}(N,\chi)\) and
        \[
          (T_{p}f)(z) = \sum_{n \ge 1}\left(a_{np}(f)+\chi(p)p^{k-1}a_{\frac{n}{p}}(f)\right)e^{2\pi inz},
        \]
        where it is understood that \(a_{\frac{n}{p}}(f) = 0\) if \(p \nmid n\).
      \end{proposition}
      \begin{proof}
        In view of \cref{thm:diamond_operator_decomposition_modular} and the linearity of the Hecke operators, it suffices to assume \(f \in \mc{S}_{k}(N,\chi)\). By \cref{prop:diamond_Hecke_operators_commute_modular}, \(T_{p}f \in \mc{S}_{k}(N,\chi)\). It remains to verify the second formula. Observe that
        \[
          \left(f\bigg\|_{k}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right)(z) = \frac{1}{p}\sum_{n \ge 1}a_{n}(f)e^{\frac{2\pi in(z+j)}{p}}.
        \]
        Summing over all \(j\) modulo \(p\) gives
        \[
          \sum_{j \tmod{p}}\left(f\bigg\|_{k}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right)(z) = \sum_{n \ge 1}a_{n}(f)e^{\frac{2\pi inz}{p}}\frac{1}{p}\sum_{j \tmod{p}}e^{\frac{2\pi nij}{p}}.
        \]
        If \(p \nmid N\) then the inner sum vanishes because it is the sum over all \(p\)-th roots of unity. If \(p \mid N\) then the sum is also \(p\). Therefore
        \[
          \sum_{j \tmod{p}}\left(f\bigg\|_{k}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right)(z) = \sum_{n \ge 1}a_{np}(f)e^{2\pi inz}.
        \]
        If \(p \mid N\) then \cref{prop:explicit_description_of_Hecke_operators_modular} implies
        \begin{equation}\label{equ:Hecke_operator_when_p_divides_modular}
          (T_{p}f)(z) = \sum_{n \ge 1}a_{np}(f)e^{2\pi inz},
        \end{equation}
        which is the claimed Fourier series of \(T_{p}f\). If \(p \nmid N\) then we have the additional term
        \begin{align*}
          \left(f\bigg\|_{k}\begin{pmatrix} m & n \\ N & p \end{pmatrix}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix}\right)(z) &= \left(\<p\>f\bigg\|_{k}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix}\right)(z) \\
          &= p^{k-1}(\<p\>f)(pz) \\
          &= \sum_{n \ge 1}p^{k-1}a_{n}(\<p\>f)e^{2\pi inpz} \\
          &= \sum_{n \ge 1}\chi(p)p^{k-1}a_{n}(f)e^{2\pi inpz},
        \end{align*}
        where the first equality holds because \(\begin{psmallmatrix} m & n \\ N & p \end{psmallmatrix} \in \G_{0}(N)\) and the last equality holds because \(\<p\>f = \chi(p)f\). In this case, \cref{prop:explicit_description_of_Hecke_operators_modular} gives
        \[
          (T_{p}f)(z) = \sum_{n \ge 1}a_{np}(f)+\chi(p)p^{k-1}a_{\frac{n}{p}}(f)e^{2\pi inz}.
        \]
        Since \(\chi(p) = 0\) if \(p \mid N\), these two cases can be expressed together as 
        \[
          (T_{p}f)(z) = \sum_{n \ge 1}\left(a_{np}(f)+\chi(p)p^{k-1}a_{\frac{n}{p}}(f)\right)e^{2\pi inz}.
        \]
      \end{proof}

      We now mention the crucial result about Hecke operators which is that they form a simultaneously commuting family with the diamond operators:

      \begin{proposition}\label{prop:Hecke_operators_commute_modular}
        Let \(p\) and \(q\) be primes and \(d,e \in (\Z/N\Z)^{\ast}\). The Hecke operators \(T_{p}\) and \(T_{q}\) and diamond operators \(\<d\>\) and \(\<e\>\) on \(\mc{S}_{k}(\G_{1}(N))\) form a simultaneously commuting family:
        \[
          T_{p}T_{q} = T_{q}T_{p}, \quad \<d\>T_{p} = T_{p}\<d\>, \quad \text{and} \quad \<d\>\<e\> = \<e\>\<d\>.
        \]
      \end{proposition}
      \begin{proof}
        Showing the diamond and Hecke operators commute was \cref{prop:diamond_Hecke_operators_commute_modular}. To show commutativity of the diamond operators, let \(\g = \begin{psmallmatrix} \ast & \ast \\ \ast & d \end{psmallmatrix} \in \G_{0}(N)\)  and \(\eta = \begin{psmallmatrix} \ast & \ast \\ \ast & e \end{psmallmatrix} \in \G_{0}(N)\). Then
        \[
          \g\eta \equiv \begin{pmatrix} \ast & \ast \\ 0 & de \end{pmatrix} \equiv \begin{pmatrix} \ast & \ast \\ 0 & ed \end{pmatrix} \equiv \eta\g \tmod{N}.
        \]
        So for any \(f \in \mc{S}_{k}(\G_{1}(N))\), we have
        \[
          \<d\>\<e\>f = f\|_{k}\g\eta = f\|_{k}\eta\g = \<e\>\<d\>f.
        \]
        We now show that the Hecke operators commute. In view of \cref{thm:diamond_operator_decomposition_modular} and linearity of the Hecke operators, it suffices to prove this for \(f \in \mc{S}_{k}(N,\chi)\). Applying \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular} twice, for any \(n \ge 1\) we compute
        \begin{align*}
          a_{n}(T_{p}T_{q}f) &= a_{np}(T_{q}f)+\chi(p)p^{k-1}a_{\frac{n}{p}}(T_{q}f) \\
          &= a_{npq}(f)+\chi(q)q^{k-1}a_{\frac{np}{q}}(f)+\chi(p)p^{k-1}(a_{\frac{nq}{p}}(f)+\chi(q)q^{k-1}a_{\frac{n}{pq}}(f)) \\
          &= a_{npq}(f)+\chi(q)q^{k-1}a_{\frac{np}{q}}(f)+\chi(p)p^{k-1}a_{\frac{nq}{p}}(f)+\chi(pq)(pq)^{k-1}a_{\frac{n}{pq}}(f).
        \end{align*}
        The last expression is symmetric in \(p\) and \(q\) so that \(a_{n}(T_{p}T_{q}f) = a_{n}(T_{q}T_{p}f)\) for all \(n \ge 1\). Since all of the Fourier coefficients are equal, we get
        \[
          T_{p}T_{q}f = T_{q}T_{p}f.
        \]
      \end{proof}

      We can use \cref{prop:Hecke_operators_commute_modular} to construct diamond operators \(\<m\>\) and Hecke operators \(T_{m}\) for all \(m \ge 1\). The \textbf{diamond operator}\index{diamond operator} \(\<m\>:\mc{S}_{k}(\G_{1}(N)) \to \mc{S}_{k}(\G_{1}(N))\) is defined to be the linear operator given by
      \[
        \<m\> = \begin{cases} \<m\> \text{ with \(m\) taken modulo \(N\)} & \text{if \((m,N) = 1\)}, \\ 0 & \text{if \((m,N) > 1\)}. \end{cases}
      \]
      Now for the Hecke operators. If \(m = p_{1}^{r_{1}}p_{2}^{r_{2}} \cdots p_{k}^{r_{k}}\) is the prime decomposition of \(m\) then we define the \(m\)-th \textbf{Hecke operator}\index{Hecke operator} \(T_{m}:\mc{S}_{k}(\G_{1}(N)) \to \mc{S}_{k}(\G_{1}(N))\) to be the linear operator given by
      \[
        T_{m} = \prod_{1 \le i \le k}T_{p_{i}^{r_{i}}},
      \]
      where \(T_{p^{r}}\) is defined inductively by
      \[
        T_{p^{r}} = \begin{cases} T_{p}T_{p^{r-1}}-p^{k-1}\<p\>T_{p^{r-2}} & \text{if \(p \nmid N\)}, \\ T_{p}^{r} & \text{if \(p \mid N\)}, \end{cases}
      \]
      for all \(r \ge 2\). Note that when \(m = 1\), the product is empty and so \(T_{1}\) is the identity operator. By \cref{prop:Hecke_operators_commute_modular}, the Hecke operators \(T_{m}\) are multiplicative but not completely multiplicative in \(m\). Moreover, they commute with the diamond operators \(\<m\>\). Using these definitions, \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular,prop:Hecke_operators_commute_modular}, a more general formula for how the Hecke operators \(T_{m}\) act on Fourier coefficients can be derived:

      \begin{proposition}\label{prop:general_Hecke_operators_acting_on_Fourier_coefficients_modular}
        Let \(f \in \mc{S}_{k}(\G_{1}(N))\) have Fourier coefficients \(a_{n}(f)\). Then for \(m \ge 1\) with \((m,N) = 1\), we have
        \[
          (T_{m}f)(z) = \sum_{n \ge 1}\left(\sum_{d \mid (n,m)}d^{k-1}a_{\frac{nm}{d^{2}}}(\<d\>f)\right)e^{2\pi inz},
        \]
        is the Fourier series of \(T_{m}f\). Moreover, if \(f \in \mc{S}_{k}(N,\chi)\) then
        \[
          (T_{m}f)(z) = \sum_{n \ge 1}\left(\sum_{d \mid (n,m)}\chi(d)d^{k-1}a_{\frac{nm}{d^{2}}}(f)\right)e^{2\pi inz}.
        \]
      \end{proposition}
      \begin{proof}
        In view of \cref{thm:diamond_operator_decomposition_modular} and linearity of the Hecke operators, we may assume \(f \in \mc{S}_{k}(N,\chi)\). Therefore we only need to verify the second formula. When \(m = 1\) the result is obvious and when \(m = p\), we have
        \[
          \sum_{d \mid (n,p)}\chi(d)d^{k-1}a_{\frac{np}{d^{2}}}(f) = a_{np}(f)+\chi(p)p^{k-1}a_{\frac{n}{p}}(f),
        \]
        which is the result obtained from \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular}. By induction assume that the desired formula holds for \(m = 1,p,\ldots,p^{r-1}\). Using the definition of \(T_{p^{r}}\) and \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular}, for any \(n \ge 1\) we compute
        \begin{align*}
          a_{n}(T_{p^{r}}f) &= a_{n}(T_{p}T_{p^{r-1}}f)-\chi(p)p^{k-1}a_{n}(T_{p^{r-2}}f) \\
          &= a_{np}(T_{p^{r-1}}f)+\chi(p)p^{k-1}a_{\frac{n}{p}}(T_{p^{r-1}}f)-\chi(p)p^{k-1}a_{n}(T_{p^{r-2}}f).
        \end{align*}
        By our induction hypothesis, this last expression is
        \[
          \sum_{d \mid (np,p^{r-1})}\chi(d)d^{k-1}a_{\frac{np^{r}}{d^{2}}}(f)+\chi(p)p^{k-1}\sum_{d \mid \left(\frac{n}{p},p^{r-1}\right)}\chi(d)d^{k-1}a_{\frac{np^{r-2}}{d^{2}}}(f)-\chi(p)p^{k-1}\sum_{d \mid (n,p^{r-2})}\chi(d)d^{k-1}a_{\frac{np^{r-2}}{d^{2}}}(f).
        \]
        Write the first sum as
        \[
          \sum_{d \mid (np,p^{r-1})}\chi(d)d^{k-1}a_{\frac{np^{r}}{d^{2}}}(f) = a_{np^{r}}(f)+\sum_{d \mid (n,p^{r-2})}\chi(d)d^{k-1}a_{\frac{np^{r-2}}{d^{2}}}(f),
        \]
        and observe that the sum on the right-hand side cancels the entire third term above. Therefore our expression reduces to
        \begin{align*}
          a_{np^{r}}(f)+\chi(p)p^{k-1}\sum_{d \mid \left(\frac{n}{p},p^{r-1}\right)}\chi(d)d^{k-1}a_{\frac{np^{r-2}}{d^{2}}}(f) &= a_{np^{r}}(f)+\sum_{d \mid \left(\frac{n}{p},p^{r-1}\right)}\chi(dp)(dp)^{k-1}a_{\frac{np^{r-2}}{d^{2}}}(f) \\
          &= a_{np^{r}}(f)+\sum_{\substack{d \mid (n,p^{r}) \\ d \neq 1}}\chi(d)d^{k-1}a_{\frac{np^{r}}{d^{2}}}(f) \\
          &= \sum_{d \mid (n,p^{r})}\chi(d)d^{k-1}a_{\frac{np^{r}}{d^{2}}}(f),
        \end{align*}
        where in the second line we have performed the change of variables \(dp \mapsto d\) in the sum. This proves the claim when \(m = p^{r}\) for all \(r \ge 0\). By multiplicativity of the Hecke operators, it suffices to prove the claim when \(m = p^{r}q^{s}\) for another prime \(q\) and some \(s \ge 0\). We compute
        \begin{align*}
          a_{n}(T_{p^{r}q^{s}}f) &= a_{n}(T_{p^{r}}T_{q^{s}}f) \\
          &= \sum_{d_{1} \mid (n,p^{r})}\chi(d_{1})d_{1}^{k-1}a_{\frac{np^{r}}{d_{1}^{2}}}(T_{q^{s}}f) \\
          &= \sum_{d_{1} \mid (n,p^{r})}\chi(d_{1})d_{1}^{k-1}\sum_{d_{2} \mid \left(\frac{np^{r}}{d_{1}^{2}},q^{s}\right)}\chi(d_{2})d_{2}^{k-1}a_{\frac{np^{r}q^{s}}{(d_{1}d_{2})^{2}}}(f) \\
          &= \sum_{d_{1} \mid (n,p^{r})}\sum_{d_{2} \mid \left(\frac{np^{r}}{d_{1}^{2}},q^{s}\right)}\chi(d_{1}d_{2})(d_{1}d_{2})^{k-1}a_{\frac{np^{r}q^{s}}{(d_{1}d_{2})^{2}}}(f).
        \end{align*}
        Summing over pairs \((d_{1},d_{2})\) of divisors of \((n,p^{r})\) and \(\left(\frac{np^{r}}{d^{2}},q^{s}\right)\) respectively is the same as summing over divisors \(d\) of \((n,p^{r}q^{s})\). Indeed, because \(p\) and \(q\) are relative prime, any such \(d\) is of the form \(d = d_{1}d_{2}\) where \(d_{1} \mid (n,p^{r})\) and \(d_{2} \mid \left(\frac{np^{r}}{d_{2}^{2}},q^{s}\right)\). Therefore the double sum becomes
        \[
          \sum_{d \mid (n,p^{r}q^{s})}\chi(d)d^{k-1}a_{\frac{np^{r}q^{s}}{d^{2}}}(f).
        \]
        This completes the proof.
      \end{proof}

      The diamond and Hecke operators turn out to be normal on the subspace of cusp forms. To prove this fact, we will require a lemma:

      \begin{lemma}\label{lem:adjoint_lemma}
        Let \(\G\) be a congruence subgroup and let \(\a \in \GL_{2}^{+}(\Q)\). Then there exist \(\b_{1},\ldots,\b_{n} \in \GL_{2}^{+}(\Q)\), where \(n = [\G:\a^{-1}\G\a \cap \G] = [\G:\a\G\a^{-1} \cap \G]\), and such that
        \[
          \G\a\G = \bigcup_{1 \le j \le n}\G\b_{j} = \bigcup_{1 \le j \le n}\b_{j}\G.
        \]
      \end{lemma}
      \begin{proof}
        By \cref{lem:coset_lemma_1} and that congruence subgroups are preserved under intersection, we see that \(\a\G\a^{-1} \cap \G\) is a congruence subgroup. By \cref{lem:invariance_of_volume}, it follows that \(d_{\a^{-1}\G\a \cap \G} = d_{\a\G\a^{-1} \cap \G}\). Dividing both sides by \(d_{\G}\) gives
        \[
          [\G:\a^{-1}\G\a \cap \G] = [\G:\a\G\a^{-1} \cap \G].
        \]
        Therefore we can find representatives \(\g_{1},\ldots,\g_{n} \in \G\) and \(\wtilde{\g}_{1},\ldots,\wtilde{\g}_{n} \in \G\) such that
        \[
          \G = \bigcup_{1 \le j \le n}(\a^{-1}\G\a \cap \G)\g_{j} = \bigcup_{1 \le j \le n}(\a^{-1}\G\a \cap \G)\wtilde{\g}_{j}^{-1}.
        \]
        Upon invoking \cref{lem:coset_lemma_2} twice, we obtain
        \[
          \bigcup_{1 \le j \le n}(\a^{-1}\G\a \cap \G)\g_{j} = \bigcup_{1 \le j \le n}\G\a\g_{j} \quad \text{and} \quad \bigcup_{1 \le j \le n}(\a^{-1}\G\a \cap \G)\wtilde{\g}_{j}^{-1} = \bigcup_{1 \le j \le n}\G\a^{-1}\wtilde{\g}_{j}^{-1}.
        \]
        It follows that
        \[
          \G = \bigcup_{1 \le j \le n}\G\a\g_{j} = \bigcup_{1 \le j \le n}\wtilde{\g}_{j}\a\G.
        \]
        For each \(j\), the orbits \(\G\a\g_{j}\) and \(\wtilde{\g}_{j}\a\G\) have nonempty intersection. For if they did we would have
        \[
          \G\a\g_{j} \subseteq \bigcup_{\substack{1 \le i \le n \\ i \neq j}}\wtilde{\g}_{i}\a\G,
        \]
        and thus
        \[
          \G\a\G \subseteq \bigcup_{\substack{1 \le i \le n \\ i \neq j}}\wtilde{\g}_{i}\a\G.
        \]
        This contradicts the previous decomposition of \(\G\). Therefore we can find representatives \(\b_{j} \in \G\a\g_{j} \cap \wtilde{\g}_{j}\a\G\) for every \(j\). Then
        \[
          \G = \bigcup_{1 \le j \le n}\G\b_{j} = \bigcup_{1 \le j \le n}\b_{j}\G,
        \]
        as desired.
      \end{proof}

      We can use \cref{lem:adjoint_lemma} to compute adjoints:

      \begin{proposition}\label{prop:Petersson_adjoint_modular}
        Let \(\G\) be a congruence subgroup and let \(\a \in \GL_{2}^{+}(\Q)\). Set \(\a' = \det(\a)\a^{-1}\). Then the following are true:
        \begin{enumerate}[label*=(\roman*)]
          \item If \(\a^{-1}\G\a \subseteq \SL_{2}(\Z)\) then for all \(f \in \mc{S}_{k}(\G)\) and \(g \in \mc{S}_{k}(\a^{-1}\G\a)\), we have
          \[
            \<f|_{k}\a,g\>_{\a^{-1}\G\a} = \<f,g|_{k}\a'\>_{\G}.
          \]
          \item For all \(f,g \in \mc{S}_{k}(\G)\), we have
          \[
            \<f[\G\a\G]_{k},g\> = \<f,g[\G\a'\G]_{k}\>.
          \]
        \end{enumerate}
        In particular, if \(\a^{-1}\G\a = \G\) then \(|_{k}\a^{\ast} = |_{k}\a'\), \(\|_{k}\a^{\ast} = \|_{k}\a'\), and \([\G\a\G]_{k}^{\ast} = [\G\a'\G]_{k}\).   
      \end{proposition}
      \begin{proof}
        To prove (i) we first compute
        \begin{align*}
          \<f|_{k}\a,g\>_{\a^{-1}\G\a} &= \frac{1}{V_{\a^{-1}\G\a}}\int_{\mc{F}_{\a^{-1}\G\a}}(f|_{k}\a)(z)\conj{g(z)}\Im(z)^{k}\,d\mu \\
          &= \frac{1}{V_{\a^{-1}\G\a}}\int_{\mc{F}_{\a^{-1}\G\a}}\det(\a)^{\frac{k}{2}}j(\a,z)^{-k}f(\a z)\conj{g(z)}\Im(z)^{k}\,d\mu \\
          &= \frac{1}{V_{\G}}\int_{\mc{F}_{\a^{-1}\G\a}}\det(\a)^{\frac{k}{2}}j(\a,z)^{-k}f(\a z)\conj{g(z)}\Im(z)^{k}\,d\mu && \text{\cref{lem:invariance_of_volume}} \\
          &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\det(\a)^{\frac{k}{2}}j(\a,\a^{-1}z)^{-k}f(z)\conj{g(\a^{-1}z)}\Im(\a^{-1}z)^{k}\,d\mu && \text{\(z \mapsto \a^{-1}z\).}
        \end{align*}
        As \(\a'\) acts as \(\a^{-1}\) on \(\H\) and \(\det(\a') = \det(\a)\), using \cref{equ:Mobius_transformation_imaginary_part_j}, this latter integral is equivalent to
        \[
          \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\det(\a')^{\frac{3k}{2}}j(\a,\a'z)^{-k}f(z)\conj{g(\a'z)}\Im(\a'z)^{k}\,d\mu.
        \]
        Applying the cocycle condition, \cref{equ:Mobius_transformation_imaginary_part_j}, and the identity \(j(\a\a',z) = \det(\a')\), we can further rewrite the integral as
        \[
          \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\det(\a')^{\frac{k}{2}}\conj{j(\a',z)^{-k}}f(z)\conj{g(\a'z)}\Im(z)^{k}\,d\mu.
        \]
        Reversing the first computation in the start of the proof but applied to this integral shows that that
        \[
          \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\det(\a')^{\frac{k}{2}}\conj{j(\a',z)^{-k}}f(z)\conj{g(\a'z)}\Im(z)^{k}\,d\mu = \<f,g|_{k}\a'\>_{\G},
        \]
        which completes the proof of (i). To prove (ii), \cref{lem:adjoint_lemma} implies the coset decomposition \(\G\a\G = \bigcup_{1 \le j \le n}\G\b_{j}\), with \(n = [\G:\a^{-1}\G\a \cap \G] = [\G:\a\G\a^{-1} \cap \G]\), so that we can use the \(\b_{j}\) as representatives for the \([\G\a\G]_{k}\) operator. As the \(\b_{j}\) also satisfy \(\G\a\G = \bigcup_{1 \le j \le n}\b_{j}\G\), upon inverting \(\b_{j}\) and noting that \(\b_{j} \in \G\a\), we obtain \(\G\a^{-1}\G = \bigcup_{1 \le j \le n}\G\b_{j}^{-1}\). Since scalar multiplication commutes with matrices and the matrices in \(\G\) have determinant \(1\), we conclude that \(\G\a'\G = \bigcup_{1 \le j \le n}\G\b_{j}'\) where \(\b_{j}' = \det(\b_{j})\b_{j}^{-1}\) (also \(\det(\b_{j}) = \det(\a)\)). So we can use the \(\b_{j}'\) as representatives in the \([\G\a'\G]_{k}\) operator. The statement now follows from (i) and \cref{equ:relationship_between_slash_operators}. The last statement is obvious (again using \cref{equ:relationship_between_slash_operators}).
      \end{proof}

      We can now prove that the diamond and Hecke operators are normal:

      \begin{proposition}\label{prop:Hecke_operators_normal_modular}
        On \(\mc{S}_{k}(\G_{1}(N))\), the diamond operators \(\<m\>\) and Hecke operators \(T_{m}\) are normal for all \(m \ge 1\) with \((m,N) = 1\). Moreover, their adjoints are given by
        \[
          \<m\>^{\ast} = \<\conj{m}\> \quad \text{and} \quad T_{p}^{\ast} = \<\conj{p}\>T_{p}.
        \]
      \end{proposition}
      \begin{proof}
        By multiplicativity of the diamond and Hecke operators, it suffices to prove the two formulas when \(m = p\) for a prime \(p \nmid N\). We will prove the adjoint formula for diamond operators first. Let \(\a = \begin{psmallmatrix} \conj{p} & \ast \\ \ast & p \end{psmallmatrix} \in \G_{0}(N)\) and \(\a' = \det(\a)\a^{-1} = \begin{psmallmatrix} p & \ast \\ \ast & \conj{p} \end{psmallmatrix} \in \G_{0}(N)\). Then \cref{prop:Petersson_adjoint_modular} implies
        \[
          \<p\>^{\ast} = \<\conj{p}\>.
        \]
        This proves the adjoint formula for the diamond operators and normality follows from multiplicativity. For the Hecke operators, let \(\a = \begin{psmallmatrix} 1 & 0 \\ 0 & p \end{psmallmatrix}\) and set \(\a' = \det(\a)\a^{-1} = \begin{psmallmatrix} p & 0 \\ 0 & 1 \end{psmallmatrix}\). Also let \(m\) and \(n\) be such that \(\det\left(\begin{psmallmatrix} m & n \\ N & p \end{psmallmatrix}\right) = 1\) (by B\'ezout's identity). Observe that
        \[
          \begin{pmatrix} 1 & n \\ N & pm \end{pmatrix}^{-1}\a\begin{pmatrix} p & n \\ N & m \end{pmatrix} = \begin{pmatrix} pm & -n \\ -N & 1 \end{pmatrix}\begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix}\begin{pmatrix} p & n \\ N & m \end{pmatrix} = \a'.
        \]
        Now \(\begin{psmallmatrix} 1 & n \\ N & pm \end{psmallmatrix} \in \G_{1}(N)\) (note that \(pm \equiv 1 \tmod{N}\) since \(pm-Nn = 1\)) and \(\begin{psmallmatrix} p & n \\ N & m \end{psmallmatrix} \in \G_{0}(N)\). These facts and that \(\G_{1}(N)\) is normal in \(\G_{0}(N)\) together imply
        \[
          \G_{1}(N)\a'\G_{1}(N) = \G_{1}(N)\a\G_{1}(N)\begin{pmatrix} p & n \\ N & m \end{pmatrix}.
        \]
        As \(m \equiv \conj{p} \tmod{N}\), the above identity and \cref{prop:Petersson_adjoint_modular} together give
        \[
          T_{p}^{\ast} = \<\conj{p}\>T_{p}.
        \]
        This proves the adjoint formula for the Hecke operators and normality follows from multiplicativity.
      \end{proof}

      Note that on \(\mc{S}_{k}(\SL_{2}(\Z))\), all of the diamond operators are the identity and therefore \(T_{p}^{\ast} = T_{p}\) for all primes \(p\). That is, the Hecke operators are self-adjoint (as are the diamond operators since they are the identity). Now suppose \(f\) is a non-constant cusp form. Let the eigenvalue of \(T_{m}\) for \(f\) be \(\l_{f}(m)\). We say that the \(\l_{f}(m)\) are the \textbf{Hecke eigenvalues}\index{Hecke eigenvalues} of \(f\). If \(f\) is a simultaneous eigenfunction for all diamond operators \(\<m\>\) and Hecke operators \(T_{m}\) with \((m,N) = 1\), we call \(f\) an \textbf{eigenform}\index{eigenform}. If the condition \((m,N) = 1\) can be dropped, so that \(f\) is a simultaneous eigenfunction for all diamond and Hecke operators, we say \(f\) is a \textbf{Hecke eigenform}\index{Hecke eigenform}. In particular, on \(\SL_{2}(\Z)\backslash\H\) all eigenforms are Hecke eigenforms. Now let \(f\) have Fourier coefficients \(a_{n}(f)\). If \(f\) is a Hecke eigenform then \cref{prop:general_Hecke_operators_acting_on_Fourier_coefficients_modular} immediately implies that the first Fourier coefficient of \(T_{m}f\) is \(a_{m}(f)\) and so
      \[
        a_{m}(f) = \l_{f}(m)a_{1}(f),
      \]
      for all \(m \ge 1\). Therefore we cannot have \(a_{1}(f) = 0\) for this would mean \(f\) is constant. So we can normalize \(f\) by dividing by \(a_{1}(f)\) which guarantees that this Fourier coefficient is \(1\). It follows that
      \[
        a_{m}(f) = \l_{f}(m),
      \]
      for all \(m \ge 1\). This normalization is called the \textbf{Hecke normalization}\index{Hecke normalization} of \(f\). The \textbf{Petersson normalization}\index{Petersson normalization} of \(f\) is where we normalize so that \(\<f,f\> = 1\). In particular, any orthonormal basis of \(\mc{S}_{k}(\G_{1}(N))\) is Petersson normalized. From the spectral theorem we derive an important corollary:

      \begin{theorem}\label{thm:eigenforms_forms_spectral_theory_modular}
        \(\mc{S}_{k}(\G_{1}(N))\) admits an orthonormal basis of eigenforms.
      \end{theorem}
      \begin{proof}
        By \cref{thm:modular_forms_finite_dimensional}, \(\mc{S}_{k}(\G_{1}(N))\) is finite dimensional. The claim then follows from the spectral theorem along with \cref{prop:Hecke_operators_commute_modular,prop:Hecke_operators_normal_modular}.
      \end{proof}

      The Hecke eigenvalues of Hecke eigenforms satisfy certain relations known as the \textbf{Hecke relations}\index{Hecke relations} for modular forms:

      \begin{proposition*}[Hecke relations, modular]
      Let \(f \in \mc{S}_{k}(N,\chi)\) be a Hecke eigenform with Hecke eigenvalues \(\l_{f}(m)\). Then the Hecke eigenvalues are multiplicative and satisfy
      \[
        \l_{f}(n)\l_{f}(m) = \sum_{d \mid (n,m)}\chi(d)d^{k-1}\l_{f}\left(\frac{nm}{d^{2}}\right) \quad \text{and} \quad \l_{f}(nm) = \sum_{d \mid (n,m)}\mu(d)\chi(d)d^{k-1}\l_{f}\left(\frac{n}{d}\right)\l_{f}\left(\frac{m}{d}\right),
      \]
      for all \(n,m \ge 1\) with \((nm,N) = 1\). Moreover,
      \[
        \l_{f}(p^{r}) = \l_{f}(p)^{r},
      \]
      for all \(p \mid N\) and \(r \ge 2\).
      \end{proposition*}
      \begin{proof}
        If necessary, Hecke normalize \(f\). The multiplicativity of the Hecke eigenvalues now follows from the multiplicativity of the Hecke operators. The first identity follows from computing the \(n\)-th Fourier coefficient of \(T_{m}f\) in two different ways. On the one hand, use that \(f\) is a Hecke eigenform to get \(\l_{f}(n)\l_{f}(m)\). On the other hand, use \cref{prop:general_Hecke_operators_acting_on_Fourier_coefficients_modular} to obtain \(\sum_{d \mid (n,m)}\chi(d)d^{k-1}\l_{f}\left(\frac{nm}{d^{2}}\right)\). For the second identity, computing the \(p\)-th Fourier coefficient of \(T_{p}\) in two different ways just as before, we have
        \[
          \chi(p)p^{k-1} = \l_{f}(p)^{2}-\l_{f}(p^{2}),
        \]
        provided \((p,N) = 1\). As the left-hand sides is completely multiplicative, the first identity implies that \(\l_{f}(n)\) is specially multiplicative. The second identity now follows from \cref{prop:specially_multiplicative_functions}. The third identity follows from inspecting the first Fourier coefficient of \(T_{p^{r}}f\) and noting that \(T_{p^{r}} = T_{p}^{r}\) provided \(p \mid N\).
      \end{proof}

      As an immediate consequence of the Hecke relations, the Hecke operators satisfy analogous relations:

      \begin{corollary}\label{cor:Hecke_relations_operator_modular}
        The Hecke operators are multiplicative and satisfy
        \[
          T_{n}T_{m} = \sum_{d \mid (n,m)}\chi(d)d^{k-1}T_{\frac{nm}{d^{2}}} \quad \text{and} \quad T_{nm} = \sum_{d \mid (n,m)}\mu(d)\chi(d)d^{k-1}T_{\frac{n}{d}}T_{\frac{m}{d}},
        \]
        for all \(n,m \ge 1\) with \((nm,N) = 1\).
      \end{corollary}
      \begin{proof}
        This is immediate from \cref{thm:eigenforms_forms_spectral_theory_modular} and the Hecke relations.
      \end{proof}

      The identities in \cref{cor:Hecke_relations_operator_modular} can also be established directly. Moreover, the first identity is symmetric in \(n\) and \(m\) so it can be used to show that the Hecke operators commute.\fi
    \iffalse\subsection{\todo{Atkin-Lehner Theory}}
      So far, our entire theory of modular forms has started with a fixed congruence subgroup of some level. Atkin-Lehner theory, or the theory of oldforms and newforms, allows us to discuss modular forms in the context of moving between levels. In this setting, we will only deal with congruence subgroups of the form \(\G_{1}(N)\) and \(\G_{0}(N)\). The easiest way lift a modular form from a smaller level to a larger level is to observe that if \(M \mid N\) then \(\G_{1}(N) \subseteq \G_{1}(M)\) so there is a natural inclusion \(\mc{S}_{k}(\G_{1}(M)) \subseteq \mc{S}_{k}(\G_{1}(N))\). There is a less trivial way of lifting from \(\mc{S}_{k}(\G_{1}(M))\) to \(\mc{S}_{k}(\G_{1}(N))\). For any \(d \mid \frac{N}{M}\), let
      \[
        \a_{d} = \begin{pmatrix} d & 0 \\ 0 & 1 \end{pmatrix}.
      \]
      If \(f \in \mc{S}_{k}(\G_{1}(M))\), we consider
      \[
        (f\|_{k}\a_{d})(z) = d^{k-1}f(dz).
      \]
      It turns out that \(\|_{k}\a_{d}\) maps \(\mc{S}_{k}(\G_{1}(M))\) into \(\mc{S}_{k}(\G_{1}(N))\) and more:
      
      \begin{proposition}\label{equ:lifting_operator_modular}
        Let \(M\) and \(N\) be positive integers such that \(M \mid N\). For any \(d \mid \frac{N}{M}\), \(\|_{k}\a_{d}\) maps \(\mc{S}_{k}(\G_{1}(M))\) into \(\mc{S}_{k}(\G_{1}(N))\). In particular, \(\|_{k}\a_{d}\) takes \(\mc{S}_{k}(M,\chi)\) into \(\mc{S}_{k}(N,\chi)\).
      \end{proposition}
      \begin{proof}
        By \cref{thm:diamond_operator_decomposition_modular}, it suffices to verify only the latter statement so we may assume \(f \in \mc{S}_{k}(M,\chi)\). It is clear that holomorphy is satisfied for \(f\|_{k}\a_{d}\). To verify modularity, let \(\g = \begin{psmallmatrix} a & b \\ c & d' \end{psmallmatrix} \in \G_{1}(N)\) and set \(\g' = \begin{psmallmatrix} a & bd \\ d^{-1}c & d' \end{psmallmatrix} \in \G_{1}(M)\) (because \(c \equiv 0 \tmod{N}\) and \(d \mid \frac{N}{M}\)). Then
        \[
          \a_{d}\g\a_{d}^{-1} = \begin{pmatrix} d & 0 \\ 0 & 1 \end{pmatrix}\begin{pmatrix} a & b \\ c & d' \end{pmatrix}\begin{pmatrix} d^{-1} & 0 \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} a & bd \\ d^{-1}c & d' \end{pmatrix} = \g',
        \]
        and therefore \(\a_{d}\G_{1}(N)\a_{d}^{-1} \subseteq \G_{1}(M)\), or equivalently, \(\G_{1}(N) \subseteq \a_{d}^{-1}\G_{1}(M)\a_{d}\). It is also clear that \(\chi(\g') = \chi(\g)\). Using these facts, we compute
        \begin{align*}
          ((f\|_{k}\a_{d})|_{k}\g)(z) &= d^{\frac{k}{2}-1}(f|_{k}\a_{d}\g)(z) && \text{\cref{equ:relationship_between_slash_operators}} \\
          &= d^{\frac{k}{2}-1}(f|_{k}\g'\a_{d})(z) \\
          &= \chi(\g')d^{\frac{k}{2}-1}(f|_{k}\a_{d})(z) && \text{modularity} \\
          &= \chi(\g)d^{\frac{k}{2}-1}(f|_{k}\a_{d})(z) \\
          &= \chi(\g)(f\|_{k}\a_{d})(z).
        \end{align*}
        This verifies modularity of \(f\|_{k}\a_{d}\). For the growth condition, let \(\s_{\mf{a}}\) be a scaling matrix for a cusp \(\mf{a}\) of \(\G_{1}(M)\backslash\H\). Then \(\a_{d}\s_{\mf{a}}\) takes \(\infty\) to an element of \(\what{\Q}\) since \(\a_{d} \in \GL_{2}^{+}(\Q)\). In other words, \(\a_{d}\s_{\mf{a}}\infty = \mf{b}\) for some cusp \(\mf{b}\) of \(\G_{1}(N)\backslash\H\). Then by \cref{equ:relationship_between_slash_operators},
        \[
          ((f\|_{k}\a_{d})|_{k}\s_{\mf{a}})(z) = d^{\frac{k}{2}-1}(f|_{k}\a_{d}\s_{\mf{a}})(z),
        \]
        and so the growth condition follows from that of \(f\). In particular, \(f\|_{k}\a_{d}\) is a cusp form since \(f\) is.
      \end{proof}

      We can now define oldforms and newforms. For each divisor \(d\) of \(N\), set
      \[
        i_{d}:\mc{S}_{k}\left(\G_{1}\left(\frac{N}{d}\right)\right) \op \mc{S}_{k}\left(\G_{1}\left(\frac{N}{d}\right)\right) \to \mc{S}_{k}(\G_{1}(N)) \qquad (f,g) \mapsto f+g\|_{k}\a_{d}.
      \]
      This map is well-defined by \cref{equ:lifting_operator_modular}. The subspace of \textbf{oldforms}\index{oldforms} of level \(N\) is
      \[
        \mc{S}_{k}^{\mathrm{old}}(\G_{1}(N)) = \bigop_{p \mid N}\Im(i_{p}),
      \]
      and the subspace of \textbf{newforms}\index{newforms} of level \(N\) is
      \[
        \mc{S}_{k}^{\mathrm{new}}(\G_{1}(N)) = \mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))^{\perp}.
      \]
      An element of these subspaces is called an \textbf{oldform}\index{oldform} or \textbf{newform}\index{newform} respectively. Note that there are no oldforms of level \(1\). We will need a useful operator for the study of oldforms and newforms. Let
      \[
        W_{N} = \begin{pmatrix} 0 & -1 \\ N & 0 \end{pmatrix},
      \]
      and note that \(\det(W_{N}) = N\). This matrix normalizes \(\G_{0}(N)\). Indeed, let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}(N)\) and set \(g' = \begin{psmallmatrix} d & -N^{-1}c \\ -Nb & a \end{psmallmatrix} \in \G_{0}(N)\). Then
      \begin{equation}\label{equ:Atkin_Lehner_normalization}
        W_{N}\g W_{N}^{-1} = \begin{pmatrix} 0 & -1 \\ N & 0 \end{pmatrix}\begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} 0 & N^{-1} \\ -1 & 0 \end{pmatrix} = \begin{pmatrix} d & -N^{-1}c \\ -Nb & a \end{pmatrix} = \g'.
      \end{equation}
      It follows that \(W_{N}\) normalizes \(\G_{0}(N)\) as claimed. We define the \textbf{Atkin-Lehner operator}\index{Atkin-Lehner operator} \(\w_{N}\) to be the linear operator on \(\mc{S}_{k}(\G_{1}(N))\) given by
      \[
        (\w_{N}f)(z) = N^{1-k}(f\|_{k}W_{N})(z).
      \]
      As \(W_{N}\) is invertible, so is the Atkin-Lehner operator \(\w_{N}\). It is not difficult to see how the Atkin-Lehner operator acts on \(\mc{S}_{k}(\G_{1}(N))\):

      \begin{proposition}\label{prop:Atkin_Lehner_modular}
        The Atkin-Lehner operator \(\w_{N}\) maps \(\mc{S}_{k}(\G_{1}(N))\) into itself. In particular, \(\w_{N}\) takes \(\mc{S}_{k}(N,\chi)\) into \(\mc{S}_{k}(N,\cchi)\) and preserves the subspaces of oldforms and newforms. Moreover, the adjoint is given by
        \[
          \w_{N}^{\ast} = (-1)^{k}\w_{N}.
        \]
        We also have
        \[
          \w_{N}^{2} = (-1)^{k}.
        \]
      \end{proposition}
      \begin{proof}
        In light of \cref{thm:diamond_operator_decomposition_modular}, the first statement is a consequence of the latter ones. Therefore we may assume \(f \in \mc{S}_{k}(N,\chi)\). Holomorphy is obvious. For modularity, let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}(N)\) and set \(\g' = \begin{psmallmatrix} d & -N^{-1}c \\ -Nb & a \end{psmallmatrix} \in \G_{0}(N)\). Then \(W_{N}\g = \g'W_{N}\) by \cref{equ:Atkin_Lehner_normalization} and we also have \(\chi(\g') = \cchi(\g)\) because \(ad \equiv 1 \tmod{N}\). Using these facts, we compute
        \begin{align*}
          ((\w_{N}f)|_{k}\g)(z) &= N^{-\frac{k}{2}}(f|_{k}W_{N}\g)(z) && \text{\cref{equ:relationship_between_slash_operators}} \\
          &= N^{-\frac{k}{2}}(f|_{k}\g'W_{N})(z) \\
          &= \chi(\g')N^{-\frac{k}{2}}(f|_{k}W_{N})(z) && \text{modularity} \\
          &= \cchi(\g)N^{1-k}(f\|_{k}W_{N})(z) \\
          &= \cchi(\g)(\w_{N}f)(z).
        \end{align*}
        This verifies modularity of \(\w_{N}f\). As for the growth condition, let \(\s_{\mf{a}}\) be a scaling matrix for a cusp \(\mf{a}\). Then \(W_{N}\s_{\mf{a}}\) takes \(\infty\) to an element of \(\what{\Q}\) since \(W_{N} \in \GL_{2}^{+}(\Q)\). In other words, \(W_{N}\s_{\mf{a}}\infty = \mf{b}\) for some cusp \(\mf{b}\). Then
        \[
          ((\w_{N}f)|_{k}\s_{\mf{a}})(z) = N^{-\frac{k}{2}}(f|_{k}W_{N}\s_{\mf{a}})(z),
        \]
        and so the growth condition follows from that of \(f\). In particular, \(\w_{N}f\) is a cusp form because \(f\) is. It total we have shown that \(\w_{N}f \in \mc{S}_{k}(N,\cchi)\). We now prove the adjoint formula for the Atkin-Lehner operator. Let \(W_{N}' = \det(W_{N})W_{N}^{-1}\). Then \(W_{N}' = -W_{N}\). Since \(W_{N}\) normalizes \(\G_{0}(N)\) so does \(-W_{N}\). As \(-W_{N}\) and \(W_{N}\) act the same on \(\H\), \cref{prop:Petersson_adjoint_modular} implies that
        \[
          \w_{N}^{\ast} = (-1)^{k}\w_{N}.
        \]
        This proves the adjoint formula for the Atkin-Lehner operator. We now show that the Atkin-Lehner operator preserves the subspaces of oldforms and newforms. To show that it preserves \(\mc{S}_{k}^{\text{old}}(\G_{1}(N))\), let \(h = f+g\|_{k}\a_{p}\) be in the image of \(i_{p}\), with \(p \mid N\), so that \(i_{p}(f,g) = h\). Then it suffices to show
        \[
          \w_{N}i_{p}(f,g) = i_{p}(\w_{\frac{N}{p}}p^{k-2}g,\w_{\frac{N}{p}}p^{1-k}f).
        \]
        This will follow from the formulas
        \[
          \w_{N}f = (\w_{\frac{N}{p}}p^{1-k}f)\|_{k}\a_{p} \quad \text{and} \quad \w_{N}(g\|_{k}\a_{p}) = \w_{\frac{N}{p}}(p^{k-2}g),
        \]
        which are implied by the identities
        \[
          W_{N} = W_{\frac{N}{p}}\a_{p} \quad \text{and} \quad \a_{p}W_{N} = I_{p}W_{\frac{N}{p}}.
        \]
        Thus the Atkin-Lehner operator \(\w_{N}\) preserves the subspace of oldforms. To see that \(\w_{N}\) preserves the subspace of newforms as well, let \(f\) and \(g\) be a newform and an oldform respectively. The adjoint formula for \(\w_{N}\) and that it preserves the subspace of oldforms gives
        \[
          \<\w_{N}f,g\> = (-1)^{k}\<f,\w_{N}g\> = 0.
        \]
        Hence \(\w_{N}f\) must also be a newform and so \(\w_{N}\) preserves the subspace of newforms. It remains to prove the last formula. For this, observe that \(W_{N}^{2} = -I_{N}\). This fact and \cref{equ:relationship_between_slash_operators} together imply
        \[
          (\w_{N}^{2}f)(z) = N^{-k}(f|_{k}W_{N}^{2})(z) = N^{-k}(f|_{k}(-I_{N}))(z) = (-1)^{k}f.
        \]
        This completes the proof
      \end{proof}

      \cref{prop:Atkin_Lehner_modular} shows that the Atkin-Lehner operator \(\w_{N}\) is self-adjoint and an involution if \(k\) is even. In fact, regardless of the parity of \(k\), \(\w_{N}\) is at most of order \(4\). We now need to understand how the Atkin-Lehner operator interacts with the diamond and Hecke operators:

      \begin{proposition}\label{prop:Atkin_Lehner_adjoint_diamond_Hecke_modular}
        On \(\mc{S}_{k}(\G_{1}(N))\), the diamond operators \(\<m\>\) and Hecke operators \(T_{m}\) satisfy the adjoint formulas
        \[
          \<m\>^{\ast} = \w_{N}\<m\>\w_{N}^{-1} \quad \text{and} \quad T_{m}^{\ast} = \w_{N}T_{m}\w_{N}^{-1},
        \]
        for all \(m \ge 1\).
      \end{proposition}
      \begin{proof}
        By multiplicativity of the diamond and Hecke operators, it suffices to prove the two adjoint formulas when \(m = p\) for a prime \(p\). For the diamond operators, the formula is obvious when \(p \mid N\) since \(\<p\>\) is the zero operator. So suppose \(p \nmid N\), let \(\a = \begin{psmallmatrix} \conj{p} & \ast \\ \ast & p \end{psmallmatrix} \in \G_{0}(N)\) and set \(\a' = \det(\a)\a^{-1} = \begin{psmallmatrix} p & \ast \\ \ast & \conj{p} \end{psmallmatrix} \in \G_{0}(N)\). \cref{equ:Atkin_Lehner_normalization} shows that \(\a' = W_{N}\begin{psmallmatrix} \conj{p} & \ast \\ \ast & p \end{psmallmatrix}W_{N}^{-1}\) for some \(\begin{psmallmatrix} \conj{p} & \ast \\ \ast & p \end{psmallmatrix} \in \G_{0}(N)\). Then \cref{prop:Petersson_adjoint_modular} gives
        \[
          \<p\>^{\ast} = \w_{N}\<p\>\w_{N}^{-1}.
        \]
        This is the desired adjoint formula for the diamond operators when \(p \mid N\). Thus the adjoint formula holds for all the diamond operators. For the Hecke operators, let \(\a = \begin{psmallmatrix}1 & 0 \\ 0 & p\end{psmallmatrix}\) and set \(\a' = \det(\a)\a^{-1} = \begin{psmallmatrix} p & 0 \\ 0 & 1\end{psmallmatrix}\). \cref{equ:Atkin_Lehner_normalization} shows that \(\a' = W_{N}\a W_{N}^{-1}\). Then \cref{prop:Petersson_adjoint_modular} gives
        \[
          T_{p}^{\ast} = \w_{N}T_{p}\w_{N}^{-1}.
        \]
        This is the desired adjoint formula for the Hecke operators.
      \end{proof}
      
      It turns out that the spaces of oldforms and newforms are invariant under the diamond and Hecke operators:

      \begin{proposition}\label{prop:old/new_subspaces_are_invariant_modular}
        On \(\mc{S}_{k}(\G_{1}(N))\), the diamond operators \(\<m\>\) and Hecke operators \(T_{m}\) preserve the subspaces of oldforms and newforms for all \(m \ge 1\).
      \end{proposition}
      \begin{proof}
        By multiplicativity of the diamond and Hecke operators, it suffices to prove this when \(m\) is prime. Moreover, if \(N = 1\) the result is trivial because there are no oldforms. Therefore we may assume \(N > 1\) and hence consider a prime \(p\) with \(p \mid N\). We will first show that the diamond and Hecke operators preserve \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\). Let \(h = f+g\|_{k}\a_{p}\) be in the image of \(i_{p}\) so that \(i_{p}(f,g) = h\) and let \(q\) be a prime. For the diamond operators, it suffices to show
        \[
          \<q\>i_{p}(f,g) = i_{p}(\<q\>f,\<q\>g).
        \]
        This will follow from the formulas
        \[
          \<q\>f = \<q\>f \quad \text{and} \quad \<q\>(g\|_{k}\a_{p}) = (\<q\>g)\|_{k}\a_{p},
        \]
        where the diamond operators on the left-hand and right-hand sides are on levels \(N\) and \(\frac{N}{p}\) respectively. Both formulas are trivial if \(q \mid N\) because then \(\<q\>\) is the zero operator. So suppose \(q \nmid N\). If \(\a = \begin{psmallmatrix} \ast & \ast \\ \ast & q \end{psmallmatrix} \in \G_{0}(N)\) then \(\a \in \G_{0}\left(\frac{N}{p}\right)\) and the first formula follows. The second formula follows from the identity
        \[
          \begin{pmatrix} \ast & \ast \\ \ast & q \end{pmatrix}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix}\begin{pmatrix} \ast & \ast \\ \ast & q \end{pmatrix}.
        \]
        Therefore the diamond operators preserve \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\). The case for the Hecke operators is slightly more involved. Consider the Hecke operator \(T_{q}\) for a prime \(p\) with \(q \neq p\). For this Hecke operator, it suffices to show
        \[
          T_{q}i_{p}(f,g) = i_{p}(T_{q}f,T_{q}g).
        \]
        This will follow from the formulas
        \[
          T_{q}f = T_{q}f \quad \text{and} \quad T_{q}(g\|_{k}\a_{p}) = (T_{q}g)\|_{k}\a_{p},
        \]
        where the Hecke operators on the left-hand and right-hand sides are on levels \(N\) and \(\frac{N}{p}\) respectively. The first formula follows immediately from \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular} since this shows that the action of the Hecke operators on the Fourier coefficients is identical. For the second formula, by \cref{thm:diamond_operator_decomposition_modular} we may assume that \(g \in \mc{S}\left(\frac{N}{p},\chi\right)\). Then \(g\|_{k}\a_{p} \in \mc{S}_{k}(N,\chi)\) (recall \cref{equ:lifting_operator_modular}) and the second formula follows by comparing Fourier coefficients using \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular}. Thus the Hecke operators \(T_{q}\), save for \(q = p\), preserve \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\). Lastly, we consider the Hecke operator \(T_{p}\). For this Hecke operator, it suffices to show
        \[
          T_{p}i_{p}(f,g) = i_{p}(T_{p}f+p^{k-1}g,-\<p\>f).
        \]
        This will follow from the formulas
        \[
          T_{p}f = T_{p}f-(\<p\>f)\|_{k}\a_{p} \quad \text{and} \quad T_{p}(g\|_{k}\a_{p}) = p^{k-1}g,
        \]
        where the diamond and Hecke operators on the left-hand and right-hand sides are on levels \(N\) and \(\frac{N}{p}\) respectively. Since \(p \mid N\), \cref{prop:explicit_description_of_Hecke_operators_modular} gives
        \[
          T_{p}f = \sum_{j \tmod{p}}f\bigg\|_{k}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix} = T_{p}f-(\<p\>f)\|_{k}\a_{p},
        \]
        where the second equality follows regardless of whether \(p \mid \frac{N}{p}\) or not because either \(\<p\>\) is the zero operator on level \(\frac{N}{p}\) (in the case \(p \mid \frac{N}{p}\)) or it annihilates the extra term in the Hecke operator \(T_{p}\) on level \(\frac{N}{p}\) (in the case \(p \nmid \frac{N}{p}\)). Therefore the first formula holds. Similarly, since \(p \mid N\), \cref{prop:explicit_description_of_Hecke_operators_modular} gives
        \[
          T_{p}(g\|_{k}\a_{p})(z) = \sum_{j \tmod{p}}g\bigg\|_{k}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix}\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix} = \sum_{j \tmod{p}}g\bigg\|_{k}\begin{pmatrix} p & pj \\ 0 & p \end{pmatrix} = p^{k-1}g,
        \]
        where the last equality follows because \(g\) is \(1\)-periodic (as \(h_{\infty} = 1\)). This shows that the second formula holds. Thus the Hecke operator \(T_{p}\) preserves \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\). We have now shown that all of the diamond and Hecke operators preserve \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\). To show that they also preserve \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\), let \(f\) and \(g\) be a newform and an oldform respectively. Then for any \(m \ge 1\), \cref{prop:Atkin_Lehner_adjoint_diamond_Hecke_modular} gives
        \[
          \<\<m\>f,g\> = \<f,\w_{N}\<m\>\w_{N}^{-1}g\> = 0 \quad \text{and} \quad \<T_{m}f,g\> = \<f,\w_{N}T_{m}\w_{N}^{-1}g\> = 0,
        \]
        where the second equality in either identity holds because the diamond and Hecke operators preserve \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\) and so does the Atkin-Lehner operator \(\w_{N}\) (and hence its inverse as well) by \cref{prop:Atkin_Lehner_modular}. It follows that the diamond and Hecke operators preserve \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) and this completes the proof.
      \end{proof}

      As a corollary, we deduce that these subspaces admit orthogonal bases of eigenforms:

      \begin{corollary}\label{cor:old/new_eigenbasis_modular}
        \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\) and \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) admit orthonormal bases of eigenforms.
      \end{corollary}
      \begin{proof}
        This follows immediately from \cref{thm:eigenforms_forms_spectral_theory_modular,prop:old/new_subspaces_are_invariant_modular}.
      \end{proof}

      Something quite amazing happens for the subspace in \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\); the eigenforms are eigenfunctions for all of the diamond and Hecke operators so that they are Hecke eigenforms. We require a preliminary result whose proof is quite involved but it is not beyond the scope of this text (see \cite{diamond2005first} for a proof):

      \begin{lemma}\label{lem:the_main_lemma_for_newforms_modular}
        If \(f \in \mc{S}_{k}(\G_{1}(N))\) has Fourier coefficients \(a_{n}(f)\) and is such that \(a_{n}(f) = 0\) for all \(n \ge 1\) whenever \((n,N) = 1\) then
        \[
          f = \sum_{p \mid N}p^{k-1}f_{p}\|_{k}\a_{p},
        \]
        for some \(f_{p} \in \mc{S}_{k}\left(\G_{1}\left(\frac{N}{p}\right)\right)\).
      \end{lemma}

      The important observation to make about \cref{lem:the_main_lemma_for_newforms_modular} is that if \(f \in \mc{S}_{k}(\G_{1}(N))\) is such that its \(n\)-th Fourier coefficients vanish when \(n\) is relatively prime to the level then \(f\) must be an oldform. With this lemma we can prove the main theorem about \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\). The introduction of some language will be useful for the statement and its proof. We say that \(f\) is a \textbf{primitive Hecke eigenform}\index{primitive Hecke eigenform} if it is a nonzero Hecke normalized Hecke eigenform in \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\). We can now prove the main result about newforms which is that Hecke eigenforms exist:

      \begin{theorem}\label{thm:newforms_characterization_modular}
        Let \(f \in \mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) be an eigenform. Then the following hold:
        \begin{enumerate}[label*=(\roman*)]
          \item \(f\) is a Hecke eigenform.
          \item If \(g\) is any cusp form with the same Hecke eigenvalues at all primes then \(g = cf\) for some nonzero \(c \in \C\).
        \end{enumerate}
        Moreover, the primitive Hecke eigenforms in \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) form an orthogonal basis and each such eigenform lies in an eigenspace \(\mc{S}_{k}(N,\chi)\).
      \end{theorem}
      \begin{proof}
        First suppose \(f \in \mc{S}_{k}(\G_{1}(N))\) is an eigenform with Fourier coefficients \(a_{n}(f)\). For \(m \ge 1\) with \((m,N) = 1\), there exists \(\l_{f}(m),\mu_{f}(m) \in \C\) such that \(T_{m}f = \l_{f}(m)f\) and \(\<m\>f = \mu_{f}(m)f\). Actually, \(\<m\>f = \mu_{f}(m)f\) holds for all \(m \ge 1\) because \(\<m\>\) is the zero operator if \((m,N) > 1\) and in this case we can take \(\mu_{f}(m) = 0\). If we set \(\chi(n) = \mu_{f}(m)\) then \(\chi\) is a Dirichlet character modulo \(N\). This follows because multiplicativity of \(\<m\>\) implies the same for \(\chi\) and \(\chi\) is \(N\)-periodic since \(\<m\>\) is \(N\)-periodic (\(\<m\>\) is defined by \(m\) taken modulo \(N\)). But then \(\<m\>f = \chi(m)f\) so that \(f \in \mc{S}_{k}(N,\chi)\). As \(f\) is an eigenform, we also have \(a_{m}(f) = \l_{f}(m)a_{1}(f)\) provided \((m,N) = 1\). So if \(a_{1}(f) = 0\) then \cref{lem:the_main_lemma_for_newforms_modular} implies \(f \in \mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\). With this fact in hand, we can prove the statements.
        \begin{enumerate}[label*=(\roman*)]
          \item The claim is trivial if \(f\) is zero, so assume otherwise. If \(f \in \mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) then \(f \notin \mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\) and so by what we have shown \(a_{1}(f) \neq 0\). Therefore we may Hecke normalize \(f\) so that \(a_{1}(f) = 1\) and \(a_{m}(f) = \l_{f}(m)\). Now set \(g_{m} = T_{m}f-\l_{f}(m)f\) for any \(m \ge 1\). By \cref{prop:old/new_subspaces_are_invariant_modular}, \(g_{m} \in \mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\). Moreover, \(g_{m}\) is an eigenform and its first Fourier coefficient is zero. But then \(g_{m} \in \mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\) too and so \(g_{m} = 0\) because \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) and \(\mc{S}_{k}^{\mathrm{old}}(\G_{1}(N))\) are orthogonal subspaces. This means \(T_{m}f = \l_{f}(m)f\) for any \(m \ge 1\). Therefore \(f\) is a primitive Hecke eigenform and so is a Hecke eigenform before Hecke normalization.
          \item Suppose \(g\) has the same Hecke eigenvalues at all primes. By multiplicativity of the Hecke operators, \(g\) is a Hecke eigenform. After Hecke normalization, \(f\) and \(g\) have the same Fourier coefficients and so are identical. It follows that before Hecke normalization \(f = cg\) for some nonzero \(c \in \C\).
        \end{enumerate}
        Note that our initial remarks together with (i) show that each primitive Hecke eigenform \(f\) belongs to some eigenspace \(\mc{S}_{k}(N,\chi)\). By \cref{cor:old/new_eigenbasis_modular}, \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) admits an orthogonal basis of eigenforms which by (i) are Hecke eigenforms. As \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) is finite dimensional (because \(\mc{S}_{k}(\G_{1}(N))\) is), it follows that all of the primitive Hecke eigenforms form an orthogonal basis for \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) if we can show that they are linearly independent. So suppose to the contrary that we have a nontrivial linear relation
        \[
          \sum_{1 \le i \le r}c_{i}f_{i} = 0,
        \]
        for some primitive Hecke eigenforms \(f_{i}\), nonzero constants \(c_{i}\), and with \(r\) minimal. Note that \(r \ge 2\) for else we do not have a nontrivial linear relation. Letting \(m \ge 1\) applying the operator \(T_{m}-\l_{f_{1}}(m)\) to our nontrivial linear relation gives
        \[
          \sum_{2 \le i \le r}c_{i}(\l_{f_{i}}(m)-\l_{f_{1}}(m))f_{i} = 0,
        \]
        which has one less term. Since \(r\) was chosen to be minimal, this implies \(\l_{f_{i}}(m)-\l_{f_{1}}(m)\) for all \(i\). But \(m\) was arbitrary, so \(f_{i} = f_{1}\) for all \(i\) by (ii). Hence \(r = 1\) which is a contradiction.
      \end{proof}

      Statement (i) in \cref{thm:newforms_characterization_modular} implies that primitive Hecke eigenforms satisfy the Hecke relations for all \(n,m \ge 1\). Statement (ii) is known as \textbf{multiplicity one}\index{multiplicity one} for modular forms and can be interpreted as saying that a basis of newforms for \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) contains one element per set of eigenvalues for the Hecke operators. We will now discuss conjugate cusp forms. For any \(f \in \mc{S}_{k}(N,\chi)\), we define the \textbf{conjugate}\index{conjugate} \(f^{\s}\) of \(f\) by
      \[
        f^{\s}(z) = \conj{f(-\conj{z})}.
      \]
      Note that if \(f\) has Fourier coefficients \(a_{n}(f)\) then \(f^{\s}\) has Fourier coefficients \(\conj{a_{n}(f)}\). It turns out that \(f^{\s}\) is indeed a cusp form and behaves well with respect to the Hecke operators:

      \begin{proposition}\label{cref:conjugate_cusp_form_modular}
        If \(f \in \mc{S}_{k}(N,\chi)\) then \(f^{\s} \in \mc{S}_{k}(N,\cchi)\). Moreover,
        \[
          T_{m}f^{\s} = (T_{m}f)^{\s},
        \]
        for all \(m \ge 1\) with \((m,N) = 1\). In particular, if \(f\) is an eigenform with Hecke eigenvalues \(\l_{f}(m)\) then \(f^{\s}\) is too with Hecke eigenvalues \(\conj{\l_{f}(m)}\).
      \end{proposition}
      \begin{proof}
        Holomorphy is clear so we need next need to verify modularity. For this, let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}(N)\) and set \(\g' = \begin{psmallmatrix} a & -b \\ -c & d \end{psmallmatrix} \in \G_{0}(N)\). Then \(-\conj{\g z} = \g'(-\conj{z})\) and \(j(\g',-\conj{z}) = j(\g,\conj{z})\) for all \(z \in \H\). We also have \(\chi(\g') = \chi(\g)\). Using these fact, we compute
        \begin{align*}
          (f^{\s}|_{k}\g)(z) &= j(\g,z)^{-k}f^{\s}(\g z) \\
          &= \conj{j(\g,\conj{z})^{-k}f(-\conj{\g z})} \\
          &= \conj{j(\g,\conj{z})^{-k}f(\g'(-\conj{z}))} \\
          &= \conj{\chi(\g)f(-\conj{z})} && \text{modularity} \\
          &= \cchi(\g)f^{\s}(z).
        \end{align*}
        This proves modularity of \(f^{\s}\). The growth condition follows immediately from that of \(f\) and thus \(f^{\s}\) is a cusp form since \(f\) is. This proves the first statement. The second statement is immediate from \cref{prop:general_Hecke_operators_acting_on_Fourier_coefficients_modular}. For the last statement, suppose \(f \in \mc{S}_{k}(N,\chi)\) is an eigenform with Hecke eigenvalues \(\l_{f}(m)\). Then by what we have already shown,
        \[
          (T_{m}f^{\s})(z) = ((T_{m}f)^{\s})(z) = \conj{T_{m}f(-\conj{z})} = \conj{\l_{f}(m)f(-\conj{z})} = \conj{\l_{f}(m)}f^{\s}(z),
        \]
        which completes the proof.
      \end{proof}
      
      In conjunction with \cref{thm:newforms_characterization_modular}, \cref{cref:conjugate_cusp_form_modular} implies that the primitive Hecke eigenforms in \(\mc{S}_{k}^{\mathrm{new}}(\G_{1}(N))\) are conjugate invariant and if \(f \in \mc{S}_{k}(N,\chi)\) is such an eigenform then \(f^{\s} \in \mc{S}_{k}(N,\cchi)\) is as well. The crucial fact we need is how \(\w_{N}f\) is related to \(f^{\s}\) when \(f\) is a primitive Hecke eigenform:

      \begin{proposition}\label{prop:Atkin_Lehner_conjugation_modular}
        If \(f \in \mc{S}_{k}(N,\chi)\) is a primitive Hecke eigenform then
        \[
          \w_{N}f = \w_{N}(f)f^{\s},
        \]
        where \(f^{\s} \in \mc{S}_{k}(N,\cchi)\) is a primitive Hecke eigenform and \(\w_{N}(f) \in \C\) is nonzero with \(|\w_{N}(f)| = 1\).
      \end{proposition}
      \begin{proof}
        Let \(f\) have Hecke eigenvalues \(\l_{f}(m)\). On the one hand, \cref{thm:newforms_characterization_modular,cref:conjugate_cusp_form_modular} together imply that \(f^{\s}\) is a primitive Hecke eigenform with Hecke eigenvalues \(\conj{\l_{f}(m)}\). One the other hand, \cref{prop:Atkin_Lehner_adjoint_diamond_Hecke_modular} implies \(\w_{N}T_{m} = T_{m}^{\ast}\w_{N}\) for all \(m \ge 1\). Then
        \[
          \<T_{m}\w_{N}f,\w_{N}f\> = \<\w_{N}f,T_{m}^{\ast}\w_{N}f\> = \<\w_{N}f,\w_{N}T_{m}f\> = \<\w_{N}f,\l_{m}(f)\w_{N}f\> = \conj{\l_{f}(m)}\<\w_{N}f,\w_{N}f\>,
        \]
        and it follows that \(T_{m}\w_{N}f = \conj{\l_{f}(m)}\w_{N}f\). In other words, \(\w_{N}f\) is a Hecke eigenform with Hecke eigenvalues \(\conj{\l_{f}(m)}\). Then multiplicity one gives
        \[
          \w_{N}f = \w_{N}(f)f^{\s},
        \]
        for some nonzero \(\w_{N}(f) \in \C\). Actually, by \cref{prop:Atkin_Lehner_modular} we see that \(\w_{N}\) is at most of order \(4\) so necessarily \(|\w_{N}(f)| = 1\).
      \end{proof} 
    \subsection{\todo{The Ramanujan-Petersson Conjecture}}
      We will now discuss a famous conjecture about the Hecke eigenvalues of primitive Hecke eigenforms. Historically the conjecture was born from conjectures made about the \textbf{modular discriminant}\index{modular discriminant} \(\D\) given by
      \[
        \D = \frac{1}{1728}(E_{4}^{3}-E_{6}^{2}),
      \]
      which is a primitive Hecke eigenform in \(\mc{S}_{12}(1)\) (see \cite{diamond2005first} for a proof). Therefore it is natural to begin our discussion here. It can be shown that the Fourier series of the modular discriminant is
      \[
        \D(z) = \sum_{n \ge 1}\tau(n)e^{2\pi i nz},
      \]
      where the \(\tau(n)\) are integers with \(\tau(1) = 1\) and \(\tau(2) = -24\) (see \cite{diamond2005first} for a proof). The function \(\tau:\Z_{\ge 1} \to \Z\) is called \textbf{Ramanujan's \(\tau\) function}\index{Ramanujan's \(\tau\) function}. Ramanujan himself studied this function in his 1916 paper (see \cite{ramanujan1916certain}), and computed \(\tau(n)\) for \(1 \le n \le 30\). From these computations he conjectured that \(\tau\) should satisfy the following three properties:
      \begin{enumerate}[label*=(\roman*)]
        \item If \((n,m) = 1\) then \(\tau(nm) = \tau(n)\tau(m)\).
        \item \(\tau(p^{n}) = \tau(p^{n-1})\tau(p)-p^{11}\tau(p^{n-2})\) for all primes \(p\).
        \item \(|\tau(p)| \le 2p^{\frac{11}{2}}\) for all primes \(p\).
      \end{enumerate}
      Note that (i) means \(\tau\) is multiplicative. Moreover, (i) and (ii) are strikingly similar to the properties satisfied by the Hecke operators. In fact, (i) and (ii) are follow from the fact that \(\D\) is a Hecke eigenform. Property (iii) turned out to be drastically more difficult to prove and is essentially the Ramanujan-Petersson conjecture for the modular discriminant \(\D\). To state the Ramanujan-Petersson conjecture for modular forms, suppose \(f \in \mc{S}_{k}(N,\chi)\) is a primitive Hecke eigenform with Hecke eigenvalues \(\l_{f}(m)\). For each prime \(p\), consider the polynomial
      \[
        1-\l_{f}(p)p^{-\frac{k-1}{2}}p^{-s}+\chi(p)p^{-2s}.
      \]
      We call this the \(p\)-th \textbf{Hecke polynomial}\index{Hecke polynomial} of \(f\). We call the roots \(\a_{1}(p)\) and \(\a_{2}(p)\) the \(p\)-th \textbf{Hecke roots}\index{Hecke roots} of \(f\). From this quadratic, we have
      \[
        \a_{1}(p)+\a_{2}(p) = \l_{f}(p)p^{-\frac{k-1}{2}} \quad \text{and} \quad \a_{1}(p)\a_{2}(p) = \chi(p).
      \]
      Then the more general \textbf{Ramanujan-Petersson conjecture}\index{Ramanujan-Petersson conjecture} for modular forms is following statement:

      \begin{theorem*}[Ramanujan-Petersson conjecture, modular]
        Let \(f \in \mc{S}_{k}(N,\chi)\) be a primitive Hecke eigenform with Hecke eigenvalues \(\l_{f}(m)\) and let \(\a_{1}(p)\) and \(\a_{2}(p)\) be the \(p\)-th Hecke roots of \(f\). Then for all primes \(p\), we have
        \[
          |\l_{f}(p)| \le 2p^{\frac{k-1}{2}}.
        \]
        Moreover, if \(p \nmid N\) then
        \[
          |\a_{1}(p)| = |\a_{2}(p)| = 1.
        \]
      \end{theorem*}

      In the 1970's Deligne proved the Ramanujan-Petersson conjecture (see \cite{deligne1971formes} and \cite{deligne1974conjecture} for the full proof). The argument is significantly beyond the scope of this text, and in actuality follows from Deligne's work on the Weil conjectures (except in the case \(k = 1\) which requires a modified argument). This requires understanding classical algebraic topology and \(\ell\)-acid cohomology in addition to number theory. As such, the proof of the Ramanujan-Petersson conjecture has been one of the biggest advances in number theory in recent decades. From the Hecke relations and the Ramanujan-Petersson conjecture, we have the more general bound \(\l_{f}(m) \ll \s_{0}(m)m^{\frac{k-1}{2}}\). Then \cref{prop:sum_of_divisors_growth_rate} gives the slightly weaker estimate \(\l_{f}(m) \ll_{\e} m^{\frac{k-1}{2}+\e}\).
    \subsection{\todo{Twists by Dirichlet Characters}}
      We can also twist modular forms by Dirichlet characters. Let \(f \in \mc{S}_{k}(N,\chi)\) have Fourier series
      \[
        f(z) = \sum_{n \ge 1}a_{n}(f)e^{2\pi inz},
      \]
      and let \(\psi\) be a Dirichlet character modulo \(M\). We define the \textbf{twist}\index{twist} \(f \ox \psi\) of \(f\) by \(\psi\) by the Fourier series
      \[
        (f \ox \psi)(z) = \sum_{n \ge 1}a_{n}(f)\psi(n)e^{2\pi inz}.
      \]
      It turns out that \(f \ox \psi\) is a modular form. The following proposition proves this and more in the case \(\psi\) is primitive:

      \begin{proposition}\label{prop:twisted_modular_forms_primitive}
        Suppose \(f \in \mc{S}_{k}(N,\chi)\) and \(\psi\) is a primitive Dirichlet character of conductor \(q\). Then \(f \ox \psi \in \mc{S}_{k}(Nq^{2},\chi\psi^{2})\).
      \end{proposition}
      \begin{proof}
        By \cref{cor:gauss_sum_primitive_formula}, we can write
        \begin{align*}
          (f \ox \psi)(z) &= \sum_{n \ge 1}a_{n}(f)\psi(n)e^{2\pi inz} \\
          &= \sum_{n \ge 1}a_{n}(f)\left(\frac{1}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)e^{\frac{2\pi irn}{q}}\right)e^{2\pi inz} \\
          &= \frac{1}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)\sum_{n \ge 1}a_{n}(f)e^{2\pi in\left(z+\frac{r}{q}\right)} \\
          &= \frac{1}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)f\left(z+\frac{r}{q}\right).
        \end{align*}
        From this last expression, holomorphy is immediate since the sum is finite. For modularity, let \(\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{0}(Nq^{2})\) and set \(\g_{r} = \begin{psmallmatrix} 1 & \frac{r}{q} \\ 0 & 1 \end{psmallmatrix}\) for every \(r\) modulo \(q\). Then for \(r\) and \(r'\) taken modulo \(q\), we compute
        \[
          \g_{r}\g\g_{r'}^{-1} = \begin{pmatrix} 1 & \frac{r}{q} \\ 0 & 1 \end{pmatrix}\begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} 1 & -\frac{r'}{q} \\ 0 & 1 \end{pmatrix} = \begin{pmatrix} a+\frac{cr}{q} & b-\frac{ar'-dr}{q}-\frac{crr'}{q^{2}} \\ c & d-\frac{cr'}{q} \end{pmatrix}.
        \]
        Since \(c \equiv 0 \tmod{Nq^{2}}\), if we choose \(r'\) (for each \(r\)) such that \(ar' \equiv dr \tmod{q}\) then \(\g_{r}\g\g_{r}^{-1} \in \G_{0}(N)\). Such a choice exists and is unique by B\'ezout's identity because \(a\) and \(d\) are relatively prime to \(q\) as \(ad \equiv 1 \tmod{Nq^{2}}\). Making this choice and setting \(\eta_{r} = \g_{r}\g\g_{r'}^{-1}\), modularity implies
        \[
          f\left(\g z+\frac{r}{q}\right) = f(\g_{r}\g z) = f(\eta_{r}\g_{r'}z) = \chi(\eta_{r})j(\eta_{r},\g_{r'}z)^{k}f(\g_{r'}z) = \chi(\eta_{r})j(\eta_{r},\g_{r'}z)^{k}f\left(z+\frac{r'}{q}\right).
        \]
        Moreover,
        \[
          \chi(\eta_{r})j(\eta_{r},\g_{r'}z) = \chi\left(d-\frac{cr'}{q}\right)\left(c\g_{r'}z+d-\frac{cr'}{q}\right) = \chi(d)(cz+d) = \chi(\g)j(\g,z).
        \]
        These two computations together imply
        \[
          f\left(\g z+\frac{r}{q}\right) = \chi(\g)j(\g,z)^{k}f\left(z+\frac{r'}{q}\right).
        \]
        Now, as \(ar' \equiv dr \tmod{q}\) and \(ad \equiv 1 \tmod{q}\), we have
        \[
          \conj{\psi}(r) = \conj{\psi}(a\conj{d}r') = \psi^{2}(d)\conj{\psi}(r') = \psi^{2}(\g)\conj{\psi}(r').
        \]
        Putting everything together,
        \begin{align*}
          (f \ox \psi)(\g z) &= \frac{1}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)f\left(\g z+\frac{r}{q}\right) \\
          &= \chi(\g)j(\g,z)^{k}\frac{1}{\tau(\conj{\psi})}\sum_{r' \tmod{q}}\conj{\psi}(r)f\left(z+\frac{r'}{q}\right) \\
          &= \chi\psi^{2}(\g)j(\g,z)^{k}\frac{1}{\tau(\conj{\psi})}\sum_{r' \tmod{q}}\conj{\psi}(r')f\left(z+\frac{r'}{q}\right) \\
          &= \chi\psi^{2}(\g)j(\g,z)^{k}(f \ox \psi)(z).
        \end{align*}
        from which modularity of \(f \ox \psi\) follows. For the growth condition, let \(\s_{\mf{a}}\) be a scaling matrix for a cusp \(\mf{a}\) of \(\G_{0}(Nq^{2})\backslash\H\). As \(\g_{r} \in \GL_{2}^{+}(\Q)\), \(\g_{r}\s_{\mf{a}}\) takes \(\infty\) to an element of \(\what{\Q}\). Thus \(\g_{r}\s_{\mf{a}}\infty = \mf{b}\) for some cusp \(\mf{b}\) of \(\G_{0}(N)\backslash\H\). Then as \(j(\g_{r},\s_{\mf{a}}z) = 1\), our previous work implies
        \[
          ((f \ox \psi)|_{k}\s_{\mf{a}})(z) = \frac{1}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)j(\g_{r}\s_{\mf{a}},z)^{-k}f(\g_{r}\s_{\mf{a}}z),
        \]
        and so the growth condition follows from that of \(f\). Thus \(f \ox \psi\) is a cusp form since \(f\) is.
      \end{proof}

      The generalization of \cref{prop:twisted_modular_forms_primitive} to all characters is slightly more involved. To this end, define operators \(U_{p}\) and \(V_{p}\) on \(\mc{S}_{k}(\G_{1}(N))\) to be the linear operators given by
      \[
        (U_{p}f)(z) = \sum_{n \ge 1}a_{np}(f)e^{2\pi inz},
      \]
      and
      \[
        (V_{p}f)(z) = \sum_{n \ge 1}a_{n}(f)e^{2\pi inpz},
      \]
      if \(f\) has Fourier series
      \[
        f(z) = \sum_{n \ge 1}a_{n}(f)e^{2\pi inz}.
      \]
      We will show that both \(U_{p}\) and \(V_{p}\) map \(\mc{S}_{k}(\G_{1}(N))\) into \(\mc{S}_{k}(\G_{1}(Np))\) and more:

      \begin{lemma}\label{lem:twisted_modular_lemma}
        For any prime \(p\), \(U_{p}\) and \(V_{p}\) map \(\mc{S}_{k}(\G_{1}(N))\) into \(\mc{S}_{k}(\G_{1}(Np))\). In particular, \(U_{p}\) and \(V_{p}\) map \(\mc{S}_{k}(N,\chi)\) into \(\mc{S}_{k}(Np,\chi\chi_{p,0})\).
      \end{lemma}
      \begin{proof}
        In light of \cref{thm:diamond_operator_decomposition_modular}, the first statement follows from the second. As \(N \mid Np\), \(\G_{1}(Np) \subseteq \G_{1}(N)\) so that \(f \in \mc{S}_{k}(\G_{1}(Np))\) if \(f \in \mc{S}_{k}(\G_{1}(N))\). Now suppose \(f \in \mc{S}_{k}(N,\chi)\). Similarly, \(N \mid Np\) implies \(\G_{0}(Np) \subseteq \G_{0}(N)\) so that \(f \in \mc{S}_{k}(Np,\chi\chi_{p,0})\) for the modulus \(Np\) character \(\chi\chi_{p,0}\). Therefore we may assume \(f \in \mc{S}_{k}(Np,\chi\chi_{p,0})\). Now consider \(U_{p}\). As \(p \mid Np\), \cref{equ:Hecke_operator_when_p_divides_modular} implies \(U_{p} = T_{p}\) is the \(p\)-th Hecke operator on \(\mc{S}_{k}(\G_{1}(Np))\) and the claim follows from the definition of the Hecke operators and \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_modular}. Now consider \(V_{p}\). We have
        \[
          (V_{p}f)(z) = f(pz),
        \]
        and the claim follows by regarding \(f \in \mc{S}_{k}(Np,\chi\chi_{p,0})\) and that \(I_{p}\) lies in the center of \(\SL_{2}(\Z)\).
      \end{proof}

      We can now generalize \cref{prop:twisted_modular_forms_primitive} to all characters:

      \begin{proposition}\label{prop:twisted_modular_forms}
        Suppose \(f \in \mc{S}_{k}(N,\chi)\) and \(\psi\) is a Dirichlet character modulo \(M\). Then \(f \ox \psi \in \mc{S}_{k}(NM^{2},\chi\psi^{2})\).
      \end{proposition}
      \begin{proof}
        Let \(\wtilde{\psi}\) be the primitive character of conductor \(q\) inducing \(\psi\). Then \(\psi = \wtilde{\psi}\psi_{\frac{M}{q},0}\). As \(\psi_{\frac{M}{q},0} = \prod_{p \mid \frac{M}{q}}\psi_{p,0}\), it suffices to prove the claim in the cases when \(\psi\) is primitive and when \(\psi = \psi_{p,0}\). The primitive case follows from \cref{prop:twisted_modular_forms_primitive}. So suppose \(\psi = \psi_{p,0}\). Then
        \[
          f \ox \psi_{p,0} = f-V_{p}U_{p}f.
        \]
        Now by \cref{lem:twisted_modular_lemma}, \(V_{p}U_{p}f \in \mc{S}_{k}(Np^{2},\chi\psi_{p,0}^{2})\) (where we have written \(\psi_{p,0}^{2}\) in place of \(\chi_{p,0}\)). Since we also have \(f \in \mc{S}_{k}(Np^{2},\chi\psi_{p,0}^{2})\) (because \(N \mid Np^{2}\) so that \(\G_{1}(Np^{2}) \subseteq \G_{1}(N)\) and \(\G_{0}(Np^{2}) \subseteq \G_{0}(N)\) and again writing \(\psi_{p,0}^{2}\) in place of \(\chi_{p,0}\)), it follows that \(f \ox \psi_{p,0} \in \mc{S}_{k}(Np^{2},\chi\psi_{p,0}^{2})\). This proves the claim in the case \(\psi = \psi_{p,0}\) and thus completes the proof.
      \end{proof}

      In particular, \cref{prop:twisted_modular_forms} shows that \(f \ox \psi\) is well-defined for any Dirichlet character \(\psi\).
    \section{The Petersson Trace Formula}
      From \cref{thm:newforms_characterization_modular}, \(\mc{S}_{k}(N,\chi)\) admits an orthonormal basis of Hecke eigenforms. In particular, \(\mc{S}_{k}(N,\chi)\) admits a merely orthogonal basis. Denote this basis by \(u_{1},\ldots,u_{r}\) where \(r\) is the dimension of \(\mc{S}_{k}(N,\chi)\). Each of these forms admits a Fourier series at the \(\mf{a}\) cusp given by
      \[
        (u_{j}|_{k}\s_{\mf{a}})(z) = \sum_{n \ge 1}a_{j,\mf{a}}(n)e^{2\pi inz}.
      \]
      The Petersson trace formula is an equation relating the Fourier coefficients \(a_{j,\mf{a}}(n)\) and \(a_{j,\mf{b}}(n)\) for \(1 \le j \le r\) at two cusps \(\mf{a}\) and \(\mf{b}\) of \(\G_{0}(N)\backslash\H\) to a sum of \(J\)-Bessel functions and Sali\'e sums. To prove the Petersson trace formula we compute the inner product of two Poincar\'e series \(P_{n,k,\chi,\mf{a}}(z)\) and \(P_{m,k,\chi,\mf{b}}(z)\) in two different ways. One way is geometric in nature while the other is spectral. Since \cref{thm:Petersson_inner_product_with_Poincare_series} says that \(\<P_{n,k,\chi,\mf{a}},P_{m,k,\chi,\mf{b}}\>\) extracts the \(m\)-th Fourier coefficient of \(P_{n,k,\chi,\mf{a}}\) at the \(\mf{b}\) cusp up to a constant, the Petersson trace formula amounts to computing the \(m\)-th Fourier coefficient of \(P_{n,k,\chi,\mf{a}}\) in two different ways. We will begin with the geometric method first. This is easy as we have already computed the Fourier series of the Poincar\'e series. Applying \cref{thm:Petersson_inner_product_with_Poincare_series} to \(\<P_{n,k,\chi,\mf{a}},P_{m,k,\chi,\mf{b}}\>\) and using \cref{prop:Fourier_series_Poincare_modular} gives
      \begin{equation}\label{equ:Petersson_trace_1}
        \begin{aligned}
          \<P_{n,k,\chi,\mf{a}},P_{m,k,\chi,\mf{b}}\> &= \frac{\G(k-1)h_{\mf{b}}^{k}}{V_{\G_{0}(N)}(4\pi m)^{k-1}} \\
          &\cdot \left(\d_{\mf{a},\mf{b}}\d_{n,m}+2\pi i^{-k}\left(\frac{\sqrt{mh_{\mf{a}}}}{\sqrt{nh_{\mf{b}}}}\right)^{k-1}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi,\mf{a},\mf{b}}(n,m,c)}{ch_{\mf{b}}}J_{k-1}\left(\frac{4\pi\sqrt{nm}}{c\sqrt{h_{\mf{a}}h_{\mf{b}}}}\right)\right).
        \end{aligned}
      \end{equation}
      This is the first identity we are after. To obtain the second identity, we use the fact that \(u_{1},\ldots,u_{r}\) is an orthogonal basis for \(\mc{S}_{k}(N,\chi)\) and \cref{thm:Petersson_inner_product_with_Poincare_series} to write
      \[
        P_{n,k,\chi,\mf{a}}(z) = \sum_{1 \le j \le r}\frac{\<P_{n,k,\chi,\mf{a}},u_{j}\>}{\<u_{j},u_{j}\>}u_{j}(z) = \sum_{1 \le j \le r}\frac{\conj{\<u_{j},P_{n,k,\chi,\mf{a}}\>}}{\<u_{j},u_{j}\>}u_{j}(z) = \frac{\G(k-1)h_{\mf{a}}^{k}}{V_{\G_{0}(N)}(4\pi n)^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j,\mf{a}}(n)}}{\<u_{j},u_{j}\>}u_{j}(z).
      \]
      This last expression is the spectral decomposition of \(P_{n,k,\chi,\mf{a}}(z)\) in terms of the basis \(u_{1},\ldots,u_{r}\). So if we take the inner product of this last expression with \(P_{m,k,\chi,\mf{b}}\) and apply \cref{thm:Petersson_inner_product_with_Poincare_series}, we obtain
      \begin{equation}\label{equ:Petersson_trace_2}
        \<P_{n,k,\chi,\mf{a}},P_{m,k,\chi,\mf{b}}\> = \frac{\G(k-1)^{2}(h_{\mf{a}}h_{\mf{b}})^{k}}{V_{\G_{0}(N)}^{2}(16\pi^{2}nm)^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j,\mf{a}}(n)}a_{j,\mf{b}}(m)}{\<u_{j},u_{j}\>}.
      \end{equation}
      This is the second identity we are after. Combine \cref{equ:Petersson_trace_1,equ:Petersson_trace_2} and clear the \(\frac{\G(k-1)h_{\mf{b}}^{k}}{V_{\G_{0}(N)}(4\pi m)^{k-1}}\) factor to see that
      \[
        \frac{\G(k-1)h_{\mf{a}}^{k}}{V_{\G_{0}(N)}(4\pi n)^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j,\mf{a}}(n)}a_{j,\mf{b}}(m)}{\<u_{j},u_{j}\>} = \d_{\mf{a},\mf{b}}\d_{n,m}+2\pi i^{-k}\left(\frac{\sqrt{mh_{\mf{a}}}}{\sqrt{nh_{\mf{b}}}}\right)^{k-1}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi,\mf{a},\mf{b}}(n,m,c)}{ch_{\mf{b}}}J_{k-1}\left(\frac{4\pi\sqrt{nm}}{c\sqrt{h_{\mf{a}}h_{\mf{b}}}}\right).
      \]
      Since \(\left(\frac{\sqrt{mh_{\mf{a}}}}{\sqrt{nh_{\mf{b}}}}\right)^{k-1} = 1\) when \(\d_{\mf{a},\mf{b}}\d_{n,m} = 1\), we can factor this term out of the entire right-hand side and clear it resulting in
      \[
        \frac{\G(k-1)h_{\mf{a}}\sqrt{h_{\mf{a}}h_{\mf{b}}}^{k-1}}{V_{\G_{0}(N)}(4\pi\sqrt{nm})^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j,\mf{a}}(n)}a_{j,\mf{b}}(m)}{\<u_{j},u_{j}\>} = \d_{\mf{a},\mf{b}}\d_{n,m}+2\pi i^{-k}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi,\mf{a},\mf{b}}(n,m,c)}{ch_{\mf{b}}}J_{k-1}\left(\frac{4\pi\sqrt{nm}}{c\sqrt{h_{\mf{a}}h_{\mf{b}}}}\right).
      \]
      Finally, divide by \(h_{\mf{a}}\) and note that \(h_{\mf{a}} = \sqrt{h_{\mf{a}}h_{\mf{b}}}\) when \(\d_{\mf{a},\mf{b}} = 1\) to obtain the \textbf{Petersson trace formula}\index{Petersson trace formula} relative to the \(\mf{a}\) and \(\mf{b}\) cusps:
      \[
        \frac{\G(k-1)\sqrt{h_{\mf{a}}h_{\mf{b}}}^{k-1}}{V_{\G_{0}(N)}(4\pi\sqrt{nm})^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j,\mf{a}}(n)}a_{j,\mf{b}}(m)}{\<u_{j},u_{j}\>} = \frac{\d_{\mf{a},\mf{b}}\d_{n,m}}{\sqrt{h_{\mf{a}}h_{\mf{b}}}}+2\pi i^{-k}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi,\mf{a},\mf{b}}(n,m,c)}{ch_{\mf{a}}h_{\mf{b}}}J_{k-1}\left(\frac{4\pi\sqrt{nm}}{c\sqrt{h_{\mf{a}}h_{\mf{b}}}}\right).
      \]
      We refer to the left-hand side side as the \textbf{spectral side}\index{spectral side} and the right-hand side as the \textbf{geometric side}\index{geometric side}. We collect our work as a theorem:

      \begin{theorem*}[Petersson trace formula]
        Let \(u_{1},\ldots,u_{r}\) be an orthogonal basis of Hecke eigenforms for \(\mc{S}_{k}(N,\chi)\) with Fourier coefficients \(a_{j,
        \mf{a}}(n)\) at the \(\mf{a}\) cusp. Then for any positive integers \(n,m \ge 1\) and any two cusps \(\mf{a}\) and \(\mf{b}\) of \(\G_{0}(N)\backslash\H\), we have
        \[
          \frac{\G(k-1)\sqrt{h_{\mf{a}}h_{\mf{b}}}^{k-1}}{V_{\G_{0}(N)}(4\pi\sqrt{nm})^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j,\mf{a}}(n)}a_{j,\mf{b}}(m)}{\<u_{j},u_{j}\>} = \frac{\d_{\mf{a},\mf{b}}\d_{n,m}}{\sqrt{h_{\mf{a}}h_{\mf{b}}}}+2\pi i^{-k}\sum_{c \in \mc{C}_{\mf{a},\mf{b}}}\frac{S_{\chi,\mf{a},\mf{b}}(n,m,c)}{ch_{\mf{a}}h_{\mf{b}}}J_{k-1}\left(\frac{4\pi\sqrt{nm}}{c\sqrt{h_{\mf{a}}h_{\mf{b}}}}\right).
        \]
      \end{theorem*}
      
      Note that if we take \(u_{1},\ldots,u_{r}\) to be an orthonormal basis, equivalently the basis elements are Hecke normalized, then \(\<u_{j},u_{j}\> = 1\). Regardless, a particularly important case of the Petersson trace formula is when \(\mf{a} = \mf{b} = \infty\) and \(\s_{\mf{a}} = \s_{\mf{b}} = I\). For then \(h_{\mf{a}} = h_{\mf{b}} = 1\), \(\mc{C}_{\infty,\infty} = \{c \ge 1:c \equiv 0 \tmod{N}\}\), the Sali\'e sum reduces to the usual one, and the Petersson trace formula takes the form
      \[
        \frac{\G(k-1)}{V_{\G_{0}(N)}(4\pi \sqrt{nm})^{k-1}}\sum_{1 \le j \le r}\frac{\conj{a_{j}(n)}a_{j}(m)}{\<u_{j},u_{j}\>} = \d_{n,m}+2\pi i^{-k}\sum_{\substack{c \ge 1 \\ c \equiv 0 \tmod{N}}}\frac{S_{\chi}(n,m,c)}{c}J_{k-1}\left(\frac{4\pi\sqrt{nm}}{c}\right).
    \]
\fi\end{document}